### 2018-12-10 ms5n17-tlp-mn-180216-001.tex
First files

\documentclass[preprint,12pt]{article}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,authblk,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{Modular transmission line probes for microfluidic NMR}
\author[1]{Manvendra Sharma}
\author[1]{Marcel Utz}
\affil[1]{School of Chemistry, University of Southampton, Southampton SO17 1BJ, United Kingdom}
\date{\today}
\setcounter{Maxaffil}{0}
\renewcommand\Affilfont{\itshape\footnotesize}
\maketitle
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Microfluidic NMR (Nuclear Magnetic Resonance) presents the possibility of probing chemical or bio-chemical reactions, cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment. We present a dual channel modular probe assembly for  high efficiency microfluidic-NMR. The samples are contained in exchangeable, flow compatible planar microfluidic devices. The detector including the tuning and matching circuitry of the probe is modular which allows the use of different detectors optimised for different experimental conditions on the same probe base. The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB materials. The probe can be built from scratch with no requirement of any parts or electronics from commercial probes. The probe has a limit of detection of 1.18 nmol s$^{-1/2}$ and excellent B$_{1}$ homogeneity. The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel ($^{13}$C or $^{15}$N) frequencies. We have successfully acquired $^1$H-$^{13}$C and $^1$H-$^{15}$N heteronuclear correlation spectrum (HSQC). Particularly, $^1$H-$^{15}$N HSQC spectrum of 1 mM $^{15}$N labeled ubiquitin from 2.5 $\mu$l of sample volume.
\end{abstract}
\maketitle
%\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}	
\label{sec:intro}
%\begin{itemize}
%	\item Microfluidic NMR: importance and prospects
%	\item Flow probes based on solenoids and strip lines
%	\item For NMR observation on microfluidic devices, easy exchange of the device is important; flow probes
%	are not always practical
%	\item Different microfluidic NMR applications require different probe geometries and tunings (nuclei, optimisation,
%		sample size, magnetic field, environmental controls VT etc)
%	\item Heteronuclear / double resonance
%	\item Building standalone probes for all these different cases may not be desirable/practical
%	\item We present a modular probe concept in which the detector and tuning/matching circuitry can be easily exchanged
%	to meet different needs
%	\item We demonstrate this by a probe that can acquire NMR spectra for 1H, 1H/15N, 1H/13C, as well as MR images
%	\item No compromises are required in terms of sensitivity
%	\item The incremental cost of an additional insert is very small (o(200 Euros))
%\end{itemize}
NMR (Nuclear Magnetic Resonance) is a well established technique used in chemical analysis~\cite{NMR-chemical-1995, hills1994magnetic, rabenstein1991quantitative}, metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, molecular structure determination~\cite{wuthrich1990protein}, reaction monitoring~\cite{maiwald2004quantitative} etc. Microfluidic lab-on-a-chip (LOC) devices are increasingly finding wide applications in chemistry and the life sciences~\cite{whitesides2006origins,mark2010microfluidic}. In addition to providing a way to integrate complex chemical and biochemical analytical processes with sample preparation and even culture of cells and other biological systems, they allow detailed control over growth conditions, and high experimental throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. In general, information on the system under study is extracted from microfluidic devices by spectroscopic techniques at the end point of the experiment. This typically involves interrogation using fluorescent probes which bind to one or a few analytes of interest. This approach can reach very high sensitivity, with limits of detection down to femtomolar concentrations. However, it is usually destructive, since the sample is affected by the addition of the marker, and can only be done once, at the end of the experiment. Following kinetic processes therefore requires using multiple samples. By contrast, NMR spectroscopy is non-invasive, generic (virtually all organic molecules give an NMR signal), and highly specific (no two metabolites share the same NMR spectrum). For these reasons, NMR spectroscopy could provide a useful complementary readout capability for microfluidic devices. For example, the metabolic activity of a cell culture sample can be followed non-invasively by NMR throughout the course of the experiment, while effects on cell differentiation can still be analysed by a (destructive) transcriptomic analysis at the end. Unfortunately, the sensitivity of NMR is much lower than that of optical techniques. The small volumes involved in microfluidic systems (typically in the range of 1 $\mu$l) compound this problem. Fortunately, the mass limit of detection of Inductive NMR detectors tends to improve as they are scaled down~\cite{Olson1995}. On this basis, a number of different micro-NMR detector designs have been proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline coils~\cite{stripline_jan}. While significant research has gone into developing micro-NMR detectors for flow probes, only a few designs that allow insertion of a generic microfluidic device into the detector have been described.\par
In this paper we present a novel modular probe designed for generic microfluidic-NMR experiments. The design is based on a transmission line detector~\cite{stripline_jan,gream_2016}, which is realised using inexpensive printed circuit board (PCB) technology. A modular design ensures that detectors of different geometry and size can be easily exchanged. NMR detector (including the tuning and matching circuit) is connected to the probe skeleton through detachable connectors. Modularity of the probe not only allows fast optimisation of the detector but also different detectors optimised for different experimental conditions like mass sensitivity, concentration sensitivity, sample volume, single or dual channel etc can be used on a single probe base. Using the same probe skeleton does not need any compromise of NMR sensitivity, resolution or microfluidic functionality. The cost of an additional detector is only $\sim$200 $\geneuro$ and can be manufactured within 2-3 days. The probe is designed for proton detected double resonance. The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or $^{31}$P. The probe skeleton is designed entirely from easily obtainable raw materials such as aluminium profiles and tubes of standard size, with a small number of custom-machined parts holding the structure together. Detailed construction drawings for the probe are provided in the supporting information. Planer design of the detector allows to use planar exchangeable microfluidic devices. Microfluidic devices can be designed freely for specific experimental requirements as long as the overall shape of the device is maintained within l$\times$ w$\times$ t = 90mm$\times$ 20mm$\times$ 1mm.\par
In the remainder of this paper, we discuss the probe design, and characterise its performance in terms of sensitivity and resolution. We also demonstrate its application in microfluidic cell culture, protein NMR spectroscopy, and micro-imaging. Using the same probe base does not need any compromise of NMR sensitivity, resolution or microfluidic functionality.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
The probe assembly design is based on readily and easily available materials and parts with minimal requirement for fabrication of customised parts to avoid any bottlenecks in the building process. The probe can be built from scratch with no requirement of any part or electronics from commercial NMR probes. All the parts and electronics can be bought readily from commercial sources, with the exception of a small number of precision-machined parts which are used to hold the assembly together. These can be ordered from commercial prototyping manufacturers or machined in-house if mechanical workshop facilities are available.\par
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181015-probe-explode.png} 
\caption{Exploded view of he probe design (left) and assembled probe (right). Probe base (blue) and scaffold assembly (green) with base PCB (brown,8) makes a generic mounting point for the NMR detector (red). A microfluidic device (1) can be inserted from the top of the probe. The device sits on a spacer (4) between the detector planes (3 and 5) having the sample chamber coinciding with the constriction of the PCB planes. A modular PCB insert (6) can be exchanged to change the X channel frequency to $^{13}$C or $^{15}$N. Modular NMR detector is made up of parts 3 to 6 and is connected to the base plate PCB (8) through detachable SMP connectors. Top shows a photograph of the PCB plane 3 having stripline geometry and pads for circuit elements and SMP connectors for RF insert 6. }
\label{fig:probe-explode} 
\end{figure}
The skeleton of the probe consisting of a base (blue in~\ref{fig:probe-explode}) and a scaffold assembly (green in~\ref{fig:probe-explode}) made from standard aluminium profiles. The base is made from a prefabricated aluminium profile and contains the BNC connectors for RF (Radio Frequency) input. The scaffold assembly is made up of two aluminium tubes held together with precision machined parts (10). A base PCB (8) is put on the top of the probe skeleton held with the brass rods (9) for stability. The base PCB holds capacitors (7) for secondary tuning and matching of the resonator at the magnet and low-loss SMP connectors (11 in figure~\ref{fig:ProbePhoto}) to connect the rest of the probe. The probe skeleton with the base PCB serves as a generic mounting point for the NMR detector. The NMR detector is made up of two PCBs (3 and 5), a spacer between them (4) and an RF-insert (6). The PCBs (3 and 5) also carry the circuit electronics for the channel separation and primary tuning and matching of the detector. A copper or brass auxiliary disk (2) holds the PCB's together. The probe sheath (not shown here) is connected to the auxiliary disk (2) and the scaffold assembly through screws. An exchangeable microfluidic device (1) can be inserted from the top of the detector. A microfluidic device can be filled with a sample before putting it in the probe or the device can be put in the probe with some fluidic connectors attached to fill or exchange the sample in-situ. The microfluidic device sits on the spacer between the two PCB planes coinciding the sample chamber with the constriction on the detector.  RF-insert (6) can be exchanged to tune and match the probe to different frequencies at X channel. As the detector is connected to the probe base through detachable connectors, various detectors can be used on the same probe skeleton. The detectors are based on a transmission line design~\cite{gream_2016,stripline_jan}, and fabricated from easily accessible PCB materials. Use of PCB to manufacture the detector allows for easy optimisation of detector dimensions for several applications compared to other manufacturing methods. A detector can be optimised for mass sensitivity, concentration sensitivity, resolution, sample volume, single or dual channel etc for required application.\par
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. A has an O.D. of 44.45 mm, in B, circuit elements of X channel are integrated on the PCB itself making it compact (38 mm O.D.). Detachable SMP connectors (11) are used to connect the RF insert (6) and also the assembled NMR detector. The cost and effort to make a new detector are minimal so, various detectors could be made for various X channel frequencies.}
\label{fig:ProbePhoto}
\end{figure}
Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) for X channel. In (A) X channel could be tuned to different nuclei by exchanging 6. However, in (B) the circuitry of the RF insert (6) is manufactured on the PCB plane (5). Inclusion of the circuitry of 6 on 5 makes the design compact. Probe (A) is compatible with Varian 600 ultra shield 14.1 T magnet having an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B) has an outer diameter (O.D.) of 38 mm including the sheath and hence can be used with a narrow bore magnet. Naturally, B can also be used with wide bore magnets with spacers or gradient stack to keep the probe centred . As already mentioned, the cost and time of making a new PCB is minimal so, different detectors could be made for different X channel frequencies.\par
The microfluidic devices are made from thermally bonded PMMA sheets. The sample chamber and fluidic network are made in the middle layer. The middle layer is sealed in between the bottom and the top layers with inlet and outlet in the top layer. A flow can be introduced from the inlet and outlet of the device for flow studies or sample exchange. The fluidic network on the device can be made freely with the only constrained on the overall size of the device [l $\times$ w $\times$ t = 90 mm $\times$ 20mm $\times$ 1mm]. Other layers can be employed to allow parallel flow as long as the total thickness remains below 1mm.\par
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png} 
\caption{Microfluidic devices for different applications compatible with the current setup. From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow, hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and, to grow cells on the device.}
\label{fig:device} 
\end{figure}
The circuit for a double resonance probe is based on design shown in figure~\ref{fig:circuit}. Dimensions of the detector were chosen for a $\lambda/2$ standing wave at frequency few 100s MHz higher than the proton larmor frequency. The resonator can then be tuned to desired frequency by applying additional capacitance at the resonator. For the X channel the detector is used as a load with the other circuit elements. The detector is connected to the secondary T\&M capacitors with the transmission lines on the PCB planes. As all the circuit elements are assembled on the PCB planes, the transmission lines on the PCB have lengths similar to detector. Hence transmission lines may become a part of the resonance circuit and can severely affect the probe performance. To avoid this problem a series capacitor was included with the transmission line just before the detector to adjust the impedance of transmission line to 50~$\Omega$. In this situation the detector is matched by the transmission line and secondary T\&M capacitors can be used for fine tuning and matching.\par
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe. Proton frequency is feed in from the left (port 2) and X frequency is feed in from right (port 7).}
\label{fig:circuit}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
%\begin{itemize}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%\end{itemize}
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed and simulated on Solidworks (Solidworks, Dassault Syst\`{e}mes). The prefabricated aluminium profiles (base platform, scaffold aluminium tube, probe sleeve) were made from 6061-T3 alloy and were obtained from Aluminum Warehouse, UK to build the probe skeleton. A few customised precision-machined parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford, UK) after providing CAD files. A small number parts were machined in-house (brass support rods, auxiliary support disks). All the electronic components and the semi rigid transmission lines were purchased from Digikey. Cell cast poly (methyl methacrylate) (PMMA) sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were cut to desired size and functionality (holes or channels) through a laser cutter (HPC Laser L3040). The fluidic channels were cut or scored in a 0.5 mm thickness PMMA sheet. The device is made by thermally bonding PMMA sheets using the protocol described in~\cite{yilmaz_bonding}.\par
Dimensions of the detector were calculated from the simulation described in~\cite{gream_2016}. The probe circuit for the double resonance probe was simulated on Mathematica using a symbolic analysis network code to asses the performance of both the channels~\cite{gream-thesis}.\par
The probe circuit was compiled in KiCAD to design the PCB layout. The PCB layout was provided to beta-layout (Aarbergen Germany) and P.W. Circuits LTD (Wigston , UK) to manufacture the PCBs. Easily and inexpensively available FR4 was used for PCB manufacturing (figure~\ref{fig:ProbePhoto} A) but inhomogeneities were observed in B${_0}$ field images for this material. Rogers RO35 from rogers corporation was later used for PCBs (figure~\ref{fig:ProbePhoto} B).\par
The probe skeleton was assembled by holding the prefab aluminium profiles with precision-machined parts and screws. Semi-rigid transmission lines were then threaded through the skeleton. The base PCB plate was soldered on top of the semi-rigid transmission lines. The detector planes (3 and 5) were soldered together separately with the required electronic components characterise by network analysis. Minor changes were made to the values of the probe electronic components to optimise the probe performance in practise.\par
NMR experiments were performed on Varian VNMRS console on a Varian 600 ultra shield 14.1 T magnet. Spectra in figure~\ref{fig:lineshape} and \ref{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse. Spectrum in figure~\ref{fig:1H-nutation} was acquired with increasing the pulse length. Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}. All the samples were purchased from commercial sources and were used without further purification.\par
Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet. To obtain the tissue slices first a core of 8 mm diameter was extracted using a biopsy punch from the liver. PCLS of thickness 250-300 $\mu$m were prepared using a Krumdieck Tissue slicer. Circular slices of 3 mm diameter were then cut from this slice using a smaller punch.The slices were put in the incubator for 2 hours before imaging to allow equilibrium.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
%\begin{itemize}
%	\item Tuning/matching/channel separation
%	\item tuning range (different field strengths)
%	\item Sensitivity calibration
%	\item Resolution
%	\item RF efficiency, B1 homogeneity
%	\item Example spectra to illustrate versatility:
%		\begin{itemize}
%		\item Growth media (1H), cell culture
%		\item Comparison of spectra obtained at 300, 500, 600 MHz
%		\item HSQC (13C, 15N)
%		\item Liver slice image
%		\end{itemize}
%\end{itemize}
A double channel probe allows heteronuclear NMR experiments which are essential for many applications like protein structure determination. The current probe can be simultaneously operated at 2 frequencies. The probe has been tuned to protons and one X channel ($^{13}$C or $^{15}$N) frequencies at a time. As already explained, the X channel tuning frequency can be changed by simply exchanging an rf-insert or the complete detector. Figure~\ref{fig:tandm} shows the measured T\&M curves at different proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz) corresponding to the larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively. The measurement were performed in the pairs of 600 MHz and 60 MHz and, 500 MHz and 125 MHz. The loaded Q factors are 42, 49, 32, 36 at 600 MHz, 500 MHz, 125 MHz and, 60 MHz respectively. Channel separation is better than 15 decibels at all operating frequencies and thus sufficient to perform decoupling during experiments.\par
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
\caption{Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 60 MHz ($^{15}$N frequency at 14 T) and, 125 MHz ($^{13}$C frequency at  and 11.7 T). Probe can be tuned to 2 frequencies at a time, above results were measured in pairs of 600 MHz with 60 MHz and 500 MHz with125 MHz. Decoupling can be performed at all the frequencies as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm} 
\end{figure}
$^1$H nutation diagram of water peak for a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz is shown figure~\ref{fig:1H-nutation}. RF field is highly homogeneous with 810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% at 600~MHz. The probe can generate 100 kHz RF-field for an input power of 100 watts both at 600 MHz and 500 MHz corresponding to RF field efficiency of 10 kHz watts$^{-1/2}$ . $^{15}$N nutation detected on protons for the same sample is shown in figure~\ref{fig:15N-nutation}. An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$ measurements.\par
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png} 
\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz. The 810$^{\circ}$/90$^{\circ}$ ratio is more than 90\% at 600~MHz. The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 Watts. Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz}
\label{fig:1H-nutation} 
\end{figure}
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.}
\label{fig:15N-nutation} 
\end{figure}
Figure~\ref{fig:lineshape} shows a spectrum of 130 mM Na-acetate dissolved in H$_2$O acquired after water presaturation at 600 MHz with 32 averages. The figure in the inset shows expanded view of the base of the acetate peak. Carbon satellites can be seen well above noise level. The orange curve corresponds to a lorentzian lineshape with full width at half maximum of 3.35 Hz. Limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ is  1.18 nmol s$^{1/2}$ at 600 MHz for the acetate sample. The measured LOD is found to be better than the calculated LOD in~\cite{gream_2016} for 600 MHz.\par
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/lineshape.png} 
\caption{Spectrum of 130 mM sodium acetate dissolved in water acquired in 32 scans with water presaturation. Carbon satellites can be seen in the expanded base of the acetate line. The orange curve shows a lorentzian lineshape with full width at half maximum of 3.35 Hz.}
\label{fig:lineshape} 
\end{figure}
Though the resolution for the current setup is not optimised, it can be used to acquired spectrum with sufficient resolution to differentiate between peaks of different molecules in a mixture. Spectrum of DMEM (Dulbecco's modified Eagle's medium) cell growth media acquired with 256 scans in 20 mins is shown in figure~\ref{fig:media-spec} to demonstrate the feasibility of acquiring spectrum for metabolomic studies. Figure~\ref{fig:HSQC} shows the possibility of useful double resonance experiments in the current setup. On left, $^{13}$C-$^{1}$H-HSQC spectrum, acquired in 12 mins (32 t$_1$ increments and 16 scans) from 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in water. On right, $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in a buffer solution. $^{15}$N is a very insensitive nuclei hence very difficult to detect. $^{15}$N-$^{1}$H-HSQC spectrum on 1 mM of protein sample clearly shows that the current probe can be used for protein structure studies with minimal amount of isotopically labeled protein.\par
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png} 
\caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
\label{fig:media-spec} 
\end{figure}
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 
\caption{$^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14 T. Glucose HSQC spectrum was acquired in 12 minutes from a 100 mM sample. Ubiquitin HSQC spectrum was acquired in 400 minutes from a 1 mM sample.}
\label{fig:HSQC} 
\end{figure}
The probe has been used to make micro MR (magnetic resonance) images using a Bruker imaging unit. Figure~\ref{fig:tisli} shows MR images of mouse liver tissue slice immersed in DMEM cell growth media acquired by putting the slices in a microfluidic device with circular sample chamber to accommodate the slice. The acquisition times for MR images were 1 minute, 25 minutes and 8 minutes for gradient echo, spin echo and RARE 8 (rapid acquisition with relaxation enhancement) respectively. Though the commercial imaging unit is optimised for bigger sample size (30 mm inner diameter max), images with in-plane resolution of 30 ($\mu$m)$^{2}$ are recorded for a 3 mm liver slice of thickness 300~$\mu$m. Here we have presented preliminary results of imaging experiments. In future we aim to include a dedicated micro-imaging setup for better resolution to make metabolic profile maps by diffusion tensor imaging.
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 
\caption{MR images of a freshly cut live slice from a mouse. A: optical micrograph; B: Gradient echo image acquired in 1 minute; C: magnetic field map; D Spin echo image acquired in 30 minutes; E: RARE8 image acquired in 8 minutes.}
\label{fig:tisli} 
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
We have presented a novel modular NMR probe assembly for generic high sensitivity microfluidic NMR experiments. The probe is built from the readily accessible materials with no requirement of parts from commercial probes. The modularity of the probe enables to use different detectors tailored for specific experimental requirements on the same probe skeleton. The detector is made from easily available PCB materials. The use of PCB allows to modify the probe circuit and design without disturbing the probe geometry. The probe has excellent B$_1$ homogeneity and sensitivity. The resolution is reasonable for primary metabolic studies but needs to be improved for generic applications. The probe has already been used for various diverse experiments like reaction monitoring, protein structure determination, micro-imaging of mouse liver tissue slices, metabolic studies of mammalian cells, hyperpolarisation on the chip etc. Although in the current form the probe can be used for generic 2D experiments, in the future we intend to include extra channels for lock and pulses on other nuclei. Though, commercial gradient system has been successful to make micro images of mouse liver tissue slices, a dedicated gradient system can be included on the probe PCB for shimming and imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgement}
This research was funded through "Future and Emerging Technologies" (FETOPEN) call of the EU Horizon 2020 research framework. Authors would like to thank William Hale and Bishnubrata Patra for making microfluidic devices and help with the imaging experiments.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\bibliographystyle{plain}
\bibliography{science}
\end{document}

### 2018-12-19 ms5n17-tlp-mn-180216-001.tex
New figures

@@
 \begin{document}
-\title{Modular transmission line probes for microfluidic NMR}
+\title{Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging}
 \author[1]{Manvendra Sharma}
@@
 \begin{abstract}
-Microfluidic NMR (Nuclear Magnetic Resonance) presents the possibility of probing chemical or bio-chemical reactions, cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment.
-We present a dual channel modular probe assembly for  high efficiency microfluidic-NMR.
+Microfluidic NMR (Nuclear Magnetic Resonance) can probe chemical or bio-chemical reactions, including the metabolism of cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment.
+We present a dual-channel modular probe assembly for  high efficiency microfluidic-NMR.
 The samples are contained in exchangeable, flow compatible planar microfluidic devices.
-The detector including the tuning and matching circuitry of the probe is modular which allows the use of different detectors optimised for different experimental conditions on the same probe base.
-The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB materials.
+The detector including the tuning and matching circuitry of the probe is modular and allows the use of different detectors optimised for different experimental conditions on the same probe base.
+The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit borard) materials.
 The probe can be built from scratch with no requirement of any parts or electronics from commercial probes.
@@
 \maketitle
-%\clearpage
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Microfluidic lab-on-a-chip (LOC) devices are increasingly finding wide applications in chemistry and the life sciences~\cite{whitesides2006origins,mark2010microfluidic}.
-In addition to providing a way to integrate complex chemical and biochemical analytical processes with sample preparation and even culture of cells and other biological systems, they allow detailed control over growth conditions, and high experimental throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}.
-In general, information on the system under study is extracted from microfluidic devices by spectroscopic techniques at the end point of the experiment.
-This typically involves interrogation using fluorescent probes which bind to one or a few analytes of interest.
+In addition to providing a way to integrate complex chemical and biochemical analytical processes with sample preparation and even culture of cells and other biological systems, they allow detailed control over growth conditions, and offer high experimental throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}.
+In spite of its analytical power, NMR is rarely used in microfluidic systems.
+In general, information on the system under study is extracted from microfluidic devices by spectroscopic techniques at the end point of the experiment using fluorescent probes which bind to one or a few analytes of interest.
 This approach can reach very high sensitivity, with limits of detection down to femtomolar concentrations.
@@
 The small volumes involved in microfluidic systems (typically in the range of 1 $\mu$l) compound this problem.
-Fortunately, the mass limit of detection of Inductive NMR detectors tends to improve as they are scaled down~\cite{Olson1995}.
+Fortunately, the mass limit of detection of inductive NMR detectors tends to improve as they are scaled down~\cite{Olson1995}.
 On this basis, a number of different micro-NMR detector designs have been proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}.
@@
 A modular design ensures that detectors of different geometry and size can be easily exchanged.
-NMR detector (including the tuning and matching circuit) is connected to the probe skeleton through detachable connectors.
-Modularity of the probe not only allows fast optimisation of the detector but also different detectors optimised for different experimental conditions like mass sensitivity, concentration sensitivity, sample volume, single or dual channel etc can be used on a single probe base.
+The NMR detector (including the tuning and matching circuit) is connected to the probe skeleton through detachable connectors.
+Modularity of the probe not only allows fast optimisation of the detector but also different detectors optimised for different microfluidic device designs can be used on a single probe base.
 Using the same probe skeleton does not need any compromise of NMR sensitivity, resolution or microfluidic functionality.
@@
 Detailed construction drawings for the probe are provided in the supporting information.
-Planer design of the detector allows to use planar exchangeable microfluidic devices.
+Planar design of the detector allows to use planar exchangeable microfluidic devices.
 Microfluidic devices can be designed freely for specific experimental requirements as long as the overall shape of the device is maintained within l$\times$ w$\times$ t = 90mm$\times$ 20mm$\times$ 1mm.\par
-In the remainder of this paper, we discuss the probe design, and characterise its performance in terms of sensitivity and resolution.
+In the remainder of this paper, we discuss the probe design in more detail, and characterise its performance in terms of sensitivity and resolution.
 We also demonstrate its application in microfluidic cell culture, protein NMR spectroscopy, and micro-imaging.
-Using the same probe base does not need any compromise of NMR sensitivity, resolution or microfluidic functionality.
+Using the same probe base does not require any compromise of NMR sensitivity, resolution or microfluidic functionality.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\end{itemize}
+\begin{figure}
+\centering
+\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png} 
+\caption{Micrograph of the probe with and without the sleeve.}
+\label{fig:probe} 
+\end{figure}
 The probe assembly design is based on readily and easily available materials and parts with minimal requirement for fabrication of customised parts to avoid any bottlenecks in the building process.
 The probe can be built from scratch with no requirement of any part or electronics from commercial NMR probes.
-All the parts and electronics can be bought readily from commercial sources, with the exception of a small number of precision-machined parts which are used to hold the assembly together.
+All parts and electronic components are readily available from commercial sources, with the exception of a small number of precision-machined parts which are used to hold the assembly together.
 These can be ordered from commercial prototyping manufacturers or machined in-house if mechanical workshop facilities are available.\par
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181015-probe-explode.png} 
+\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
 \caption{Exploded view of he probe design (left) and assembled probe (right).
-Probe base (blue) and scaffold assembly (green) with base PCB (brown,8) makes a generic mounting point for the NMR detector (red).
+Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a generic mounting point for the NMR detector (red).
 A microfluidic device (1) can be inserted from the top of the probe.
-The device sits on a spacer (4) between the detector planes (3 and 5) having the sample chamber coinciding with the constriction of the PCB planes.
+The device is held in place by a spacer (4) between the detector planes (3 and 5) assuring alignment of the sample chamber with the constriction of the PCB planes.
 A modular PCB insert (6) can be exchanged to change the X channel frequency to $^{13}$C or $^{15}$N.
@@
 \end{figure}
-The skeleton of the probe consisting of a base (blue in~\ref{fig:probe-explode}) and a scaffold assembly (green in~\ref{fig:probe-explode}) made from standard aluminium profiles.
-The base is made from a prefabricated aluminium profile and contains the BNC connectors for RF (Radio Frequency) input.
-The scaffold assembly is made up of two aluminium tubes held together with precision machined parts (10).
-A base PCB (8) is put on the top of the probe skeleton held with the brass rods (9) for stability.
-The base PCB holds capacitors (7) for secondary tuning and matching of the resonator at the magnet and low-loss SMP connectors (11 in figure~\ref{fig:ProbePhoto}) to connect the rest of the probe.
-The probe skeleton with the base PCB serves as a generic mounting point for the NMR detector.
+The probe assembly can be divided into three main assemblies: A) probe base; B) scaffold assembly; C) detector assembly.
+The  base (blue in~\ref{fig:probe-explode}) and the scaffold assembly (green in~\ref{fig:probe-explode}) together make the skeleton of the probe.
+Both the base and scaffold assembly are made from standard aluminium profiles.
+The base contains the BNC connectors for RF (Radio Frequency) input.
+These BNC connectors are connected to semi-rigid coaxial cables for RF transport in the probe.\par
+The scaffold assembly is made up of two hollow aluminium tubes held together with precision machined parts (scaffold support disks (10)).
+The semi-rigid cables are threaded through these hollow aluminium tubes to reach the detector assembly .
+Additional auxiliary support disks made from 5 mm PMMA are used for better stability of the scaffold assembly.
+A tuning and matching PCB (8) is put on the top of the probe skeleton held with the detector support rods (9) and semi-rigid coaxial cables.
+Both conductors of the coaxial cables are connected to the tuning and matching PCB.
+The tuning and matching PCB holds capacitors (7) for secondary tuning and matching of the detector and low-loss SMP connectors (11 in figure~\ref{fig:ProbePhoto}) to connect the detector assembly.
+Secondary tuning and matching capacitors are used for fine tuning and matching of a detector at the magnet through tuning rods.
+The tuning and matching PCB provides a mechanical connection between capacitors (7) and tuning rods such that the detectors tuned to very different frequencies (100s of MHz apart) can be exchanged freely without disturbing the tuning and matching capacitors (7).
+The base, the scaffold assembly and, the tuning and matching PCB all have a free circular axial bore providing access from the bottom of the probe.
+A free access from the bottom can be used for temperature and environmental control inside the probe.\par
 The NMR detector is made up of two PCBs (3 and 5), a spacer between them (4) and an RF-insert (6).
-The PCBs (3 and 5) also carry the circuit electronics for the channel separation and primary tuning and matching of the detector.
-A copper or brass auxiliary disk (2) holds the PCB's together.
+The detector is based on a planar transmission line geometry as described before~\cite{gream_2016,stripline_jan}.
+In this geometry the detector is made from a planar copper strip.
+The width of the copper strip is larger at the ends and smaller in the middle making a constriction.
+Due to smaller width the current density and hence the sensitivity increases at the constriction.
+Both the PCBs (3 and 5) have the constriction geometry  and also carry the circuit electronics for the channel separation and primary tuning and matching of the detector.
+A copper or brass auxiliary disk (2) holds the PCBs together.
 The probe sheath (not shown here) is connected to the auxiliary disk (2) and the scaffold assembly through screws.
@@
 As the detector is connected to the probe base through detachable connectors, various detectors can be used on the same probe skeleton.
-The detectors are based on a transmission line design~\cite{gream_2016,stripline_jan}, and fabricated from easily accessible PCB materials.
+The detectors are fabricated from easily accessible PCB materials.
 Use of PCB to manufacture the detector allows for easy optimisation of detector dimensions for several applications compared to other manufacturing methods.
-A detector can be optimised for mass sensitivity, concentration sensitivity, resolution, sample volume, single or dual channel etc for required application.\par
+Example of different detectors can be detectors tuned to different resonance frequencies or detectors with customised constriction geometries for different microfluidic devices.\par
 \begin{figure}
 \centering
-\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
+\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
 \caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel.
@@
 \end{figure}
-Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) for X channel.
-In (A) X channel could be tuned to different nuclei by exchanging 6.
+Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) for the X channel.
+In (A) the X channel can be tuned to different nuclei by exchanging 6.
 However, in (B) the circuitry of the RF insert (6) is manufactured on the PCB plane (5).
-Inclusion of the circuitry of 6 on 5 makes the design compact.
+Inclusion of the circuitry of 6 on 5 makes the design more compact.
 Probe (A) is compatible with Varian 600 ultra shield 14.1 T magnet having an outer diameter (O.D.) of 44.45 mm including the sheath.
-Probe (B) has an outer diameter (O.D.) of 38 mm including the sheath and hence can be used with a narrow bore magnet.
-Naturally, B can also be used with wide bore magnets with spacers or gradient stack to keep the probe centred .
-As already mentioned, the cost and time of making a new PCB is minimal so, different detectors could be made for different X channel frequencies.\par
+Probe (B), with an outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a Bruker narrow bore shim stack.
+Probe (B) also fits inside a Bruker micro-imaging gradient unit.
+Naturally, B can also be used with wide bore magnets with spacers or gradient stack to keep the probe centred .\par
 The microfluidic devices are made from thermally bonded PMMA sheets.
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png} 
 \caption{Microfluidic devices for different applications compatible with the current setup.
@@
 The circuit for a double resonance probe is based on design shown in figure~\ref{fig:circuit}.
-Dimensions of the detector were chosen for a $\lambda/2$ standing wave at frequency few 100s MHz higher than the proton larmor frequency.
-The resonator can then be tuned to desired frequency by applying additional capacitance at the resonator.
-For the X channel the detector is used as a load with the other circuit elements.
-The detector is connected to the secondary T\&M capacitors with the transmission lines on the PCB planes.
-As all the circuit elements are assembled on the PCB planes, the transmission lines on the PCB have lengths similar to detector.
+Dimensions of the detector were calculated from the simulations described in~\cite{gream_2016}.
+However, the size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger sample volumes for some cases.
+The detector is tuned to proton larmor frequency of protons.
+Primary tuning of the detector is performed through the circuit elements.
+The detector is connected to the secondary tuning and matching capacitors with the transmission lines on the PCB planes.
+As all the circuit elements are assembled on the PCB planes, the transmission lines on the PCB have lengths similar to the detector.
 Hence transmission lines may become a part of the resonance circuit and can severely affect the probe performance.
 To avoid this problem a series capacitor was included with the transmission line just before the detector to adjust the impedance of transmission line to 50~$\Omega$.
-In this situation the detector is matched by the transmission line and secondary T\&M capacitors can be used for fine tuning and matching.\par
+In this situation the detector is matched by the transmission line and secondary tuning and matching capacitors can be used for fine tuning and matching.\par
 \begin{figure}
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
 \caption{Circuit diagram of the double resonance probe. Proton frequency is feed in from the left (port 2) and X frequency is feed in from right (port 7).}
@@
 Circuits LTD (Wigston , UK) to manufacture the PCBs.
-Easily and inexpensively available FR4 was used for PCB manufacturing (figure~\ref{fig:ProbePhoto} A) but inhomogeneities were observed in B${_0}$ field images for this material.
-Rogers RO35 from rogers corporation was later used for PCBs (figure~\ref{fig:ProbePhoto} B).\par
+Easily and inexpensively available FR4 was used for PCB manufacturing for (figure~\ref{fig:ProbePhoto} A).
+Rogers RO35 from rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par
 The probe skeleton was assembled by holding the prefab aluminium profiles with precision-machined parts and screws.
@@
 Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}.
-All the samples were purchased from commercial sources and were used without further purification.\par
+Sodium acetate and $^{15}$N labeled urea were purchased from Merek and Dulbecco Modified Eagle?s Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
 Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet.
@@
 As already explained, the X channel tuning frequency can be changed by simply exchanging an rf-insert or the complete detector.
-Figure~\ref{fig:tandm} shows the measured T\&M curves at different proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz) corresponding to the larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively.
+Figure~\ref{fig:tandm} shows the measured tuning and matching curves at different proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz) corresponding to the larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively.
 The measurement were performed in the pairs of 600 MHz and 60 MHz and, 500 MHz and 125 MHz.
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
 \caption{Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 60 MHz ($^{15}$N frequency at 14 T) and, 125 MHz ($^{13}$C frequency at  and 11.7 T).
@@
 RF field is highly homogeneous with 810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% at 600~MHz.
-The probe can generate 100 kHz RF-field for an input power of 100 watts both at 600 MHz and 500 MHz corresponding to RF field efficiency of 10 kHz watts$^{-1/2}$ .
+The probe can generate 100 kHz RF-field for an input power of 100 W both at 600 MHz and 500 MHz corresponding to RF field efficiency (B$_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$ .
 $^{15}$N nutation detected on protons for the same sample is shown in figure~\ref{fig:15N-nutation}.
-An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$ measurements.\par
+An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N with 100 W power and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$C with measurements.\par
 \begin{figure}
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png} 
 \caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz.
 The 810$^{\circ}$/90$^{\circ}$ ratio is more than 90\% at 600~MHz.
-The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 Watts.
+The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 W.
 Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz}
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
 \caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.}
@@
 Carbon satellites can be seen well above noise level.
-The orange curve corresponds to a lorentzian lineshape with full width at half maximum of 3.35 Hz.
+The orange curve corresponds to a Lorentzian lineshape with full width at half maximum of 3.35 Hz.
 Limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ is  1.18 nmol s$^{1/2}$ at 600 MHz for the acetate sample.
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/lineshape.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/lineshape.png} 
 \caption{Spectrum of 130 mM sodium acetate dissolved in water acquired in 32 scans with water presaturation.
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png} 
 \caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 
 \caption{$^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14 T.
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 
 \caption{MR images of a freshly cut live slice from a mouse.
@@
 \end{figure}
+Although FR4 is a cheap and quickly available material, inhomogeneities were observed in B$_0$ field images made from this PCBs.
+Better resolution can be achieved using Rogers RO35 from rogers corporation.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \clearpage
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{science}

### 2018-12-20 ms5n17-tlp-mn-180216-001.tex
Need help for results

@@
 Easily and inexpensively available FR4 was used for PCB manufacturing for (figure~\ref{fig:ProbePhoto} A).
-Rogers RO35 from rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par
+Rogers RO3035 from rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par
 The probe skeleton was assembled by holding the prefab aluminium profiles with precision-machined parts and screws.
@@
 \end{figure}
-Although FR4 is a cheap and quickly available material, inhomogeneities were observed in B$_0$ field images made from this PCBs.
-Better resolution can be achieved using Rogers RO35 from rogers corporation.
+Initially FR4 PCB material was used to make detector assembly because of its low cost and easy availability.
+B$_0$ field maps of the sample chamber generated from gradient echo images using these detectors showed inhomogeneities in the B$_0$ field.
+To avoid inhomogeneities and therefore to achieve better resolution, detectors were made from RO3035 material from Rogers corporation.
+Though RO3035 provides better resolution it is more expensive and takes longer to obtain compared to FR4.
+A new detector design can first be tested using FR4 material and the optimised design can be made from RO3035.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-12-20 ms5n17-tlp-mn-180216-001.tex
V3 corrections fixed

@@
 The detector including the tuning and matching circuitry of the probe is modular and allows the use of different detectors optimised for different experimental conditions on the same probe base.
-The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit borard) materials.
-The probe can be built from scratch with no requirement of any parts or electronics from commercial probes.
-The probe has a limit of detection of 1.18 nmol s$^{-1/2}$ and excellent B$_{1}$ homogeneity.
+The complete probe can be built from easily available parts.
+The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit board) materials.
+The probe has a limit of detection of 1.18 nmol s$^{-1/2}$, resolution of 3.35 Hz and, excellent B$_{1}$ homogeneity.
 The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel ($^{13}$C or $^{15}$N) frequencies.
@@
 Planar design of the detector allows to use planar exchangeable microfluidic devices.
-Microfluidic devices can be designed freely for specific experimental requirements as long as the overall shape of the device is maintained within l$\times$ w$\times$ t = 90mm$\times$ 20mm$\times$ 1mm.\par
+Microfluidic devices can be designed freely for specific experimental requirements as long as the overall shape of the device is maintained within l$\times$w$\times$t = 90mm$\times$20mm$\times$1mm.\par
 In the remainder of this paper, we discuss the probe design in more detail, and characterise its performance in terms of sensitivity and resolution.
@@
 \caption{Exploded view of he probe design (left) and assembled probe (right).
-Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a generic mounting point for the NMR detector (red).
+Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a generic mounting point for the NMR detector assembly(red).
 A microfluidic device (1) can be inserted from the top of the probe.
@@
 Modular NMR detector is made up of parts 3 to 6 and is connected to the base plate PCB (8) through detachable SMP connectors.
-Top shows a photograph of the PCB plane 3 having stripline geometry and pads for circuit elements and SMP connectors for RF insert 6.
-}
+The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) and, auxiliary support disks (12).}
 \label{fig:probe-explode} 
 \end{figure}
-The probe assembly can be divided into three main assemblies: A) probe base; B) scaffold assembly; C) detector assembly.
-The  base (blue in~\ref{fig:probe-explode}) and the scaffold assembly (green in~\ref{fig:probe-explode}) together make the skeleton of the probe.
+The probe assembly can be divided into three main assemblies: A) probe base; B) scaffold assembly; C) detector assembly(figure~\ref{fig:probe}).
+The  base (blue in figure~\ref{fig:probe-explode}) and the scaffold assembly (green in figure~\ref{fig:probe-explode}) together make the skeleton of the probe.
 Both the base and scaffold assembly are made from standard aluminium profiles.
@@
 These BNC connectors are connected to semi-rigid coaxial cables for RF transport in the probe.\par
-The scaffold assembly is made up of two hollow aluminium tubes held together with precision machined parts (scaffold support disks (10)).
+The scaffold assembly is made up of two hollow aluminium tubes (11) held together with precision machined parts (scaffold support disks (10)).
 The semi-rigid cables are threaded through these hollow aluminium tubes to reach the detector assembly .
-Additional auxiliary support disks made from 5 mm PMMA are used for better stability of the scaffold assembly.
+Additional auxiliary support disks (12) made from 5 mm poly (methyl methacrylate) (PMMA) are used for better stability of the scaffold assembly.
 A tuning and matching PCB (8) is put on the top of the probe skeleton held with the detector support rods (9) and semi-rigid coaxial cables.
 Both conductors of the coaxial cables are connected to the tuning and matching PCB.
-The tuning and matching PCB holds capacitors (7) for secondary tuning and matching of the detector and low-loss SMP connectors (11 in figure~\ref{fig:ProbePhoto}) to connect the detector assembly.
-Secondary tuning and matching capacitors are used for fine tuning and matching of a detector at the magnet through tuning rods.
-The tuning and matching PCB provides a mechanical connection between capacitors (7) and tuning rods such that the detectors tuned to very different frequencies (100s of MHz apart) can be exchanged freely without disturbing the tuning and matching capacitors (7).
+The tuning and matching PCB holds capacitors (7) for secondary tuning and matching of the detector and low-loss SMP connectors (14 in figure~\ref{fig:ProbePhoto}) to connect the detector assembly.
+Secondary tuning and matching capacitors are used for fine tuning and matching of a detector at the magnet through tuning rods(13).
+The tuning and matching PCB provides a mechanical connection between capacitors (7) and tuning rods (13) such that the detectors tuned to very different frequencies (100s of MHz apart) can be exchanged freely on the same probe skeleton without disturbing the tuning and matching circuit.
 The base, the scaffold assembly and, the tuning and matching PCB all have a free circular axial bore providing access from the bottom of the probe.
@@
 The width of the copper strip is larger at the ends and smaller in the middle making a constriction.
-Due to smaller width the current density and hence the sensitivity increases at the constriction.
+Due to smaller width at the constriction the current density and hence the sensitivity increases.
 Both the PCBs (3 and 5) have the constriction geometry  and also carry the circuit electronics for the channel separation and primary tuning and matching of the detector.
@@
 of 44.45 mm, in B, circuit elements of X channel are integrated on the PCB itself making it compact (38 mm O.D.).
-Detachable SMP connectors (11) are used to connect the RF insert (6) and also the assembled NMR detector.
+Detachable SMP connectors (14) are used to connect the RF insert (6) and also the assembled NMR detector.
 The cost and effort to make a new detector are minimal so, various detectors could be made for various X channel frequencies.}
@@
 A flow can be introduced from the inlet and outlet of the device for flow studies or sample exchange.
-The fluidic network on the device can be made freely with the only constrained on the overall size of the device [l $\times$ w $\times$ t = 90 mm $\times$ 20mm $\times$ 1mm].
+The fluidic network on the device can be made freely with the only constrained on the overall size of the device.
 Other layers can be employed to allow parallel flow as long as the total thickness remains below 1mm.\par
@@
 The circuit for a double resonance probe is based on design shown in figure~\ref{fig:circuit}.
-Dimensions of the detector were calculated from the simulations described in~\cite{gream_2016}.
-However, the size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger sample volumes for some cases.
-The detector is tuned to proton larmor frequency of protons.
-Primary tuning of the detector is performed through the circuit elements.
+The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger sample volumes for some cases.
+Primary tuning of the detector is performed through the circuit elements (mainly C$_6$).
 The detector is connected to the secondary tuning and matching capacitors with the transmission lines on the PCB planes.
@@
 Hence transmission lines may become a part of the resonance circuit and can severely affect the probe performance.
-To avoid this problem a series capacitor was included with the transmission line just before the detector to adjust the impedance of transmission line to 50~$\Omega$.
+To avoid this problem a series capacitor (C$_5$) was included with the transmission line just before the detector to adjust the impedance of transmission line to 50~$\Omega$.
 In this situation the detector is matched by the transmission line and secondary tuning and matching capacitors can be used for fine tuning and matching.\par
@@
 All the parts and the probe assembly were designed and simulated on Solidworks (Solidworks, Dassault Syst\`{e}mes).
-The prefabricated aluminium profiles (base platform, scaffold aluminium tube, probe sleeve) were made from 6061-T3 alloy and were obtained from Aluminum Warehouse, UK to build the probe skeleton.
+The prefabricated aluminium profiles (base platform, scaffold aluminium tubes, probe sleeve) were made from 6061-T3 alloy and were obtained from Aluminum Warehouse, UK to build the probe skeleton.
 A few customised precision-machined parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford, UK) after providing CAD files.
-A small number parts were machined in-house (brass support rods, auxiliary support disks).
+A small number parts were machined in-house (detector support rods, auxiliary support disks).
 All the electronic components and the semi rigid transmission lines were purchased from Digikey.
-Cell cast poly (methyl methacrylate) (PMMA) sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK).
+Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK).
 Microfluidic devices were designed on AutoCAD.
@@
 Easily and inexpensively available FR4 was used for PCB manufacturing for (figure~\ref{fig:ProbePhoto} A).
-Rogers RO3035 from rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par
-The probe skeleton was assembled by holding the prefab aluminium profiles with precision-machined parts and screws.
+RO3035 from Rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par
+The probe skeleton was assembled by holding the prefabricated aluminium profiles with precision-machined parts and screws.
 Semi-rigid transmission lines were then threaded through the skeleton.
@@
 Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}.
-Sodium acetate and $^{15}$N labeled urea were purchased from Merek and Dulbecco Modified Eagle?s Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
+Sodium acetate and $^{15}$N labeled urea were purchased from Merek and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
 Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet.
@@
 The current probe can be simultaneously operated at 2 frequencies.
-The probe has been tuned to protons and one X channel ($^{13}$C or $^{15}$N) frequencies at a time.
+The probe can be tuned to protons and one X channel ($^{13}$C or $^{15}$N) frequencies at a time.
 As already explained, the X channel tuning frequency can be changed by simply exchanging an rf-insert or the complete detector.
 Figure~\ref{fig:tandm} shows the measured tuning and matching curves at different proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz) corresponding to the larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively.
-The measurement were performed in the pairs of 600 MHz and 60 MHz and, 500 MHz and 125 MHz.
+The measurements were performed in the pairs of 600 MHz and 60 MHz and, 500 MHz and 125 MHz.
 The loaded Q factors are 42, 49, 32, 36 at 600 MHz, 500 MHz, 125 MHz and, 60 MHz respectively.
@@
 \end{figure}
+Initially FR4 PCB material was used to make detector assembly because of its low cost and easy availability.
+B$_0$ field maps of the sample chamber generated from gradient echo images using these detectors showed inhomogeneities in the B$_0$ field.
+To avoid inhomogeneities and therefore to achieve better resolution, detectors were made from RO3035 material from Rogers corporation.
+Though RO3035 provides better resolution it is more expensive and takes longer to obtain compared to FR4.
+A new detector design can first be tested using FR4 material and the optimised design can be made from RO3035.\par
 $^1$H nutation diagram of water peak for a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz is shown figure~\ref{fig:1H-nutation}.
@@
 $^{15}$N nutation detected on protons for the same sample is shown in figure~\ref{fig:15N-nutation}.
-An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N with 100 W power and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$C with measurements.\par
+An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$C with measurements.
+The power used at the X channel was more than 100 W still no signs of arcing were observed in the NMR spectrum.\par
 \begin{figure}
@@
 \end{figure}
-Figure~\ref{fig:lineshape} shows a spectrum of 130 mM Na-acetate dissolved in H$_2$O acquired after water presaturation at 600 MHz with 32 averages.
+Figure~\ref{fig:lineshape} shows a spectrum of 130 mM Na-acetate peak dissolved in H$_2$O acquired after water presaturation at 600 MHz with 32 averages.
 The figure in the inset shows expanded view of the base of the acetate peak.
@@
 Here we have presented preliminary results of imaging experiments.
-In future we aim to include a dedicated micro-imaging setup for better resolution to make metabolic profile maps by diffusion tensor imaging.
+In future we aim to include a dedicated micro-imaging setup for better resolution to make metabolic profile maps by diffusion tensor imaging.\par
 \begin{figure}
@@
 \end{figure}
-Initially FR4 PCB material was used to make detector assembly because of its low cost and easy availability.
-B$_0$ field maps of the sample chamber generated from gradient echo images using these detectors showed inhomogeneities in the B$_0$ field.
-To avoid inhomogeneities and therefore to achieve better resolution, detectors were made from RO3035 material from Rogers corporation.
-Though RO3035 provides better resolution it is more expensive and takes longer to obtain compared to FR4.
-A new detector design can first be tested using FR4 material and the optimised design can be made from RO3035.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This research was funded through "Future and Emerging Technologies" (FETOPEN) call of the EU Horizon 2020 research framework.
-Authors would like to thank William Hale and Bishnubrata Patra for making microfluidic devices and help with the imaging experiments.
+Authors would like to thank William Hale and Bishnubrata Patra for making microfluidic devices and Dr.
+Katrin Deinhardt from Department of Biological Science at UoS, for the mouse liver tissue..
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-12-25 ms5n17-tlp-mn-180216-001.tex
wording changes in introduction

@@
 %\end{itemize}
-NMR (Nuclear Magnetic Resonance) is a well established technique used in chemical analysis~\cite{NMR-chemical-1995, hills1994magnetic, rabenstein1991quantitative}, metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, molecular structure determination~\cite{wuthrich1990protein}, reaction monitoring~\cite{maiwald2004quantitative} etc.
-Microfluidic lab-on-a-chip (LOC) devices are increasingly finding wide applications in chemistry and the life sciences~\cite{whitesides2006origins,mark2010microfluidic}.
-In addition to providing a way to integrate complex chemical and biochemical analytical processes with sample preparation and even culture of cells and other biological systems, they allow detailed control over growth conditions, and offer high experimental throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}.
-In spite of its analytical power, NMR is rarely used in microfluidic systems.
-In general, information on the system under study is extracted from microfluidic devices by spectroscopic techniques at the end point of the experiment using fluorescent probes which bind to one or a few analytes of interest.
-This approach can reach very high sensitivity, with limits of detection down to femtomolar concentrations.
-However, it is usually destructive, since the sample is affected by the addition of the marker, and can only be done once, at the end of the experiment.
-Following kinetic processes therefore requires using multiple samples.
-By contrast, NMR spectroscopy is non-invasive, generic (virtually all organic molecules give an NMR signal), and highly specific (no two metabolites share the same NMR spectrum).
-For these reasons, NMR spectroscopy could provide a useful complementary readout capability for microfluidic devices.
-For example, the metabolic activity of a cell culture sample can be followed non-invasively by NMR throughout the course of the experiment, while effects on cell differentiation can still be analysed by a (destructive) transcriptomic analysis at the end.
-Unfortunately, the sensitivity of NMR is much lower than that of optical techniques.
-The small volumes involved in microfluidic systems (typically in the range of 1 $\mu$l) compound this problem.
-Fortunately, the mass limit of detection of inductive NMR detectors tends to improve as they are scaled down~\cite{Olson1995}.
-On this basis, a number of different micro-NMR detector designs have been proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}.
-In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline coils~\cite{stripline_jan}.
-While significant research has gone into developing micro-NMR detectors for flow probes, only a few designs that allow insertion of a generic microfluidic device into the detector have been described.\par
-In this paper we present a novel modular probe designed for generic microfluidic-NMR experiments.
-The design is based on a transmission line detector~\cite{stripline_jan,gream_2016}, which is realised using inexpensive printed circuit board (PCB) technology.
-A modular design ensures that detectors of different geometry and size can be easily exchanged.
-The NMR detector (including the tuning and matching circuit) is connected to the probe skeleton through detachable connectors.
-Modularity of the probe not only allows fast optimisation of the detector but also different detectors optimised for different microfluidic device designs can be used on a single probe base.
-Using the same probe skeleton does not need any compromise of NMR sensitivity, resolution or microfluidic functionality.
-The cost of an additional detector is only $\sim$200 $\geneuro$ and can be manufactured within 2-3 days.
+NMR (Nuclear Magnetic Resonance) is a well established technique used in chemical 
+analysis~\cite{NMR-chemical-1995, hills1994magnetic, rabenstein1991quantitative}, 
+metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, molecular 
+structure determination~\cite{wuthrich1990protein}, reaction 
+monitoring~\cite{maiwald2004quantitative} etc. Microfluidic lab-on-a-chip (LOC) devices 
+are increasingly finding applications in chemistry and the life 
+sciences~\cite{whitesides2006origins,mark2010microfluidic}. 
+They provide a convenient way to integrate complex chemical and biochemical processes. 
+In particular, microfluidic technology allows detailed control over growth conditions 
+in the culture of cells, cell aggregates, and small organisms. 
+Lab-on-a-chip devices can also enable high experimental 
+throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. 
+In spite of its analytical power, NMR has so far only rarely been used in microfluidic 
+systems. In general, information is extracted from microfluidic devices by spectroscopic 
+techniques at the end point of the experiment. Typically, 
+this is done using fluorescent probes, which bind to one or a few analytes of interest. 
+This approach can reach very high sensitivity, with limits of detection down to 
+femtomolar concentrations. However, it is usually destructive, since the sample is 
+affected by the addition of the marker, and can only be done once, at the end of the 
+experiment. Following kinetic processes therefore requires using multiple samples. By 
+contrast, NMR spectroscopy is non-invasive, generic (virtually all organic 
+molecules give an NMR signal), and highly specific (no two metabolites share 
+the same NMR spectrum).
+
+NMR spectroscopy can provide a useful complementary readout capability 
+for microfluidic devices. For example, the metabolic activity of cell cultures 
+can be followed non-invasively by NMR throughout the course of the experiment, 
+while effects on cell differentiation can still be analysed by a (destructive) 
+transcriptomic analysis at the end. Unfortunately, the sensitivity 
+of NMR is much lower than that of optical techniques. 
+The small volumes involved in microfluidic systems
+ (typically in the range of 1~$\mu$l) 
+compound this problem. As is well known, the mass limit of detection of 
+inductive NMR detectors improves as they are scaled down~\cite{Olson1995}. 
+On this basis, a number of different micro-NMR detector designs have been 
+proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. 
+In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, 
+planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline 
+detectors~\cite{stripline_jan}. 
+Significant research has gone into developing micro-NMR detectors for flow probes, 
+where the sample container takes the form of a fixed capillary into which the sample
+must be injected. Only a few designs that allow insertion of a removable microfluidic 
+device into the detector have been described [REF Graeme, Spengler, Korvink et al].
+
+In this paper we present a novel modular probe designed for generic 
+microfluidic-NMR experiments. The design is based on a transmission line 
+detector~\cite{stripline_jan,gream_2016} using inexpensive 
+printed circuit board (PCB) technology. A modular design ensures that detectors of 
+different geometry and size can be easily exchanged. 
+The NMR detector (including the tuning and matching circuit) is connected to the probe 
+skeleton through detachable connectors. Modularity of the probe not only allows 
+fast optimisation of the detector but also facilitates the use of dedicated detectors 
+for different microfluidic devices on a single probe base. 
+Once thw probe base is in place, additional detectors can be manufactured 
+within 2-3 days for less than $\sim$200 $\geneuro$. 
 The probe is designed for proton detected double resonance. 
-The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or $^{31}$P.
-The probe skeleton is designed entirely from easily obtainable raw materials such as aluminium profiles and tubes of standard size, with a small number of custom-machined parts holding the structure together.
-Detailed construction drawings for the probe are provided in the supporting information.
-Planar design of the detector allows to use planar exchangeable microfluidic devices.
-Microfluidic devices can be designed freely for specific experimental requirements as long as the overall shape of the device is maintained within l$\times$w$\times$t = 90mm$\times$20mm$\times$1mm.\par
-In the remainder of this paper, we discuss the probe design in more detail, and characterise its performance in terms of sensitivity and resolution.
-We also demonstrate its application in microfluidic cell culture, protein NMR spectroscopy, and micro-imaging.
-Using the same probe base does not require any compromise of NMR sensitivity, resolution or microfluidic functionality.
+The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or 
+$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials 
+such as aluminium profiles of standard size, with only a small number of 
+custom-machined parts holding the structure together. 
+Detailed construction drawings for the probe are provided in the supporting 
+information, and a complete set of CAD files is available for download at [...].
+The planar geometry of the detector accommodates exchangeable microfluidic devices 
+which can be designed freely for specific experimental requirements as long as the 
+overall shape of the device is maintained.
+
+In the remainder of this paper, we discuss the probe design in more detail, 
+and characterise its performance in terms of sensitivity and resolution. 
+We also demonstrate its application in microfluidic cell culture, 
+protein NMR spectroscopy, and micro-imaging. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{figure}
-The probe assembly design is based on readily and easily available materials and parts with minimal requirement for fabrication of customised parts to avoid any bottlenecks in the building process.
-The probe can be built from scratch with no requirement of any part or electronics from commercial NMR probes.
-All parts and electronic components are readily available from commercial sources, with the exception of a small number of precision-machined parts which are used to hold the assembly together.
-These can be ordered from commercial prototyping manufacturers or machined in-house if mechanical workshop facilities are available.\par
+The probe assembly design is based on readily and easily available materials and parts 
+with minimal need for fabrication of customised parts to avoid any bottlenecks in the 
+building process. The probe can be built from scratch with no requirement of any part 
+or electronics from commercial NMR probes. 
+All parts and electronic components are readily available from commercial sources, 
+with the exception of a small number of precision-machined parts which are used 
+to hold the assembly together. These can be ordered from commercial prototyping 
+manufacturers or machined in-house if mechanical workshop facilities are available.
+
 \begin{figure}
@@
 \caption{Exploded view of he probe design (left) and assembled probe (right). 
-Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a generic mounting point for the NMR detector assembly(red).
+Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a 
+generic mounting point for the NMR detector assembly(red). 
 A microfluidic device (1) can be inserted from the top of the probe. 
-The device is held in place by a spacer (4) between the detector planes (3 and 5) assuring alignment of the sample chamber with the constriction of the PCB planes.
-A modular PCB insert (6) can be exchanged to change the X channel frequency to $^{13}$C or $^{15}$N.
-Modular NMR detector is made up of parts 3 to 6 and is connected to the base plate PCB (8) through detachable SMP connectors.
-The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) and, auxiliary support disks (12).}
+The device is held in place by a spacer (4) between the detector planes (3 and 5) 
+ensuring alignment of the sample chamber with the sensitive area on the PCB planes. 
+The X channel frequency is controlled by a 
+modular PCB insert (6). The modular NMR detector is made up of parts 3 to 6 and is 
+connected to the base plate PCB (8) through standard coaxial (SMP) connectors. 
+The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) 
+and, auxiliary support disks (12).}
 \label{fig:probe-explode} 
 \end{figure}
-The probe assembly can be divided into three main assemblies: A) probe base; B) scaffold assembly; C) detector assembly(figure~\ref{fig:probe}).
-The  base (blue in figure~\ref{fig:probe-explode}) and the scaffold assembly (green in figure~\ref{fig:probe-explode}) together make the skeleton of the probe.
+
+The probe is composed of three main assemblies: A) probe base; B) scaffold assembly; 
+C) detector assembly (figure~\ref{fig:probe}). 
+The  base (blue in figure~\ref{fig:probe-explode}) and the scaffold assembly 
+(green in figure~\ref{fig:probe-explode}) together make the skeleton of the probe. 
 Both the base and scaffold assembly are made from standard aluminium profiles. 
 The base contains the BNC connectors for RF (Radio Frequency) input. 
-These BNC connectors are connected to semi-rigid coaxial cables for RF transport in the probe.\par
-The scaffold assembly is made up of two hollow aluminium tubes (11) held together with precision machined parts (scaffold support disks (10)).
-The semi-rigid cables are threaded through these hollow aluminium tubes to reach the detector assembly .
-Additional auxiliary support disks (12) made from 5 mm poly (methyl methacrylate) (PMMA) are used for better stability of the scaffold assembly.
-A tuning and matching PCB (8) is put on the top of the probe skeleton held with the detector support rods (9) and semi-rigid coaxial cables.
-Both conductors of the coaxial cables are connected to the tuning and matching PCB.
-The tuning and matching PCB holds capacitors (7) for secondary tuning and matching of the detector and low-loss SMP connectors (14 in figure~\ref{fig:ProbePhoto}) to connect the detector assembly.
-Secondary tuning and matching capacitors are used for fine tuning and matching of a detector at the magnet through tuning rods(13).
-The tuning and matching PCB provides a mechanical connection between capacitors (7) and tuning rods (13) such that the detectors tuned to very different frequencies (100s of MHz apart) can be exchanged freely on the same probe skeleton without disturbing the tuning and matching circuit.
-The base, the scaffold assembly and, the tuning and matching PCB all have a free circular axial bore providing access from the bottom of the probe.
-A free access from the bottom can be used for temperature and environmental control inside the probe.\par
-The NMR detector is made up of two PCBs (3 and 5), a spacer between them (4) and an RF-insert (6).
-The detector is based on a planar transmission line geometry as described before~\cite{gream_2016,stripline_jan}.
-In this geometry the detector is made from a planar copper strip.
-The width of the copper strip is larger at the ends and smaller in the middle making a constriction.
-Due to smaller width at the constriction the current density and hence the sensitivity increases.
-Both the PCBs (3 and 5) have the constriction geometry  and also carry the circuit electronics for the channel separation and primary tuning and matching of the detector.
-A copper or brass auxiliary disk (2) holds the PCBs together.
-The probe sheath (not shown here) is connected to the auxiliary disk (2) and the scaffold assembly through screws.
+These BNC connectors are connected to semi-rigid coaxial cables for 
+RF transport in the probe.
+
+The scaffold assembly is made up of two hollow aluminium tubes (11) held together with 
+precision machined parts at either end(scaffold support disks (10)). 
+The semi-rigid cables are  threaded through these hollow aluminium tubes 
+to reach the detector assembly. 
+Auxiliary support disks (12) provide additional rigidity for the scaffold assembly. 
+In our case, these were laser cut from 5~mm thick PMMA sheets, 
+but they may also be made by conventional machining.
+A tuning and matching PCB (TMPCB, 8) is held in place on the top of the probe skeleton by
+the detector support rods (9), with the semi-rigid coaxial cables providing
+additional support.
+The TMPCB is permantly fixed to the probe base, and serves as attachment point
+for the exchangeable detector assembly. It also provides 
+capacitors (7) for secondary tuning and matching.
+The detector assembly is connected to through a pair of
+low-loss SMP connectors (14 in figure~\ref{fig:ProbePhoto}).
+While each detector assembly is roughly
+tuned and matched with fixed circuit elements soldered onto it,
+the adjustable capacitors on the TMPCB are used for 
+fine tuning and matching 
+at the magnet through tuning rods (13) which reach all the way to the probe base.
+
+The base, the scaffold assembly and the tuning and matching PCB all have a free circular 
+axial bore providing access from the bottom of the probe, which can be used for 
+temperature and environmental control and/or fluidic connections to the sample as
+needed.
+The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an 
+RF-insert (6). The detector used here is based on a planar transmission line geometry 
+as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
+coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
+The transmission line detector consists of a pair of copper 
+planes each with a constriction at the centre.  This geometry gives rise to an 
+electromagnetic eigenmode with a strong anti-node of the magetic field between
+the two planes at the site of the constriction. This concentrates the rf field 
+and the detection snsitivity
+onto the sample area. 
+The shape and size of the copper structures have been chosen such as to produce
+an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
+solder points at the back side for chip capacitors; these can be used to tune the
+resonance to the desired proton Larmor frequency (500 or 600~MHz in the present case).
+Both the PCBs (3 and 5) also carry circuitry for the channel separation and primary 
+tuning and matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
+together. 
+The probe sheath (not shown here) is connected to the auxiliary disk (2) 
+and the scaffold assembly through screws. 
 An exchangeable microfluidic device (1) can be inserted from the top of the detector. 
-A microfluidic device can be filled with a sample before putting it in the probe or the device can be put in the probe with some fluidic connectors attached to fill or exchange the sample in-situ.
-The microfluidic device sits on the spacer between the two PCB planes coinciding the sample chamber with the constriction on the detector.
-RF-insert (6) can be exchanged to tune and match the probe to different frequencies at X channel.
-As the detector is connected to the probe base through detachable connectors, various detectors can be used on the same probe skeleton.
-The detectors are fabricated from easily accessible PCB materials.
-Use of PCB to manufacture the detector allows for easy optimisation of detector dimensions for several applications compared to other manufacturing methods.
-Example of different detectors can be detectors tuned to different resonance frequencies or detectors with customised constriction geometries for different microfluidic devices.\par
+Microfluidic devices can be used as passive sample holders, filled before putting them
+into the probe,
+or the device can be actively perfused and operated in-situ, with fluidic connections 
+attached inside the magnet. The microfluidic device is held in place by the spacer 
+between the two PCB planes coinciding the sample chamber with the constriction on the 
+detector.  The 45-degree edges of the device outline help with precise and reliable
+alignment.
+
+The RF-insert (6) can be exchanged to tune and match the probe to different frequencies 
+at the X channel. As the detector is connected to the probe base through detachable 
+connectors, various detectors can be used on the same probe skeleton. 
+Using standard PCB processes to manufacture the detector provides great flexibility
+to optimise detector performance for different applications, including different
+microfluidic sample sizes, and different combinations of target nuclei.
+\par
 \begin{figure}

### 2018-12-31 ms5n17-tlp-mn-180216-001.tex
wording changes
Almost finished...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\todo}[1]{{\color{red}\textbf{#1}}}
+\newcommand{\fig}[1]{Fig.~\ref{#1}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 must be injected. Only a few designs that allow insertion of a removable microfluidic 
-device into the detector have been described [REF Graeme, Spengler, Korvink et al].
+device into the detector have been described \todo{REF Graeme, Spengler, Korvink et al}.
 
@@
 The probe assembly design is based on readily and easily available materials and parts 
-with minimal need for fabrication of customised parts to avoid any bottlenecks in the 
-building process. The probe can be built from scratch with no requirement of any part 
-or electronics from commercial NMR probes. 
-All parts and electronic components are readily available from commercial sources, 
+with minimal need for customised fabrication.
+All mechanical and electronic components are readily available from commercial sources, 
 with the exception of a small number of precision-machined parts which are used 
-to hold the assembly together. These can be ordered from commercial prototyping 
+to hold the assembly together. These can be ordered from commercial prototvaiyping 
 manufacturers or machined in-house if mechanical workshop facilities are available.
@@
 The transmission line detector consists of a pair of copper 
-planes each with a constriction at the centre.  This geometry gives rise to an 
-electromagnetic eigenmode with a strong anti-node of the magetic field between
+planes, each with a constriction at the centre.  This geometry gives rise to an 
+electromagnetic eigenmode with a strong anti-node of the magnetic field between
 the two planes at the site of the constriction. This concentrates the rf field 
-and the detection snsitivity
+and the detection sensitivity
 onto the sample area. 
@@
 solder points at the back side for chip capacitors; these can be used to tune the
-resonance to the desired proton Larmor frequency (500 or 600~MHz in the present case).
-Both the PCBs (3 and 5) also carry circuitry for the channel separation and primary 
-tuning and matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
-together. 
-The probe sheath (not shown here) is connected to the auxiliary disk (2) 
-and the scaffold assembly through screws. 
+resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
+Both the PCBs (3 and 5) also carry circuitry for channel separation and primary 
+matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
+together at the top, and forms the top end of the probe assembly.
+The probe sheath (not shown here) is fixed to the auxiliary disk (2) 
+and the scaffold assembly with screws. 
 An exchangeable microfluidic device (1) can be inserted from the top of the detector. 
@@
 into the probe,
-or the device can be actively perfused and operated in-situ, with fluidic connections 
-attached inside the magnet. The microfluidic device is held in place by the spacer 
+or the device can be actively perfused and operated in-situ. 
+The microfluidic device is held in place by the spacer 
 between the two PCB planes coinciding the sample chamber with the constriction on the 
@@
 alignment. 
-
-The RF-insert (6) can be exchanged to tune and match the probe to different frequencies 
-at the X channel. As the detector is connected to the probe base through detachable 
-connectors, various detectors can be used on the same probe skeleton. 
+Since the detector assembly is attached to the probe base through SMP 
+connectors, it can easily be exchanged. 
 Using standard PCB processes to manufacture the detector provides great flexibility
@@
 \caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. 
-A has an O.D.
-of 44.45 mm, in B, circuit elements of X channel are integrated on the PCB itself making it compact (38 mm O.D.).
-Detachable SMP connectors (14) are used to connect the RF insert (6) and also the assembled NMR detector.
-The cost and effort to make a new detector are minimal so, various detectors could be made for various X channel frequencies.}
+A has an O.D. of 44.45 mm, in B, circuit elements of X channel are integrated on the 
+PCB itself making it compact (38 mm O.D.). Detachable SMP connectors (14) are used to 
+connect the RF insert (6) and the detector assembly. }
 \label{fig:ProbePhoto}
 \end{figure}
-Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) for the X channel.
-In (A) the X channel can be tuned to different nuclei by exchanging 6.
-However, in (B) the circuitry of the RF insert (6) is manufactured on the PCB plane (5).
-Inclusion of the circuitry of 6 on 5 makes the design more compact.
-Probe (A) is compatible with Varian 600 ultra shield 14.1 T magnet having an outer diameter (O.D.) of 44.45 mm including the sheath.
-Probe (B), with an outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a Bruker narrow bore shim stack.
-Probe (B) also fits inside a Bruker micro-imaging gradient unit.
-Naturally, B can also be used with wide bore magnets with spacers or gradient stack to keep the probe centred .\par
-The microfluidic devices are made from thermally bonded PMMA sheets.
-The sample chamber and fluidic network are made in the middle layer.
-The middle layer is sealed in between the bottom and the top layers with inlet and outlet in the top layer.
-A flow can be introduced from the inlet and outlet of the device for flow studies or sample exchange.
-The fluidic network on the device can be made freely with the only constrained on the overall size of the device.
-Other layers can be employed to allow parallel flow as long as the total thickness remains below 1mm.\par
+Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
+for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. 
+However, in (B) the circuitry of the RF insert (6) is integrated on the PCB plane (5), 
+making the design more compact.
+ Probe (A) is compatible with a Varian 600 ultra ) of
+shield 14.1 T magnet, with anouter diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an 
+outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a 
+Bruker narrow bore shim stack. 
+Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with 
+wide bore magnets with spacers or gradient stack to keep the probe centred.
+
+Microfluidic devices are made from thermally bonded PMMA sheets as described in detail elsewhere. [REF]
+Briefly, the devices consist of a 0.5~mm thick middle layer between a top- and bottom layer of 
+0.2~mm thickness each. The sample chamber and fluidic network are cut into the middle layer.
+The fluidic network on the device can be designed freely as long as the overall shape of the
+device is preserved, and the location of the sample chamber is maintained.
+
 \begin{figure}
@@
 \caption{Microfluidic devices for different applications compatible with the current setup. 
-From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow, hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and, to grow cells on the device.}
+From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow, 
+hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and, 
+to grow cells on the device.}
 \label{fig:device} 
 \end{figure}
-The circuit for a double resonance probe is based on design shown in figure~\ref{fig:circuit}.
-The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger sample volumes for some cases.
-Primary tuning of the detector is performed through the circuit elements (mainly C$_6$).
-The detector is connected to the secondary tuning and matching capacitors with the transmission lines on the PCB planes.
-As all the circuit elements are assembled on the PCB planes, the transmission lines on the PCB have lengths similar to the detector.
-Hence transmission lines may become a part of the resonance circuit and can severely affect the probe performance.
-To avoid this problem a series capacitor (C$_5$) was included with the transmission line just before the detector to adjust the impedance of transmission line to 50~$\Omega$.
-In this situation the detector is matched by the transmission line and secondary tuning and matching capacitors can be used for fine tuning and matching.\par
+
+The double resnance circuit is based on the design shown in figure~\ref{fig:circuit}. 
+%The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger 
+%sample volumes for some cases. 
+The transmission line detector is tuned to the desired proton 
+Larmor frequency by chip capacitors located at its four corners, 
+as well as a non-magnetic trimmer capacitor ($C_6$). Two primary 
+matching capacitors ($C_5$ and $C_5'$) bring the impedance into the 
+vicinity of 50$\Omega$. A short microstrip 
+with a specific impedance of 50$\Omega$ 
+on the PCB then provides a connection to the secondary tuning and matching elements on the TMPCB ($C_1$ and $C_2$).
+The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
+Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert, in combination with
+the complex admittance of the detector at the X channel frequency.
+To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
+used commercially available flat copper coils of 8 mm diameter and 3.5 turns \todo{check values} in the case of 
+\textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz 
+could be achieved without $L_1$.
+
 \begin{figure}
@@
 \includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
-\caption{Circuit diagram of the double resonance probe. Proton frequency is feed in from the left (port 2) and X frequency is feed in from right (port 7).}
+\caption{Circuit diagram of the double resonance probe. 
+Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).}
 \label{fig:circuit}
@@
 The probe was used with a spacer on varian 600 MHz.
-All the parts and the probe assembly were designed and simulated on Solidworks (Solidworks, Dassault Syst\`{e}mes).
-The prefabricated aluminium profiles (base platform, scaffold aluminium tubes, probe sleeve) were made from 6061-T3 alloy and were obtained from Aluminum Warehouse, UK to build the probe skeleton.
-A few customised precision-machined parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford, UK) after providing CAD files.
-A small number parts were machined in-house (detector support rods, auxiliary support disks).
-All the electronic components and the semi rigid transmission lines were purchased from Digikey.
-Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK).
-Microfluidic devices were designed on AutoCAD.
-PMMA sheets were cut to desired size and functionality (holes or channels) through a laser cutter (HPC Laser L3040).
-The fluidic channels were cut or scored in a 0.5 mm thickness PMMA sheet.
-The device is made by thermally bonding PMMA sheets using the protocol described in~\cite{yilmaz_bonding}.\par
-Dimensions of the detector were calculated from the simulation described in~\cite{gream_2016}.
-The probe circuit for the double resonance probe was simulated on Mathematica using a symbolic analysis network code to asses the performance of both the channels~\cite{gream-thesis}.\par
-The probe circuit was compiled in KiCAD to design the PCB layout.
-The PCB layout was provided to beta-layout (Aarbergen Germany) and P.W.
-Circuits LTD (Wigston , UK) to manufacture the PCBs.
-Easily and inexpensively available FR4 was used for PCB manufacturing for (figure~\ref{fig:ProbePhoto} A).
-RO3035 from Rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par
-The probe skeleton was assembled by holding the prefabricated aluminium profiles with precision-machined parts and screws.
-Semi-rigid transmission lines were then threaded through the skeleton.
-The base PCB plate was soldered on top of the semi-rigid transmission lines.
-The detector planes (3 and 5) were soldered together separately with the required electronic components characterise by network analysis.
-Minor changes were made to the values of the probe electronic components to optimise the probe performance in practise.\par
-NMR experiments were performed on Varian VNMRS console on a Varian 600 ultra shield 14.1 T magnet.
-Spectra in figure~\ref{fig:lineshape} and \ref{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse.
-Spectrum in figure~\ref{fig:1H-nutation} was acquired with increasing the pulse length.
-Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}.
-Sodium acetate and $^{15}$N labeled urea were purchased from Merek and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
-Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet.
-To obtain the tissue slices first a core of 8 mm diameter was extracted using a biopsy punch from the liver.
-PCLS of thickness 250-300 $\mu$m were prepared using a Krumdieck Tissue slicer.
-Circular slices of 3 mm diameter were then cut from this slice using a smaller punch.The slices were put in the incubator for 2 hours before imaging to allow equilibrium.
+All the parts and the probe assembly were designed in Solidworks (Solidworks, Dassault Syst\`{e}mes). 
+Prefabricated profiles made from 6061-T3 aluminium (Aluminum Warehouse, UK) were used for the
+ mechanical structure of the probe
+(base platform, scaffold tubes, sleeve). 
+A few customised precision-machined parts (scaffold support disks, top disk) were obtained from 
+ProtoLabs (Telford, UK) after providing CAD files. A small number parts were machined in-house
+ (detector support rods, auxiliary support disks). 
+ All  electronic components including semi-rigid transmission lines were purchased from DigiKey Ltd. 
+ Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK). Microfluidic 
+devices were designed on AutoCAD. PMMA sheets were cut to desired size and functionality (holes or channels) using a 
+laser engraving system  (HPC Laser L3040), 
+and then bonded using the protocol described in~\cite{yilmaz_bonding}.
+
+The precise dimensions of the detector were optimised for a given sample volume using 
+finite element calculations in COMSOL, as described in \cite{gream_2016}. 
+The RF response of the probe circuit was simulated using a symbolic  
+network analysis code~\cite{gream-thesis} in order to estimate appropriate component values. Final tuning
+was done by trial and error using an Agilent FieldFox 4 GHz network analyser. 
+PCB layouts were designed using KiCAD, and then sent to
+beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) 
+for manufacturing. Easily and inexpensively available FR4 PCB material
+(\fig{fig:ProbePhoto} A) proved adequate for some purposes, but limited resolution to about 10 Hz.
+A high-quality Teflon-based RF PCB material (RO3035, Rogers Corp., USA) was therefore used for optimal 
+performance in both sensitivity and resolution (\fig{fig:ProbePhoto} B).
+The probe skeleton was assembled from prefabricated aluminium tubes with the  precision-machined scaffold
+disks using brass screws. Semi-rigid transmission lines were then threaded through the tubes, and the TMPCB plate was 
+soldered on top. The detector planes (3 and 5) and the PMMA spacer between them were assembled using short bits
+of 0.5~mm magnet wire, which were soldered to the appropriate pads in the four corners of the detector structure.
+
+NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 ultra shield 14.1 T magnet.  
+Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T 
+magnet. 
+Sodium acetate and $^{15}$N labeled urea were purchased from Merek \todo{Address?} and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
+
+Precision-cut murine liver slices (PCLS) were obtained by first extracting a tissue core of 8 mm diameter 
+using a biopsy punch. PCLS of 250-300 $\mu$m thickness were cut from the core using a Krumdieck Tissue slicer, 
+and then reduced to 3~mm diameter using a smaller punch.The slices were incubated in well-plates at 37$^\circ$C and 80\%
+O\textsubscript{2}, 4\% CO\textsubscript{2}
+for 2 hours before imaging.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results and Discussion}
+The spectra in \fig{fig:lineshape} and \fig{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse.
+Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}.
+
 %\begin{itemize}
@@
 %\end{itemize}
-A double channel probe allows heteronuclear NMR experiments which are essential for many applications like protein structure determination.
-The current probe can be simultaneously operated at 2 frequencies.
-The probe can be tuned to protons and one X channel ($^{13}$C or $^{15}$N) frequencies at a time.
-As already explained, the X channel tuning frequency can be changed by simply exchanging an rf-insert or the complete detector.
-Figure~\ref{fig:tandm} shows the measured tuning and matching curves at different proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz) corresponding to the larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively.
-The measurements were performed in the pairs of 600 MHz and 60 MHz and, 500 MHz and 125 MHz.
-The loaded Q factors are 42, 49, 32, 36 at 600 MHz, 500 MHz, 125 MHz and, 60 MHz respectively.
-Channel separation is better than 15 decibels at all operating frequencies and thus sufficient to perform decoupling during experiments.\par
+The probe is designed for double resonance, with proton-detected experiments in mind. The circuit is optimised
+for efficiency and sensitivity at the high-frequency channel, while allowing RF pulses to be applied
+at the X frequency as well. As already explained, the X channel tuning frequency can be changed by simply
+ exchanging either only a small RF-insert or the complete detector assembly. 
+ \fig{fig:tandm} shows the measured reflection and transmission scattering coefficients ($S$-parameters) as a 
+ function of frequency for two combinations of 
+ proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz), 
+ corresponding to the Larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively. 
+ The measurements were performed in the pairs of 600 MHz and 60 MHz and 500 MHz and 125 MHz. The loaded $Q$ factors,
+ determined from the -3dB points of the reflection curves, are 42, 49, 32, 36 at 600 MHz, 500 MHz, 
+ 125 MHz and, 60 MHz respectively. The channel separation is better than -15dB at all operating frequencies.
+
 \begin{figure}
@@
 \includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
-\caption{Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 60 MHz ($^{15}$N frequency at 14 T) and, 125 MHz ($^{13}$C frequency at  and 11.7 T).
-Probe can be tuned to 2 frequencies at a time, above results were measured in pairs of 600 MHz with 60 MHz and 500 MHz with125 MHz.
-Decoupling can be performed at all the frequencies as the channel separation is better than 15 decibels at all frequencies.}
+\caption{
+Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 
+60 MHz (\textsuperscript{15}N frequency at 14 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
+Probe can be tuned to 2 frequencies at a time, above results were measured in 
+pairs of 600 MHz with 60 MHz and 500 MHz with125 MHz. Decoupling can be performed at all the 
+frequencies as the channel separation is better than 15 decibels at all frequencies.}
 \label{fig:tandm} 
 \end{figure}
-Initially FR4 PCB material was used to make detector assembly because of its low cost and easy availability.
-B$_0$ field maps of the sample chamber generated from gradient echo images using these detectors showed inhomogeneities in the B$_0$ field.
-To avoid inhomogeneities and therefore to achieve better resolution, detectors were made from RO3035 material from Rogers corporation.
-Though RO3035 provides better resolution it is more expensive and takes longer to obtain compared to FR4.
-A new detector design can first be tested using FR4 material and the optimised design can be made from RO3035.\par
-$^1$H nutation diagram of water peak for a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz is shown figure~\ref{fig:1H-nutation}.
-RF field is highly homogeneous with 810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% at 600~MHz.
-The probe can generate 100 kHz RF-field for an input power of 100 W both at 600 MHz and 500 MHz corresponding to RF field efficiency (B$_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$ .
-$^{15}$N nutation detected on protons for the same sample is shown in figure~\ref{fig:15N-nutation}.
-An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$C with measurements.
-The power used at the X channel was more than 100 W still no signs of arcing were observed in the NMR spectrum.\par
+
+Initially FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
+B$_0$ field maps of the sample chamber obtained from gradient echo images using these detectors 
+showed inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing (not shown).
+To avoid these inhomogeneities and therefore to achieve better resolution, 
+detectors were made from RO3035 material. While RO3035 provides better resolution, it is more expensive 
+and takes longer to obtain compared to FR4. 
+It therefore makes sense to first prototype new detector designs in FR4, and only use the more expensive RO3035 
+once the design has been validated.
+
+\fig{fig:1H-nutation} shows the $^1$H nutation diagram of the water peak in an aqueous solution of 
+100~mM $^{15}$N-urea  measured at 600~MHz. The RF field shows good homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
+ratio of more than 90\%. The probe generates 100~kHz nutation frequency from 100~W input power both at 
+600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$. 
+The detector geometry has been optimised for a sample volume of 5~$\mu$l. It compares reasonably well to
+the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.\todo{REF} for single-frequency detector 
+of half this size at a Larmor frequency of 300~MHz.
+
+The probe is not sensitive enough to make direct detection of $^{15}$N signals practical. Nutation at the
+$^{15}$N frequency was therefore detected indirectly using coherence transfer to protons. 
+\fig{fig:15N-nutation} shows the results. Using 100~W of input power \todo{verify power setting} 
+produces nutation frequencies of 6 kHz for $^{15}$N and 14 kHz for $^{13}$C. 
+No signs of arcing were obseved at this power level for pulses up to 1~ms duration.
+
 \begin{figure}
@@
 \end{figure}
+
 \begin{figure}
@@
 \end{figure}
-Figure~\ref{fig:lineshape} shows a spectrum of 130 mM Na-acetate peak dissolved in H$_2$O acquired after water presaturation at 600 MHz with 32 averages.
-The figure in the inset shows expanded view of the base of the acetate peak.
-Carbon satellites can be seen well above noise level.
-The orange curve corresponds to a Lorentzian lineshape with full width at half maximum of 3.35 Hz.
-Limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ is  1.18 nmol s$^{1/2}$ at 600 MHz for the acetate sample.
-The measured LOD is found to be better than the calculated LOD in~\cite{gream_2016} for 600 MHz.\par
+
+\fig{fig:lineshape} shows the 600 MHz proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O. 
+The spectrum was acquired with water presaturation at 100~Hz. 32 transients were averaged with a repetition delay
+of 3~s. \todo{verify all numbers} 
+The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above 
+the noise level. The orange curve corresponds to a Lorentzian lineshape with full width at half maximum of 
+3.35 Hz, corresponding to 0.0056 ppm. This is very similar to the resolution reported by Finch et al. at 300~MHz.
+While the residual cause of broadening is still under investigation, we have reason to suspect imperfections
+in the fabrications of the PMMA microfluidic devices to play a major role. Efforts to mitigate these and to
+achieve more highly resolved proton spectra are currently underway in our laboratory and will be reported at a later
+occasion.  The limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ is 
+1.18 nmol s$^{1/2}$ of protons at 600 MHz, slightly better than the value reported for a 
+smaller detector by Finch et al.~\cite{gream_2016}
+
 \begin{figure}
@@
 \end{figure}
-Though the resolution for the current setup is not optimised, it can be used to acquired spectrum with sufficient resolution to differentiate between peaks of different molecules in a mixture.
-Spectrum of DMEM (Dulbecco's modified Eagle's medium) cell growth media acquired with 256 scans in 20 mins is shown in figure~\ref{fig:media-spec} to demonstrate the feasibility of acquiring spectrum for metabolomic studies.
+
+Even though the resolution of the proton spectra still needs to be improved, it is sufficient to analyse
+complex mixtures. The proton spectrum of DMEM (Dulbecco modified Eagle's medium) cell growth medium acquired with 256 
+scans in 20 mins is shown in figure~\ref{fig:media-spec}. This demonstrates the suitability of this probe 
+for metabolomic studies of microfluidic cultures of cells, tissues, and small organisms.
+
 Figure~\ref{fig:HSQC} shows the possibility of useful double resonance experiments in the current setup.

### 2018-12-31 ms5n17-tlp-mn-180216-001.tex
wording changes 3

@@
 \section{Results and Discussion}
-The spectra in \fig{fig:lineshape} and \fig{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse.
-Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}.
 
@@
 
-Initially FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
+Initially, FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
 B$_0$ field maps of the sample chamber obtained from gradient echo images using these detectors 
@@
 The probe is not sensitive enough to make direct detection of $^{15}$N signals practical. Nutation at the
-$^{15}$N frequency was therefore detected indirectly using coherence transfer to protons. 
+$^{15}$N frequency was therefore detected indirectly using coherence transfer to protons \cite{bax_indirect}. 
 \fig{fig:15N-nutation} shows the results. Using 100~W of input power \todo{verify power setting} 
@@
 
-Figure~\ref{fig:HSQC} shows the possibility of useful double resonance experiments in the current setup.
-On left, $^{13}$C-$^{1}$H-HSQC spectrum, acquired in 12 mins (32 t$_1$ increments and 16 scans) from 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in water.
-On right, $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in a buffer solution.
-$^{15}$N is a very insensitive nuclei hence very difficult to detect.
-$^{15}$N-$^{1}$H-HSQC spectrum on 1 mM of protein sample clearly shows that the current probe can be used for protein structure studies with minimal amount of isotopically labeled protein.\par
+Figure~\ref{fig:HSQC} demonstrates proton-detected double resonance experiments in the current setup. 
+The left panel shows a $^{13}$C-$^{1}$H heteronuclear single quantum correlation (HSQC) spectrum, acquired in 12 mins 
+(32 t$_1$ increments and 16 scans) 
+from a 2.5 $\mu$l sample of 100 mM u-$^{13}$C-glucose dissolved in water. The right panel shows a 
+$^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) 
+from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7. 
+All expected cross peaks are present in the spectrum. The ability to obtain meaningful  \textsuperscript{1}H-
+\textsuperscript{15}N correlation spectra from such small samples could prove very useful in the context of
+proteins that are difficult to express and therefore only available in small quantities. The integration of
+protein NMR and microfluidic technology also opens new possibilities for high-throughput kinetics and 
+binding studies.
+
 \begin{figure}
@@
 \includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 
-\caption{$^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14 T.
+\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14 T.
 Glucose HSQC spectrum was acquired in 12 minutes from a 100 mM sample.
@@
 \end{figure}
-The probe has been used to make micro MR (magnetic resonance) images using a Bruker imaging unit.
-Figure~\ref{fig:tisli} shows MR images of mouse liver tissue slice immersed in DMEM cell growth media acquired by putting the slices in a microfluidic device with circular sample chamber to accommodate the slice.
+
+The probe can also be used to make micro MR (magnetic resonance) images using a Bruker micro-gradient  unit. 
+To this effect, the aluminium probe sleeve must be replaced by an electrically insulating material in order to 
+avoid image distortions due to eddy currents in the sleeve. 
+Figure~\ref{fig:tisli} shows MR images of mouse liver tissue slice 
+immersed in DMEM cell growth medium.
+The slice was placed in a microfluidic device with circular sample chamber centred at the detector location, as 
+shown in \fig{fig:tisli}A. 
+The image shown in \fig{fig:tisli}B was acquired using a gradient echo (FLASH) pulse sequence with repetion time
+$t_R=120$~ms and echo time $t_E=12$~ms \todo{verify all values}
 The acquisition times for MR images were 1 minute, 25 minutes and 8 minutes for gradient echo, spin echo and RARE 8 (rapid acquisition with relaxation enhancement) respectively.
@@
 Here we have presented preliminary results of imaging experiments.
-In future we aim to include a dedicated micro-imaging setup for better resolution to make metabolic profile maps by diffusion tensor imaging.\par
+In future we aim to include a dedicated micro-imaging setup for better resolution to make metabolic profile maps by diffusion tensor imaging.
+
 \begin{figure}

### 2019-01-01 ms5n17-tlp-mn-180216-001.tex
finished wording changes (excl abstract and figure captions)

@@
 \includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png} 
-\caption{Micrograph of the probe with and without the sleeve.}
+\caption{The probe with and without sleeve.}
 \label{fig:probe} 
@@
 \caption{Circuit diagram of the double resonance probe. 
-Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).}
+Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).
+\todo{modify figure to represent connections to detector structure properly, and include PCB microstrip
+transmission line}
+}
 \label{fig:circuit}
@@
 \includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
-\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.}
+\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.
+\todo{fix typo in the x-axis label}
+}
 \label{fig:15N-nutation} 
@@
 \end{figure}
-
-The probe can also be used to make micro MR (magnetic resonance) images using a Bruker micro-gradient  unit. 
+%$ 
+The probe can also be used to acquire micro magnetic resonance (MR) images using a Bruker micro-gradient unit. 
 To this effect, the aluminium probe sleeve must be replaced by an electrically insulating material in order to 
 avoid image distortions due to eddy currents in the sleeve. 
-Figure~\ref{fig:tisli} shows MR images of mouse liver tissue slice 
+\fig{fig:tisli} shows MR images of mouse liver tissue slice 
 immersed in DMEM cell growth medium.
@@
 The image shown in \fig{fig:tisli}B was acquired using a gradient echo (FLASH) pulse sequence with repetion time
-$t_R=120$~ms and echo time $t_E=12$~ms \todo{verify all values}
-The acquisition times for MR images were 1 minute, 25 minutes and 8 minutes for gradient echo, spin echo and RARE 8 (rapid acquisition with relaxation enhancement) respectively.
-Though the commercial imaging unit is optimised for bigger sample size (30 mm inner diameter max), images with in-plane resolution of 30 ($\mu$m)$^{2}$ are recorded for a 3 mm liver slice of thickness 300~$\mu$m.
-Here we have presented preliminary results of imaging experiments.
-In future we aim to include a dedicated micro-imaging setup for better resolution to make metabolic profile maps by diffusion tensor imaging.
+$t_R=120$~ms and echo time $t_E=12$~ms \todo{verify all values}. The slice thickness of  1~mm encompasses the entire thickness of the tissue; the 
+lateral dimensions of all MR images in \fig{fig:tisli} are 512$\times$512 pixels
+at a resolution of 30~$\mu$m.
+\fig{fig:tisli}C shows a $B_0$ field map, which has been obtained by acquiring
+two separate FLASH images with echo times $t_E=6$~ms and 12~ms, respectively.
+The brightness of each pixel is prootional to the sum of the magnitude of
+the two images, whereas the colour encode the phase difference bewteen them.
+The full colour range from red to blue spans phase differences from $-\pi$ to
+$+\pi$, corresponding to local field variations of $\Delta B/B_0=...$ 
+\todo{compute value and insert here}.
+A spin echo image is shown in \fig{fig:tisli}D, acquired over 25~min. Finally,
+\fig{fig:tisli}E shows a RARE image using the same parameters, with 8 echos
+acquired per scan, thus reducing the acquisition time to 8 minutes.
 
@@
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
-We have presented a novel modular NMR probe assembly for generic high sensitivity microfluidic NMR experiments.
-The probe is built from the readily accessible materials with no requirement of parts from commercial probes.
-The modularity of the probe enables to use different detectors tailored for specific experimental requirements on the same probe skeleton.
-The detector is made from easily available PCB materials.
-The use of PCB allows to modify the probe circuit and design without disturbing the probe geometry.
-The probe has excellent B$_1$ homogeneity and sensitivity.
-The resolution is reasonable for primary metabolic studies but needs to be improved for generic applications.
-The probe has already been used for various diverse experiments like reaction monitoring, protein structure determination, micro-imaging of mouse liver tissue slices, metabolic studies of mammalian cells, hyperpolarisation on the chip etc.
-Although in the current form the probe can be used for generic 2D experiments, in the future we intend to include extra channels for lock and pulses on other nuclei.
-Though, commercial gradient system has been successful to make micro images of mouse liver tissue slices, a dedicated gradient system can be included on the probe PCB for shimming and imaging.
+We have presented a novel modular NMR probe assembly for generic high 
+sensitivity microfluidic NMR experiments. 
+The probe is built from the readily accessible materials, using only a minimum
+of custom-made parts. 
+The modularity of the probe enables to use different detectors 
+tailored for specific experimental requirements on the same probe skeleton. 
+The detector itself is made from easily available PCB materials. 
+The use of PCB technology offers great flexibility, snd allows to modify the 
+probe circuit and design without affecting the probe geometry. 
+The probe has excellent B$_1$ homogeneity and its sensitivity is in line with
+the best performances that have been reported in this range of probe volumes.
+
+Using simple microfluidic devices made from PMMA sheets by laser cutting,
+spectral resolution around 0.005~ppm is achieved in proton spectra at 
+600~MHz. This is sufficient for primary metabolic studies, but some
+applications could benefit from better resolution. The probe has already been 
+used for various  experiments including reaction monitoring  \todo{REF}, 
+micro-imaging of mouse liver tissue slices, and metabolic studies of 
+mammalian cells. The probe is designed for double resonance, and
+acqusition of proton-detected heteronuclear correlation experiments
+has been demonstrated for small molecules as well as proteins. 
+In the future we intend to add a field-frequency lock channel,
+as well as additional functionality to control sample temperature, 
+as well as advanced microfluidic perfusion and flow control.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Acknowledgement}
-This research was funded through "Future and Emerging Technologies" (FETOPEN) call of the EU Horizon 2020 research framework.
-Authors would like to thank William Hale and Bishnubrata Patra for making microfluidic devices and Dr.
-Katrin Deinhardt from Department of Biological Science at UoS, for the mouse liver tissue..
+This research was supported by the "TISuMR" project,
+funded through "Future and Emerging Technologies" (FETOPEN) 
+call of the EU Horizon 2020 research framework. The authors would like to 
+thank Mr.~William Hale and Dr.~Bishnubrata Patra for help with
+making microfluidic devices, Dr.~Katrin Deinhardt for providing 
+the mouse liver tissue, and Dr.~Jörn Werner for providing the 
+labelled ubiquitin sample and for his support in the acquisition
+and processing of the HSQC spectrum.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-01-15 ms5n17-tlp-mn-180216-001.tex
few corrections

@@
-\documentclass[preprint,12pt]{article}
-\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,authblk,lineno}
+\documentclass[preprint,5p]{elsarticle}
+\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
 %\linenumbers
@@
 \author[1]{Marcel Utz}
-\affil[1]{School of Chemistry, University of Southampton, Southampton SO17 1BJ, United Kingdom}
-\date{\today}
-\setcounter{Maxaffil}{0}
-\renewcommand\Affilfont{\itshape\footnotesize}
-\maketitle
-\clearpage
+\address[1]{School of Chemistry, University of Southampton, Southampton SO17 1BJ, United Kingdom}
+%\date{\today}
+%\setcounter{Maxaffil}{0}
+%\renewcommand\Affilfont{\itshape\footnotesize}
+%\maketitle
+%\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The probe has a limit of detection of 1.18 nmol s$^{-1/2}$, resolution of 3.35 Hz and, excellent B$_{1}$ homogeneity.
-The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel ($^{13}$C or $^{15}$N) frequencies.
-We have successfully acquired $^1$H-$^{13}$C and $^1$H-$^{15}$N heteronuclear correlation spectrum (HSQC).
-Particularly, $^1$H-$^{15}$N HSQC spectrum of 1 mM $^{15}$N labeled ubiquitin from 2.5 $\mu$l of sample volume.
+The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel (\textsuperscript{13}C or \textsuperscript{15}N) frequencies.
+We have successfully acquired \textsuperscript{1}H-\textsuperscript{13}C and \textsuperscript{1}H-\textsuperscript{15}N heteronuclear correlation spectrum (HSQC).
+Particularly, \textsuperscript{1}H-\textsuperscript{15}N HSQC spectrum of 1 mM \textsuperscript{15}N labeled ubiquitin from 2.5 $\mu$l of sample volume.
 \end{abstract}
 \maketitle
-\clearpage
+%\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 analysis~\cite{NMR-chemical-1995, hills1994magnetic, rabenstein1991quantitative},
-metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, molecular 
-structure determination~\cite{wuthrich1990protein}, reaction 
+molecular structure determination~\cite{wuthrich1990protein}, metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, reaction 
 monitoring~\cite{maiwald2004quantitative} etc. Microfluidic lab-on-a-chip (LOC) devices 
@@
 must be injected. Only a few designs that allow insertion of a removable microfluidic 
-device into the detector have been described \todo{REF Graeme, Spengler, Korvink et al}.
+device into the detector have been described~\cite{Spengler-2014,Spengler-2016,gream_2016}.
 
@@
 \centering
-\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
 \caption{Exploded view of he probe design (left) and assembled probe (right). 
@@
 The probe is composed of three main assemblies: A) probe base; B) scaffold assembly; 
-C) detector assembly (figure~\ref{fig:probe}). 
-The  base (blue in figure~\ref{fig:probe-explode}) and the scaffold assembly 
-(green in figure~\ref{fig:probe-explode}) together make the skeleton of the probe. 
+C) detector assembly (\fig{fig:probe}). 
+The  base (blue in \fig{fig:probe-explode}) and the scaffold assembly 
+(green in \fig{fig:probe-explode}) together make the skeleton of the probe. 
 Both the base and scaffold assembly are made from standard aluminium profiles. 
@@
 The detector assembly is connected to through a pair of
-low-loss SMP connectors (14 in figure~\ref{fig:ProbePhoto}).
+low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
 While each detector assembly is roughly
@@
 \end{figure}
-Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
+\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
 for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. 
@@
 
-The double resnance circuit is based on the design shown in figure~\ref{fig:circuit}. 
+The double resnance circuit is based on the design shown in \fig{fig:circuit}. 
 %The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger 
@@
 To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
-used commercially available flat copper coils of 8 mm diameter and 3.5 turns \todo{check values} in the case of 
+used commercially available flat copper coils of 5 mm diameter and 4.5 turns in the case of 
 \textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz 
@@
 \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
+\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
 \caption{Circuit diagram of the double resonance probe. 
 Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).
-\todo{modify figure to represent connections to detector structure properly, and include PCB microstrip
-transmission line}
 }
@@
 for manufacturing. Easily and inexpensively available FR4 PCB material
-(\fig{fig:ProbePhoto} A) proved adequate for some purposes, but limited resolution to about 10 Hz.
+(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited resolution to about 10 Hz.
 A high-quality Teflon-based RF PCB material (RO3035, Rogers Corp., USA) was therefore used for optimal 
-performance in both sensitivity and resolution (\fig{fig:ProbePhoto} B).
+performance in both sensitivity and resolution (\fig{fig:ProbePhoto}(B)).
 The probe skeleton was assembled from prefabricated aluminium tubes with the  precision-machined scaffold
@@
 magnet. 
-Sodium acetate and $^{15}$N labeled urea were purchased from Merek \todo{Address?} and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
+Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich,UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
 
@@
 Probe can be tuned to 2 frequencies at a time, above results were measured in 
-pairs of 600 MHz with 60 MHz and 500 MHz with125 MHz. Decoupling can be performed at all the 
+pairs of 600 MHz with 60 MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the 
 frequencies as the channel separation is better than 15 decibels at all frequencies.}
@@
 The detector geometry has been optimised for a sample volume of 5~$\mu$l. It compares reasonably well to
-the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.\todo{REF} for single-frequency detector 
+the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for single-frequency detector 
 of half this size at a Larmor frequency of 300~MHz.
@@
 \includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
-\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.
-\todo{fix typo in the x-axis label}
-}
+\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.}
 \label{fig:15N-nutation} 
@@
 complex mixtures. The proton spectrum of DMEM (Dulbecco modified Eagle's medium) cell growth medium acquired with 256 
-scans in 20 mins is shown in figure~\ref{fig:media-spec}. This demonstrates the suitability of this probe 
+scans in 20 mins is shown in \fig{fig:media-spec}. This demonstrates the suitability of this probe 
 for metabolomic studies of microfluidic cultures of cells, tissues, and small organisms.
 
-Figure~\ref{fig:HSQC} demonstrates proton-detected double resonance experiments in the current setup. 
+\fig{fig:HSQC} demonstrates proton-detected double resonance experiments in the current setup. 
 The left panel shows a $^{13}$C-$^{1}$H heteronuclear single quantum correlation (HSQC) spectrum, acquired in 12 mins 
@@
 The slice was placed in a microfluidic device with circular sample chamber centred at the detector location, as 
-shown in \fig{fig:tisli}A. 
-The image shown in \fig{fig:tisli}B was acquired using a gradient echo (FLASH) pulse sequence with repetion time
+shown in \fig{fig:tisli}(A). 
+The image shown in \fig{fig:tisli}(B) was acquired using a gradient echo (FLASH) pulse sequence with repetion time
 $t_R=120$~ms and echo time $t_E=12$~ms \todo{verify all values}. The slice thickness of  1~mm encompasses the entire thickness of the tissue; the 
@@
 at a resolution of 30~$\mu$m.
-\fig{fig:tisli}C shows a $B_0$ field map, which has been obtained by acquiring
+\fig{fig:tisli}(C) shows a $B_0$ field map, which has been obtained by acquiring
 two separate FLASH images with echo times $t_E=6$~ms and 12~ms, respectively.
@@
 \todo{compute value and insert here}.
-A spin echo image is shown in \fig{fig:tisli}D, acquired over 25~min. Finally,
-\fig{fig:tisli}E shows a RARE image using the same parameters, with 8 echos
+A spin echo image is shown in \fig{fig:tisli}(D), acquired over 25~min. Finally,
+\fig{fig:tisli}(E) shows a RARE image using the same parameters, with 8 echos
 acquired per scan, thus reducing the acquisition time to 8 minutes.
@@
 \caption{MR images of a freshly cut live slice from a mouse.
-A: optical micrograph; B: Gradient echo image acquired in 1 minute; C: magnetic field map; D Spin echo image acquired in 30 minutes; E: RARE8 image acquired in 8 minutes.}
+A: optical micrograph; B: Gradient echo image acquired in 1 minute; C: magnetic field map; D: Spin echo image acquired in 30 minutes; E: RARE8 image acquired in 8 minutes.}
 \label{fig:tisli} 
@@
 applications could benefit from better resolution. The probe has already been 
-used for various  experiments including reaction monitoring  \todo{REF}, 
+used for various  experiments including reaction monitoring~\cite{Fang-2018}, 
 micro-imaging of mouse liver tissue slices, and metabolic studies of 

### 2019-01-18 ms5n17-tlp-mn-180216-001.tex
Final version MS

@@
 The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit board) materials.
-The probe has a limit of detection of 1.18 nmol s$^{-1/2}$, resolution of 3.35 Hz and, excellent B$_{1}$ homogeneity.
+The probe has a limit of detection of 1.4 nmol s$^{-1/2}$, resolution of 3.35 Hz and, an excellent B$_{1}$ homogeneity.
 The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel (\textsuperscript{13}C or \textsuperscript{15}N) frequencies.
@@
 In particular, microfluidic technology allows detailed control over growth conditions 
-in the culture of cells, cell aggregates, and small organisms. 
+in the culture of cells, cell aggregates, and small organisms~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. 
 Lab-on-a-chip devices can also enable high experimental 
-throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. 
+throughput by parallelisation. 
 In spite of its analytical power, NMR has so far only rarely been used in microfluidic 
@@
 for microfluidic devices. For example, the metabolic activity of cell cultures 
-can be followed non-invasively by NMR throughout the course of the experiment, 
+can be followed non-invasively by NMR throughout the course of the experiment~\cite{cellnmr-2015}, 
 while effects on cell differentiation can still be analysed by a (destructive) 
@@
 for different microfluidic devices on a single probe base. 
-Once thw probe base is in place, additional detectors can be manufactured 
+Once the probe base is in place, additional detectors can be manufactured 
 within 2-3 days for less than $\sim$200 $\geneuro$. 
@@
 Detailed construction drawings for the probe are provided in the supporting 
-information, and a complete set of CAD files is available for download at [...].
+information, and a complete set of CAD files is available for download at \todo{needs to be discussed}.
 The planar geometry of the detector accommodates exchangeable microfluidic devices 
@@
 with the exception of a small number of precision-machined parts which are used 
-to hold the assembly together. These can be ordered from commercial prototvaiyping 
+to hold the assembly together. These can be ordered from commercial prototyping 
 manufacturers or machined in-house if mechanical workshop facilities are available.
@@
 \includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
-\caption{Exploded view of he probe design (left) and assembled probe (right). 
-Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a 
-generic mounting point for the NMR detector assembly(red). 
+\caption{Exploded view of the probe design (left) and assembled probe (right). 
+Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 8) provides a 
+generic mounting point for the NMR detector assembly (red). 
 A microfluidic device (1) can be inserted from the top of the probe. 
@@
 modular PCB insert (6). The modular NMR detector is made up of parts 3 to 6 and is 
-connected to the base plate PCB (8) through standard coaxial (SMP) connectors. 
+connected to the TMPCB (8) through standard coaxial (SMP) connectors. 
 The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) 
@@
 The scaffold assembly is made up of two hollow aluminium tubes (11) held together with 
-precision machined parts at either end(scaffold support disks (10)). 
+precision machined parts at both ends (scaffold support disks (10)). 
 The semi-rigid cables are  threaded through these hollow aluminium tubes 
@@
 for the exchangeable detector assembly. It also provides 
-capacitors (7) for secondary tuning and matching.
-The detector assembly is connected to through a pair of
+capacitors (7) for secondary tuning and matching of the detector.
+The detector assembly is connected to the TMPCB through a pair of
 low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
@@
 together at the top, and forms the top end of the probe assembly.
-The probe sheath (not shown here) is fixed to the auxiliary disk (2) 
+The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2) 
 and the scaffold assembly with screws. 
@@
 microfluidic sample sizes, and different combinations of target nuclei.
-\par
+
 \begin{figure}
@@
 \caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. 
-A has an O.D. of 44.45 mm, in B, circuit elements of X channel are integrated on the 
-PCB itself making it compact (38 mm O.D.). Detachable SMP connectors (14) are used to 
-connect the RF insert (6) and the detector assembly. }
+O.D. of A is 44.45 mm and B is 38 mm. Circuit elements of X channel are integrated on the 
+PCB in B making it compact. Detachable SMP connectors (14) are used to 
+connect the RF insert (6) and the detector assembly.}
 \label{fig:ProbePhoto}
@@
 making the design more compact.
- Probe (A) is compatible with a Varian 600 ultra ) of
-shield 14.1 T magnet, with anouter diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an 
-outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a 
+ Probe (A) is compatible with a Varian 600 Premium shielded 14.1 T magnet, with an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an 
+O.D. of 38 mm including the sheath, is designed to fit inside a 
 Bruker narrow bore shim stack. 
@@
 
-Microfluidic devices are made from thermally bonded PMMA sheets as described in detail elsewhere. [REF]
-Briefly, the devices consist of a 0.5~mm thick middle layer between a top- and bottom layer of 
+Microfluidic devices are made from thermally bonding PMMA sheets.
+Briefly, the devices consist of a 0.5~mm thick middle layer between a top and bottom layer of 
 0.2~mm thickness each. The sample chamber and fluidic network are cut into the middle layer.
@@
 performance in both sensitivity and resolution (\fig{fig:ProbePhoto}(B)).
-The probe skeleton was assembled from prefabricated aluminium tubes with the  precision-machined scaffold
+The probe skeleton was assembled from prefabricated aluminium tubes held with the precision-machined scaffold
 disks using brass screws. Semi-rigid transmission lines were then threaded through the tubes, and the TMPCB plate was 
@@
 
-NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 ultra shield 14.1 T magnet.  
+NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet.  
 Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T 
 magnet. 
-Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich,UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
+Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.
 
@@
 using a biopsy punch. PCLS of 250-300 $\mu$m thickness were cut from the core using a Krumdieck Tissue slicer, 
-and then reduced to 3~mm diameter using a smaller punch.The slices were incubated in well-plates at 37$^\circ$C and 80\%
-O\textsubscript{2}, 4\% CO\textsubscript{2}
+and then reduced to 3~mm diameter using a smaller punch. The slices were incubated in well-plates at 37$^\circ$C and 80\%
+O\textsubscript{2}, 5\% CO\textsubscript{2}
 for 2 hours before imaging.
@@
  proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz), 
- corresponding to the Larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively. 
+ corresponding to the Larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14.1 T and 11.7 T respectively. 
  The measurements were performed in the pairs of 600 MHz and 60 MHz and 500 MHz and 125 MHz. The loaded $Q$ factors,
@@
 Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 
-60 MHz (\textsuperscript{15}N frequency at 14 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
+60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
 Probe can be tuned to 2 frequencies at a time, above results were measured in 
@@
 \end{figure}
+Initially, FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
+Inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can be seen as fringes in~\fig{fig:field map} (A).
+B$_{0}$ field maps of the sample chamber were constructed from 2 gradient echo (FLASH) images having echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms for both FR4 and RO3035 PCB materials with the same chip~(\fig{fig:field map}).
+The brightness of each pixel is proportional to the sum of the magnitude of the two images, whereas the colour encode the phase difference between them.
+The full colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.
 
-Initially, FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
-B$_0$ field maps of the sample chamber obtained from gradient echo images using these detectors 
-showed inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing (not shown).
-To avoid these inhomogeneities and therefore to achieve better resolution, 
+To avoid the inhomogeneities of FR4 and therefore to achieve better resolution, 
 detectors were made from RO3035 material. While RO3035 provides better resolution, it is more expensive 
@@
 
-\fig{fig:1H-nutation} shows the $^1$H nutation diagram of the water peak in an aqueous solution of 
-100~mM $^{15}$N-urea  measured at 600~MHz. The RF field shows good homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
-ratio of more than 90\%. The probe generates 100~kHz nutation frequency from 100~W input power both at 
+\begin{figure}
+\centering
+\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png} 
+\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and Rogers RO3035 (B) PCB material.
+Both the field maps were constructed from 2 gradient echo images acquired on a chip filled with 130 mM sodium acetate dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
+\label{fig:field map} 
+\end{figure}
+
+The RF field at proton frequency shows excellent homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
+ratio of more than 90\% measured from $^1$H nutation of the water peak in an aqueous solution of 
+100~mM $^{15}$N-urea at 600~MHz. The probe generates 100~kHz nutation frequency from 100~W input power both at 
 600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$. 
@@
 of half this size at a Larmor frequency of 300~MHz. 
-
-The probe is not sensitive enough to make direct detection of $^{15}$N signals practical. Nutation at the
-$^{15}$N frequency was therefore detected indirectly using coherence transfer to protons \cite{bax_indirect}. 
-\fig{fig:15N-nutation} shows the results. Using 100~W of input power \todo{verify power setting} 
+For X channel, 100~W of input power 
 produces nutation frequencies of 6 kHz for $^{15}$N and 14 kHz for $^{13}$C. 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png} 
-\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz.
+%\begin{figure}
+%\centering
+%\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png} 
+%\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz.
 The 810$^{\circ}$/90$^{\circ}$ ratio is more than 90\% at 600~MHz.
@@
 Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz}
-\label{fig:1H-nutation} 
-\end{figure}
+%\label{fig:1H-nutation} 
+%\end{figure}
 
-\begin{figure}
-\centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
-\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.}
-\label{fig:15N-nutation} 
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
+%\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.}
+%\label{fig:15N-nutation} 
+%\end{figure}
 
-\fig{fig:lineshape} shows the 600 MHz proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O. 
+\fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O acquired at 600 MHz. 
 The spectrum was acquired with water presaturation at 100~Hz. 32 transients were averaged with a repetition delay
-of 3~s. \todo{verify all numbers} 
-The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above 
+of 3~s. The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above 
 the noise level. The orange curve corresponds to a Lorentzian lineshape with full width at half maximum of 
@@
 achieve more highly resolved proton spectra are currently underway in our laboratory and will be reported at a later
-occasion.  The limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ is 
-1.18 nmol s$^{1/2}$ of protons at 600 MHz, slightly better than the value reported for a 
-smaller detector by Finch et al.~\cite{gream_2016}
+occasion.  The limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ ($n$ is the number of spins and $\Delta t$ is 1/linewidth of the observed resonance) is 
+1.4 nmol s$^{1/2}$ of protons at 600 MHz, slightly better than the value reported for a 
+smaller detector by Finch et al.~\cite{gream_2016}.
 
@@
 (32 t$_1$ increments and 16 scans) 
-from a 2.5 $\mu$l sample of 100 mM u-$^{13}$C-glucose dissolved in water. The right panel shows a 
+from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in water. The right panel shows a 
 $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) 
 from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7. 
-All expected cross peaks are present in the spectrum. The ability to obtain meaningful  \textsuperscript{1}H-
-\textsuperscript{15}N correlation spectra from such small samples could prove very useful in the context of
+All expected cross peaks are present in the spectrum.
+The ability to obtain meaningful  \textsuperscript{15}N-\textsuperscript{1}H correlation spectra from such small samples could prove very useful in the context of
 proteins that are difficult to express and therefore only available in small quantities. The integration of
@@
 \includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 
-\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14 T.
+\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14.1 T.
 Glucose HSQC spectrum was acquired in 12 minutes from a 100 mM sample.
@@
 shown in \fig{fig:tisli}(A). 
-The image shown in \fig{fig:tisli}(B) was acquired using a gradient echo (FLASH) pulse sequence with repetion time
-$t_R=120$~ms and echo time $t_E=12$~ms \todo{verify all values}. The slice thickness of  1~mm encompasses the entire thickness of the tissue; the 
+The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with
+$t_R=120$~ms and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness of the tissue; the 
 lateral dimensions of all MR images in \fig{fig:tisli} are 512$\times$512 pixels
 at a resolution of 30~$\mu$m.
-\fig{fig:tisli}(C) shows a $B_0$ field map, which has been obtained by acquiring
-two separate FLASH images with echo times $t_E=6$~ms and 12~ms, respectively.
-The brightness of each pixel is prootional to the sum of the magnitude of
-the two images, whereas the colour encode the phase difference bewteen them.
-The full colour range from red to blue spans phase differences from $-\pi$ to
-$+\pi$, corresponding to local field variations of $\Delta B/B_0=...$ 
+\fig{fig:tisli}(C) shows a RARE image using the same parameters, with 8 echos
+acquired per scan, thus reducing the acquisition time to 8 minutes.
+A spin echo image is shown in \fig{fig:tisli}(D), acquired over 25~min. Finally,
+\fig{fig:tisli}(E) shows a $B_0$ field map, which has been obtained by acquiring
+two separate FLASH images with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
+, corresponding to local field variations of $\Delta B/B_0=...$ 
 \todo{compute value and insert here}.
-A spin echo image is shown in \fig{fig:tisli}(D), acquired over 25~min. Finally,
-\fig{fig:tisli}(E) shows a RARE image using the same parameters, with 8 echos
-acquired per scan, thus reducing the acquisition time to 8 minutes.
 
@@
 \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 
+\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 
 \caption{MR images of a freshly cut live slice from a mouse.
-A: optical micrograph; B: Gradient echo image acquired in 1 minute; C: magnetic field map; D: Spin echo image acquired in 30 minutes; E: RARE8 image acquired in 8 minutes.}
+A: optical micrograph; B: Gradient echo image acquired in 1 minute; C: RARE8 image acquired in 8 minutes; D: Spin echo image acquired in 30 minutes; E: magnetic field map.}
 \label{fig:tisli} 
@@
 The detector itself is made from easily available PCB materials. 
-The use of PCB technology offers great flexibility, snd allows to modify the 
+The use of PCB technology offers great flexibility, and allows to modify the 
 probe circuit and design without affecting the probe geometry. 
@@
 In the future we intend to add a field-frequency lock channel,
-as well as additional functionality to control sample temperature, 
-as well as advanced microfluidic perfusion and flow control.
-
+as well as additional functionality for advanced microfluidic perfusion with temperature and flow control.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 call of the EU Horizon 2020 research framework. The authors would like to 
-thank Mr.~William Hale and Dr.~Bishnubrata Patra for help with
+thank Mr.~William Hale for help with
 making microfluidic devices, Dr.~Katrin Deinhardt for providing 
-the mouse liver tissue, and Dr.~Jörn Werner for providing the 
+the mouse liver tissue, Dr.~Bishnubrata Patra for tissue slicing and Dr.~J\"{o}rn Werner for providing the 
 labelled ubiquitin sample and for his support in the acquisition

### 2019-01-21 ms5n17-tlp-mn-180216-001.tex
updated abstract; cleanup

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-Microfluidic NMR (Nuclear Magnetic Resonance) can probe chemical or bio-chemical reactions, including the metabolism of cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment.
-We present a dual-channel modular probe assembly for  high efficiency microfluidic-NMR.
-The samples are contained in exchangeable, flow compatible planar microfluidic devices.
-The detector including the tuning and matching circuitry of the probe is modular and allows the use of different detectors optimised for different experimental conditions on the same probe base.
-The complete probe can be built from easily available parts.
-The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit board) materials.
-The probe has a limit of detection of 1.4 nmol s$^{-1/2}$, resolution of 3.35 Hz and, an excellent B$_{1}$ homogeneity.
-The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel (\textsuperscript{13}C or \textsuperscript{15}N) frequencies.
-We have successfully acquired \textsuperscript{1}H-\textsuperscript{13}C and \textsuperscript{1}H-\textsuperscript{15}N heteronuclear correlation spectrum (HSQC).
-Particularly, \textsuperscript{1}H-\textsuperscript{15}N HSQC spectrum of 1 mM \textsuperscript{15}N labeled ubiquitin from 2.5 $\mu$l of sample volume.
-\end{abstract}
-\maketitle
+\begin{abstract} Microfluidic NMR spectroscopy can probe chemical and
+bio-chemical processes non-invasively in a tightly controlled environment. We
+present a dual-channel modular probe assembly for  high efficiency microfluidic
+NMR spectroscopy and imaging. It is compatible with a wide range of microfluidic
+devices,  without constraining the fluidic design. It collects NMR signals from
+a designated sample volume on the device with high sensitivity and resolution.
+Modular design allows adapting the detector geometry to different experimental
+conditions with minimal cost, by using the same probe base. The complete probe
+can be built from easily available parts. The probe body mainly consists of
+prefabricated aluminium profiles, while the probe circuit and detector are made
+from printed circuit boards. We demonstrate a double resonance HX probe with a
+limit of detection of 1.4 nmol s$^{-1/2}$ for protons at 600~MHz, resolution of
+3.35 Hz, and excellent B$_{1}$ homogeneity. We have successfully acquired
+\textsuperscript{1}H-\textsuperscript{13}C and
+\textsuperscript{1}H-\textsuperscript{15}N heteronuclear correlation spectra
+(HSQC), including a \textsuperscript{1}H-\textsuperscript{15}N HSQC spectrum of
+1 mM \textsuperscript{15}N labeled ubiquitin in 2.5 $\mu$l of sample volume.
+\end{abstract} \maketitle
 %\clearpage
@@
 %\end{itemize}
-NMR (Nuclear Magnetic Resonance) is a well established technique used in chemical 
-analysis~\cite{NMR-chemical-1995, hills1994magnetic, rabenstein1991quantitative},
-molecular structure determination~\cite{wuthrich1990protein}, metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, reaction 
-monitoring~\cite{maiwald2004quantitative} etc. Microfluidic lab-on-a-chip (LOC) devices 
-are increasingly finding applications in chemistry and the life 
-sciences~\cite{whitesides2006origins,mark2010microfluidic}. 
-They provide a convenient way to integrate complex chemical and biochemical processes. 
-In particular, microfluidic technology allows detailed control over growth conditions 
-in the culture of cells, cell aggregates, and small organisms~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. 
-Lab-on-a-chip devices can also enable high experimental 
-throughput by parallelisation. 
-In spite of its analytical power, NMR has so far only rarely been used in microfluidic 
-systems. In general, information is extracted from microfluidic devices by spectroscopic 
-techniques at the end point of the experiment. Typically, 
-this is done using fluorescent probes, which bind to one or a few analytes of interest. 
+NMR (Nuclear Magnetic Resonance) is a well established technique used in
+chemical analysis~\cite{NMR-chemical-1995, hills1994magnetic,
+rabenstein1991quantitative}, molecular structure
+determination~\cite{wuthrich1990protein},
+metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, reaction
+monitoring~\cite{maiwald2004quantitative} etc. Microfluidic lab-on-a-chip (LOC)
+devices are increasingly finding applications in chemistry and the life
+sciences~\cite{whitesides2006origins,mark2010microfluidic}. They provide a
+convenient way to integrate complex chemical and biochemical processes. In
+particular, microfluidic technology allows detailed control over growth
+conditions in the culture of cells, cell aggregates, and small
+organisms~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}.
+Lab-on-a-chip devices can also enable high experimental throughput by
+parallelisation. In spite of its analytical power, NMR has so far only rarely
+been used in microfluidic systems. In general, information is extracted from
+microfluidic devices only at the end point of the experiment. Typically, this is
+done using fluorescent probes, which bind to one or a few analytes of interest.
 This approach can reach very high sensitivity, with limits of detection down to
-femtomolar concentrations. However, it is usually destructive, since the sample is 
-affected by the addition of the marker, and can only be done once, at the end of the 
-experiment. Following kinetic processes therefore requires using multiple samples. By 
-contrast, NMR spectroscopy is non-invasive, generic (virtually all organic 
-molecules give an NMR signal), and highly specific (no two metabolites share 
-the same NMR spectrum).
-
-NMR spectroscopy can provide a useful complementary readout capability 
-for microfluidic devices. For example, the metabolic activity of cell cultures 
-can be followed non-invasively by NMR throughout the course of the experiment~\cite{cellnmr-2015}, 
-while effects on cell differentiation can still be analysed by a (destructive) 
-transcriptomic analysis at the end. Unfortunately, the sensitivity 
-of NMR is much lower than that of optical techniques. 
-The small volumes involved in microfluidic systems
- (typically in the range of 1~$\mu$l) 
-compound this problem. As is well known, the mass limit of detection of 
-inductive NMR detectors improves as they are scaled down~\cite{Olson1995}. 
-On this basis, a number of different micro-NMR detector designs have been 
-proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. 
-In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, 
+femtomolar concentrations. However, it is usually destructive, since the sample
+is affected by the addition of the marker, and can only be done once, at the end
+of the experiment. Following kinetic processes therefore requires using multiple
+samples. By contrast, NMR spectroscopy is non-invasive, generic (virtually all
+organic molecules give an NMR signal), and highly specific (no two metabolites
+share the same NMR spectrum), and can therefore provide a useful complementary
+readout capability for microfluidic devices. For example, the metabolic activity
+of cell cultures can be followed non-invasively by NMR throughout the course of
+the experiment~\cite{cellnmr-2015}, while effects on cell differentiation can
+still be analysed by a (destructive) transcriptomic analysis at the end.
+Unfortunately, the sensitivity of NMR is much lower than that of optical
+techniques. The small volumes involved in microfluidic systems (typically in the
+range of 1~$\mu$l) compound this problem. As is well known, the mass limit of
+detection of inductive NMR detectors improves as they are scaled
+down~\cite{Olson1995}. On this basis, a number of different micro-NMR detector
+designs have been proposed and characterised in the
+literature~\cite{utz2012review,micronmr2014review}. In most cases, these are
+based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007},
 planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline
-detectors~\cite{stripline_jan}. 
-Significant research has gone into developing micro-NMR detectors for flow probes, 
-where the sample container takes the form of a fixed capillary into which the sample
-must be injected. Only a few designs that allow insertion of a removable microfluidic 
-device into the detector have been described~\cite{Spengler-2014,Spengler-2016,gream_2016}.
+detectors~\cite{stripline_jan}. Significant research has gone into developing
+micro-NMR detectors for flow probes, where the sample container takes the form
+of a fixed capillary into which the sample must be injected. Only a few designs
+that allow insertion of a removable microfluidic device into the detector have
+been described~\cite{Spengler-2014,Spengler-2016,gream_2016}.
 
@@
 custom-machined parts holding the structure together.
-Detailed construction drawings for the probe are provided in the supporting 
-information, and a complete set of CAD files is available for download at \todo{needs to be discussed}.
+Detailed construction drawings and a complete set of CAD files is
+available for download at \cite{github-probe-download-2019}.
 The planar geometry of the detector accommodates exchangeable microfluidic devices
@@
 
-Microfluidic devices are made from thermally bonding PMMA sheets.
-Briefly, the devices consist of a 0.5~mm thick middle layer between a top and bottom layer of 
-0.2~mm thickness each. The sample chamber and fluidic network are cut into the middle layer.
-The fluidic network on the device can be designed freely as long as the overall shape of the
-device is preserved, and the location of the sample chamber is maintained.
+Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
+thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.
+Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
+bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
+are cut into the middle layer. The fluidic network on the device can be designed
+freely as long as the overall shape of the device is preserved, and the location
+of the sample chamber is maintained.
 
@@
 The probe was used with a spacer on varian 600 MHz.
-All the parts and the probe assembly were designed in Solidworks (Solidworks, Dassault Syst\`{e}mes). 
-Prefabricated profiles made from 6061-T3 aluminium (Aluminum Warehouse, UK) were used for the
- mechanical structure of the probe
-(base platform, scaffold tubes, sleeve). 
-A few customised precision-machined parts (scaffold support disks, top disk) were obtained from 
-ProtoLabs (Telford, UK) after providing CAD files. A small number parts were machined in-house
- (detector support rods, auxiliary support disks). 
- All  electronic components including semi-rigid transmission lines were purchased from DigiKey Ltd. 
- Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK). Microfluidic 
-devices were designed on AutoCAD. PMMA sheets were cut to desired size and functionality (holes or channels) using a 
-laser engraving system  (HPC Laser L3040), 
-and then bonded using the protocol described in~\cite{yilmaz_bonding}.
+All the parts and the probe assembly were designed in Solidworks (Solidworks,
+Dassault Syst\`{e}mes). Prefabricated profiles made from 6061-T3 aluminium
+(Aluminum Warehouse, UK) were used for the mechanical structure of the probe
+(base platform, scaffold tubes, sleeve). A few customised precision-machined
+parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford,
+UK) after providing CAD files. A small number parts were machined in-house
+(detector support rods, auxiliary support disks). All  electronic components
+including semi-rigid transmission lines were purchased from DigiKey Ltd. Cell
+cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
+(Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were
+cut to desired size and functionality (holes or channels) using a laser
+engraving system  (HPC Laser L3040), and then bonded using the protocol
+described in~\cite{yilmaz_bonding}.
 
-The precise dimensions of the detector were optimised for a given sample volume using 
-finite element calculations in COMSOL, as described in \cite{gream_2016}. 
-The RF response of the probe circuit was simulated using a symbolic  
-network analysis code~\cite{gream-thesis} in order to estimate appropriate component values. Final tuning
-was done by trial and error using an Agilent FieldFox 4 GHz network analyser. 
-PCB layouts were designed using KiCAD, and then sent to
-beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) 
-for manufacturing. Easily and inexpensively available FR4 PCB material
-(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited resolution to about 10 Hz.
-A high-quality Teflon-based RF PCB material (RO3035, Rogers Corp., USA) was therefore used for optimal 
-performance in both sensitivity and resolution (\fig{fig:ProbePhoto}(B)).
-The probe skeleton was assembled from prefabricated aluminium tubes held with the precision-machined scaffold
-disks using brass screws. Semi-rigid transmission lines were then threaded through the tubes, and the TMPCB plate was 
-soldered on top. The detector planes (3 and 5) and the PMMA spacer between them were assembled using short bits
-of 0.5~mm magnet wire, which were soldered to the appropriate pads in the four corners of the detector structure.
+The precise dimensions of the detector were optimised for a given sample volume
+using finite element calculations in COMSOL, as described in \cite{gream_2016}.
+The RF response of the probe circuit was simulated using a symbolic network
+analysis code~\cite{gream-thesis} in order to estimate appropriate component
+values. Final tuning was done by trial and error using an Agilent FieldFox 4 GHz
+network analyser. PCB layouts were designed using KiCAD, and then sent to
+beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) for
+manufacturing. Easily and inexpensively available FR4 PCB material
+(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited
+resolution to about 10 Hz. A high-quality Teflon-based RF PCB material (RO3035,
+Rogers Corp., USA) was therefore used for optimal performance in both
+sensitivity and resolution (\fig{fig:ProbePhoto}(B)). The probe skeleton was
+assembled from prefabricated aluminium tubes held with the precision-machined
+scaffold disks using brass screws. Semi-rigid transmission lines were then
+threaded through the tubes, and the TMPCB plate was soldered on top. The
+detector planes (3 and 5) and the PMMA spacer between them were assembled using
+short bits of 0.5~mm magnet wire, which were soldered to the appropriate pads in
+the four corners of the detector structure.
 
-NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet.  
-Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T 
-magnet. 
-Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.
+NMR experiments were performed on a Varian VNMRS console attached to a Varian
+600 premium shielded 14.1 T magnet. Imaging experiments were performed on Bruker
+AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet.
+Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK
+and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life
+Technologies, USA.
 
-Precision-cut murine liver slices (PCLS) were obtained by first extracting a tissue core of 8 mm diameter 
-using a biopsy punch. PCLS of 250-300 $\mu$m thickness were cut from the core using a Krumdieck Tissue slicer, 
-and then reduced to 3~mm diameter using a smaller punch. The slices were incubated in well-plates at 37$^\circ$C and 80\%
-O\textsubscript{2}, 5\% CO\textsubscript{2}
+Precision-cut murine liver slices (PCLS) were obtained by first extracting a
+tissue core of 8 mm diameter using a biopsy punch. PCLS of 250-300 $\mu$m
+thickness were cut from the core using a Krumdieck Tissue slicer, and then
+reduced to 3~mm diameter using a smaller punch. The slices were incubated in
+well-plates at 37$^\circ$C and 80\% O\textsubscript{2}, 5\% CO\textsubscript{2}
 for 2 hours before imaging.
@@
 %\end{itemize}
-The probe is designed for double resonance, with proton-detected experiments in mind. The circuit is optimised
-for efficiency and sensitivity at the high-frequency channel, while allowing RF pulses to be applied
-at the X frequency as well. As already explained, the X channel tuning frequency can be changed by simply
- exchanging either only a small RF-insert or the complete detector assembly. 
- \fig{fig:tandm} shows the measured reflection and transmission scattering coefficients ($S$-parameters) as a 
- function of frequency for two combinations of 
- proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz), 
- corresponding to the Larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14.1 T and 11.7 T respectively. 
- The measurements were performed in the pairs of 600 MHz and 60 MHz and 500 MHz and 125 MHz. The loaded $Q$ factors,
- determined from the -3dB points of the reflection curves, are 42, 49, 32, 36 at 600 MHz, 500 MHz, 
- 125 MHz and, 60 MHz respectively. The channel separation is better than -15dB at all operating frequencies.
+The probe is designed for double resonance, with proton-detected experiments in
+mind. The circuit is optimised for efficiency and sensitivity at the
+high-frequency channel, while allowing RF pulses to be applied at the X
+frequency as well. As already explained, the X channel tuning frequency can be
+changed by simply exchanging either only a small RF-insert or the complete
+detector assembly. \fig{fig:tandm} shows the measured reflection and
+transmission scattering coefficients ($S$-parameters) as a function of frequency
+for two combinations of proton (600 MHz, 500 MHz) and X channel frequencies (60
+MHz and 125 MHz), corresponding to the Larmor frequencies of $^{15}$N and
+$^{13}$C at magnetic fields of 14.1 T and 11.7 T respectively. The measurements
+were performed in the pairs of 600 MHz and 60 MHz and 500 MHz and 125 MHz. The
+loaded $Q$ factors, determined from the -3dB points of the reflection curves,
+are 42, 49, 32, 36 at 600 MHz, 500 MHz, 125 MHz and, 60 MHz respectively. The
+channel separation is better than -15dB at all operating frequencies.
 
-\begin{figure}
-\centering
+\begin{figure} \centering
 \includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png}
-\caption{
-Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 
-60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
-Probe can be tuned to 2 frequencies at a time, above results were measured in 
-pairs of 600 MHz with 60 MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the 
-frequencies as the channel separation is better than 15 decibels at all frequencies.}
-\label{fig:tandm} 
-\end{figure}
-Initially, FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
-Inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can be seen as fringes in~\fig{fig:field map} (A).
-B$_{0}$ field maps of the sample chamber were constructed from 2 gradient echo (FLASH) images having echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms for both FR4 and RO3035 PCB materials with the same chip~(\fig{fig:field map}).
-The brightness of each pixel is proportional to the sum of the magnitude of the two images, whereas the colour encode the phase difference between them.
-The full colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.
+\caption{ Experimental tuning and matching curves measured at 600 MHz, 500 MHz,
+60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz
+(\textsuperscript{13}C frequency at  and 11.7 T). Probe can be tuned to 2
+frequencies at a time, above results were measured in pairs of 600 MHz with 60
+MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the frequencies
+as the channel separation is better than 15 decibels at all frequencies.}
+\label{fig:tandm} \end{figure} Initially, FR4 PCB material was used for the
+detector assembly because of its low cost and easy availability. Inhomogeneities
+in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can
+be seen as fringes in~\fig{fig:field map} (A). B$_{0}$ field maps of the sample
+chamber were constructed from 2 gradient echo (FLASH) images having echo times
+($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms for both FR4
+and RO3035 PCB materials with the same chip~(\fig{fig:field map}). The
+brightness of each pixel is proportional to the sum of the magnitude of the two
+images, whereas the colour encode the phase difference between them. The full
+colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.
 
 To avoid the inhomogeneities of FR4 and therefore to achieve better resolution,
-detectors were made from RO3035 material. While RO3035 provides better resolution, it is more expensive 
-and takes longer to obtain compared to FR4. 
-It therefore makes sense to first prototype new detector designs in FR4, and only use the more expensive RO3035 
-once the design has been validated.
+detectors were made from RO3035 material. While RO3035 provides better
+resolution, it is more expensive and takes longer to obtain compared to FR4. It
+therefore makes sense to first prototype new detector designs in FR4, and only
+use the more expensive RO3035 once the design has been validated.
 
-\begin{figure}
-\centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png} 
-\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and Rogers RO3035 (B) PCB material.
-Both the field maps were constructed from 2 gradient echo images acquired on a chip filled with 130 mM sodium acetate dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
+\begin{figure} \centering
+\includegraphics[width=.9\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
+\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
+Rogers RO3035 (B) PCB material. Both the field maps were constructed from 2
+gradient echo images acquired on a chip filled with 130 mM sodium acetate
+dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
 \label{fig:field map}
@@
 
-The RF field at proton frequency shows excellent homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
-ratio of more than 90\% measured from $^1$H nutation of the water peak in an aqueous solution of 
-100~mM $^{15}$N-urea at 600~MHz. The probe generates 100~kHz nutation frequency from 100~W input power both at 
-600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$. 
-The detector geometry has been optimised for a sample volume of 5~$\mu$l. It compares reasonably well to
-the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for single-frequency detector 
-of half this size at a Larmor frequency of 300~MHz. 
-For X channel, 100~W of input power 
-produces nutation frequencies of 6 kHz for $^{15}$N and 14 kHz for $^{13}$C. 
-No signs of arcing were obseved at this power level for pulses up to 1~ms duration.
+The RF field at proton frequency shows excellent homogeneity, with a
+810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation
+of the water peak in an aqueous solution of 100~mM $^{15}$N-urea at 600~MHz. The
+probe generates 100~kHz nutation frequency from 100~W input power both at
+600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$)
+of 10 kHz/$\sqrt{W}$. The detector geometry has been optimised for a sample
+volume of 5~$\mu$l. It compares reasonably well to the value of 22
+kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for
+single-frequency detector of half this size at a Larmor frequency of 300~MHz.
+For X channel, 100~W of input power produces nutation frequencies of 6 kHz for
+$^{15}$N and 14 kHz for $^{13}$C. No signs of arcing were obseved at this power
+level for pulses up to 1~ms duration.
 
@@
 
-\fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O acquired at 600 MHz. 
-The spectrum was acquired with water presaturation at 100~Hz. 32 transients were averaged with a repetition delay
-of 3~s. The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above 
-the noise level. The orange curve corresponds to a Lorentzian lineshape with full width at half maximum of 
-3.35 Hz, corresponding to 0.0056 ppm. This is very similar to the resolution reported by Finch et al. at 300~MHz.
-While the residual cause of broadening is still under investigation, we have reason to suspect imperfections
-in the fabrications of the PMMA microfluidic devices to play a major role. Efforts to mitigate these and to
-achieve more highly resolved proton spectra are currently underway in our laboratory and will be reported at a later
-occasion.  The limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ ($n$ is the number of spins and $\Delta t$ is 1/linewidth of the observed resonance) is 
-1.4 nmol s$^{1/2}$ of protons at 600 MHz, slightly better than the value reported for a 
-smaller detector by Finch et al.~\cite{gream_2016}.
-
 \begin{figure}
@@
 
-Even though the resolution of the proton spectra still needs to be improved, it is sufficient to analyse
-complex mixtures. The proton spectrum of DMEM (Dulbecco modified Eagle's medium) cell growth medium acquired with 256 
-scans in 20 mins is shown in \fig{fig:media-spec}. This demonstrates the suitability of this probe 
-for metabolomic studies of microfluidic cultures of cells, tissues, and small organisms.
-
-\fig{fig:HSQC} demonstrates proton-detected double resonance experiments in the current setup. 
-The left panel shows a $^{13}$C-$^{1}$H heteronuclear single quantum correlation (HSQC) spectrum, acquired in 12 mins 
-(32 t$_1$ increments and 16 scans) 
-from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in water. The right panel shows a 
-$^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) 
-from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7. 
-All expected cross peaks are present in the spectrum.
-The ability to obtain meaningful  \textsuperscript{15}N-\textsuperscript{1}H correlation spectra from such small samples could prove very useful in the context of
-proteins that are difficult to express and therefore only available in small quantities. The integration of
-protein NMR and microfluidic technology also opens new possibilities for high-throughput kinetics and 
-binding studies.
-
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \label{fig:media-spec}
-\end{figure}
+\end{figure*}
+
+\fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium
+acetate dissolved in H$_2$O acquired at 600 MHz. The spectrum was acquired with
+water presaturation at 100~Hz. 32 transients were averaged with a repetition
+delay of 3~s. The inset shows an expanded view of the base of the acetate peak.
+Carbon satellites can be seen well above the noise level. The orange curve
+corresponds to a Lorentzian lineshape with full width at half maximum of 3.35
+Hz, corresponding to 0.0056 ppm. This is very similar to the resolution reported
+by Finch et al. at 300~MHz. While the residual cause of broadening is still
+under investigation, we have reason to suspect imperfections in the fabrications
+of the PMMA microfluidic devices to play a major role. Efforts to mitigate these
+and to achieve more highly resolved proton spectra are currently underway in our
+laboratory and will be reported at a later occasion.  The limit of detection
+$nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ ($n$ is the number of spins and
+$\Delta t$ is 1/linewidth of the observed resonance) is 1.4 nmol s$^{1/2}$ of
+protons at 600 MHz, slightly better than the value reported for a smaller
+detector by Finch et al.~\cite{gream_2016}.
+
+Even though the resolution of the proton spectra still needs to be improved, it
+is sufficient to analyse complex mixtures. The proton spectrum of DMEM (Dulbecco
+modified Eagle's medium) cell growth medium acquired with 256 scans in 20 mins
+is shown in \fig{fig:media-spec}. This demonstrates the suitability of this
+probe for metabolomic studies of microfluidic cultures of cells, tissues, and
+small organisms.
+
+\fig{fig:HSQC} demonstrates proton-detected double resonance experiments in the
+current setup. The left panel shows a $^{13}$C-$^{1}$H heteronuclear single
+quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
+and 16 scans) from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in
+water. The right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400
+mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM
+$^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7. All
+expected cross peaks are present in the spectrum. The ability to obtain
+meaningful  \textsuperscript{15}N-\textsuperscript{1}H correlation spectra from
+such small samples could prove very useful in the context of proteins that are
+difficult to express and therefore only available in small quantities. The
+integration of protein NMR and microfluidic technology also opens new
+possibilities for high-throughput kinetics and binding studies.
+
+\begin{figure} \centering
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png}
+\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and
+$^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from
+2.5$\mu$l sample volume at 14.1 T. Glucose HSQC spectrum was acquired in 12
+minutes from a 100 mM sample. Ubiquitin HSQC spectrum was acquired in 400
+minutes from a 1 mM sample.} \label{fig:HSQC} \end{figure}
+%$
+The probe can also be used to acquire micro magnetic resonance (MR) images using
+a Bruker micro-gradient unit. To this effect, the aluminium probe sleeve must be
+replaced by an electrically insulating material in order to avoid image
+distortions due to eddy currents in the sleeve. \fig{fig:tisli} shows MR images
+of mouse liver tissue slice immersed in DMEM cell growth medium. The slice was
+placed in a microfluidic device with circular sample chamber centred at the
+detector location, as shown in \fig{fig:tisli}(A). The image shown in
+\fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms
+and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness
+of the tissue; the lateral dimensions of all MR images in \fig{fig:tisli} are
+512$\times$512 pixels at a resolution of 30~$\mu$m. \fig{fig:tisli}(C) shows a
+RARE image using the same parameters, with 8 echos acquired per scan, thus
+reducing the acquisition time to 8 minutes. A spin echo image is shown in
+\fig{fig:tisli}(D), acquired over 25~min. Finally, \fig{fig:tisli}(E) shows a
+$B_0$ field map, which has been obtained by acquiring two separate FLASH images
+with echo times $t_E=5.3$~ms and 15.3~ms, respectively. , corresponding to local
+field variations of $\Delta B/B_0=...$ \todo{compute value and insert here}.
 
@@
 \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 
-\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14.1 T.
-Glucose HSQC spectrum was acquired in 12 minutes from a 100 mM sample.
-Ubiquitin HSQC spectrum was acquired in 400 minutes from a 1 mM sample.}
-\label{fig:HSQC} 
-\end{figure}
-%$ 
-The probe can also be used to acquire micro magnetic resonance (MR) images using a Bruker micro-gradient unit. 
-To this effect, the aluminium probe sleeve must be replaced by an electrically insulating material in order to 
-avoid image distortions due to eddy currents in the sleeve. 
-\fig{fig:tisli} shows MR images of mouse liver tissue slice 
-immersed in DMEM cell growth medium.
-The slice was placed in a microfluidic device with circular sample chamber centred at the detector location, as 
-shown in \fig{fig:tisli}(A). 
-The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with
-$t_R=120$~ms and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness of the tissue; the 
-lateral dimensions of all MR images in \fig{fig:tisli} are 512$\times$512 pixels
-at a resolution of 30~$\mu$m.
-\fig{fig:tisli}(C) shows a RARE image using the same parameters, with 8 echos
-acquired per scan, thus reducing the acquisition time to 8 minutes.
-A spin echo image is shown in \fig{fig:tisli}(D), acquired over 25~min. Finally,
-\fig{fig:tisli}(E) shows a $B_0$ field map, which has been obtained by acquiring
-two separate FLASH images with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
-, corresponding to local field variations of $\Delta B/B_0=...$ 
-\todo{compute value and insert here}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png}
 \caption{MR images of a freshly cut live slice from a mouse.

### 2019-02-05 ms5n17-tlp-mn-180216-001.tex
Put in the final figure

--- 2019-01-18 ms5n17-tlp-mn-180216-001.tex
@@
 \centering
+\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png} 
+\caption{(A) Orientation of the device with respect to the constriction on the detector (PCB plane 5 is hidden). (B) Exploded view of the rf assembly with the device. }
+\label{fig:rf-device-assembly} 
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png} 
@@
 \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
+\includegraphics[width=.6\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
 \caption{Exploded view of the probe design (left) and assembled probe (right). 
-Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 8) provides a 
+Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 7) provides a 
 generic mounting point for the NMR detector assembly (red). 
@@
 ensuring alignment of the sample chamber with the sensitive area on the PCB planes.
-The X channel frequency is controlled by a 
-modular PCB insert (6). The modular NMR detector is made up of parts 3 to 6 and is 
-connected to the TMPCB (8) through standard coaxial (SMP) connectors. 
-The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) 
+The modular NMR detector is made up of parts 3,4 and, 5 and is 
+connected to the TMPCB (7) through standard coaxial (SMP) connectors. 
+The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (9) 
 and, auxiliary support disks (12).}
@@
 The scaffold assembly is made up of two hollow aluminium tubes (11) held together with 
-precision machined parts at both ends (scaffold support disks (10)). 
+precision machined parts at both ends (scaffold support disks (9)). 
 The semi-rigid cables are  threaded through these hollow aluminium tubes 
@@
 but they may also be made by conventional machining.
-A tuning and matching PCB (TMPCB, 8) is held in place on the top of the probe skeleton by
-the detector support rods (9), with the semi-rigid coaxial cables providing
+A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
+the detector support rods (8), with the semi-rigid coaxial cables providing
 additional support.
@@
 for the exchangeable detector assembly. It also provides 
-capacitors (7) for secondary tuning and matching of the detector.
+capacitors (6) for secondary tuning and matching of the detector.
 The detector assembly is connected to the TMPCB through a pair of
@@
 fine tuning and matching 
-at the magnet through tuning rods (13) which reach all the way to the probe base.
+at the magnet through tuning rods (10) which reach all the way to the probe base.
 
@@
 needed.
-The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an 
-RF-insert (6). The detector used here is based on a planar transmission line geometry 
+The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4). The detector used here is based on a planar transmission line geometry 
 as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
@@
 \includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
-\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. 
+\caption{Dual channel probes with (A) and without (B) modular RF insert (13) for X channel. 
 O.D. of A is 44.45 mm and B is 38 mm. Circuit elements of X channel are integrated on the 
 PCB in B making it compact. Detachable SMP connectors (14) are used to 
-connect the RF insert (6) and the detector assembly.}
+connect the RF insert (13) and the detector assembly.}
 \label{fig:ProbePhoto}
 \end{figure}
-\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
-for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. 
-However, in (B) the circuitry of the RF insert (6) is integrated on the PCB plane (5), 
+\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (13) 
+for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 13. 
+However, in (B) the circuitry of the RF insert (13) is integrated on the PCB plane (5), 
 making the design more compact.

### 2019-02-05 ms5n17-tlp-mn-180216-001.tex

--- 2019-01-21 ms5n17-tlp-mn-180216-001.tex
@@
 \centering
+\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png} 
+\caption{(A) Orientation of the device with respect to the constriction on the detector (PCB plane 5 is hidden). (B) Exploded view of the rf assembly with the device. }
+\label{fig:rf-device-assembly} 
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
@@
 \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png}
+\includegraphics[width=.6\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
 \caption{Exploded view of the probe design (left) and assembled probe (right). 
-Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 8) provides a
+Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 7) provides a 
 generic mounting point for the NMR detector assembly (red). 
@@
 ensuring alignment of the sample chamber with the sensitive area on the PCB planes.
-The X channel frequency is controlled by a
-modular PCB insert (6). The modular NMR detector is made up of parts 3 to 6 and is
-connected to the TMPCB (8) through standard coaxial (SMP) connectors.
-The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10)
+The modular NMR detector is made up of parts 3,4 and, 5 and is 
+connected to the TMPCB (7) through standard coaxial (SMP) connectors. 
+The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (9)
 and, auxiliary support disks (12).}
@@
 The scaffold assembly is made up of two hollow aluminium tubes (11) held together with 
-precision machined parts at both ends (scaffold support disks (10)).
+precision machined parts at both ends (scaffold support disks (9)). 
 The semi-rigid cables are  threaded through these hollow aluminium tubes 
@@
 needed.
-The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an
-RF-insert (6). The detector used here is based on a planar transmission line geometry
+
+The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4). The detector used here is based on a planar transmission line geometry
+
 as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
@@
 \includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
-\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel.
+\caption{Dual channel probes with (A) and without (B) modular RF insert (13) for X channel. 
 O.D. of A is 44.45 mm and B is 38 mm. Circuit elements of X channel are integrated on the 
 PCB in B making it compact. Detachable SMP connectors (14) are used to 
-connect the RF insert (6) and the detector assembly.}
+connect the RF insert (13) and the detector assembly.}
 \label{fig:ProbePhoto}
 \end{figure}
-\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6)
-for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6.
-However, in (B) the circuitry of the RF insert (6) is integrated on the PCB plane (5),
+\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (13) 
+for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 13. 
+However, in (B) the circuitry of the RF insert (13) is integrated on the PCB plane (5), 
 making the design more compact.

### 2019-02-07 ms5n17-tlp-mn-180216-001.tex
Ready for submission

@@
 Detailed construction drawings and a complete set of CAD files is
-available for download at \cite{github-probe-download-2019}.
+available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
 The planar geometry of the detector accommodates exchangeable microfluidic devices
 which can be designed freely for specific experimental requirements as long as the
-overall shape of the device is maintained.
+overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative orientation.
 
@@
 \centering
-\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png} 
-\caption{(A) Orientation of the device with respect to the constriction on the detector (PCB plane 5 is hidden). (B) Exploded view of the rf assembly with the device. }
+\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png} 
+\caption{Drawings of the detector assembly and the microfluidic device (1) in (A) front view and, (B) exploded view.
+Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes.
+In (A), PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3.}
 \label{fig:rf-device-assembly}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
-\caption{The probe with and without sleeve.}
-\label{fig:probe}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
+%\caption{The probe with and without sleeve.}
+%\label{fig:probe}
+%\end{figure}
 The probe assembly design is based on readily and easily available materials and parts
@@
 \centering
-\includegraphics[width=.6\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
+\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
 \caption{Exploded view of the probe design (left) and assembled probe (right). 
@@
 The probe is composed of three main assemblies: A) probe base; B) scaffold assembly;
-C) detector assembly (\fig{fig:probe}).
+C) detector assembly (\fig{fig:probe-explode}).
 The  base (blue in \fig{fig:probe-explode}) and the scaffold assembly
@@
 needed.
-
-The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4). The detector used here is based on a planar transmission line geometry
-
-as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
+The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4).
+The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
 coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
@@
 The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
-Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert, in combination with
+Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert (13), in combination with
 the complex admittance of the detector at the X channel frequency.
@@
 as the channel separation is better than 15 decibels at all frequencies.}
-\label{fig:tandm} \end{figure} Initially, FR4 PCB material was used for the
+\label{fig:tandm} \end{figure}
+Initially, FR4 PCB material was used for the
 detector assembly because of its low cost and easy availability. Inhomogeneities
@@
 
-To avoid the inhomogeneities of FR4 and therefore to achieve better resolution,
-detectors were made from RO3035 material. While RO3035 provides better
+B$_{0}$ field map of RO3035 PCB material clearly show better B$_{0}$ field homogeneity compare to FR4. To avoid the inhomogeneities in FR4 and therefore to achieve better resolution,
+detectors were made from RO3035. While RO3035 provides better
 resolution, it is more expensive and takes longer to obtain compared to FR4. It
@@
 \begin{figure} \centering
-\includegraphics[width=.9\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
+\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
 \caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
@@
 $B_0$ field map, which has been obtained by acquiring two separate FLASH images
-with echo times $t_E=5.3$~ms and 15.3~ms, respectively. , corresponding to local
-field variations of $\Delta B/B_0=...$ \todo{compute value and insert here}.
+with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
 

### 2019-02-07 ms5n17-tlp-mn-180216-001.tex
fixed figure caption

@@
 \includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png}
-\caption{Drawings of the detector assembly and the microfluidic device (1) in (A) front view and, (B) exploded view.
+\caption{Drawings of the detector assembly and the microfluidic device (1).
+A: front view; B: exploded view.
 Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes.
-In (A), PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3.}
+In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3.}
 \label{fig:rf-device-assembly}

### 2019-02-08 cover-letter/ms5n17-tlp-mn-180216-001.tex
cover letter

\documentclass[12pt, letterpaper, twoside]{article}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\parskip}{\baselineskip}
\title{Cover letter Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging}
\begin{document}

Dear Editor,

We would like to submit a manuscript by M. Sharma and M. Utz entitled ``Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging" for possible publication in Journal of Magnetic Resonance.

In this manuscript, we report a novel modular dual channel NMR probe assembly for generic high sensitivity microfluidic NMR experiments. The probe assembly is designed to keep the manufacturing process as simple as possible and retaining generic NMR and microfluidic functionality. The sample is contained in a home made exchangeable microfluidic device. Microfluidic devices are made from cheap plastic materials with rapid prototyping techniques. The probe body is built from the readily accessible materials and the detector is made from PCB materials. Modularity of the detector enables the use of different detectors on the same probe base while the use of PCB materials ensures quick and easy design and manufacturing. Spectral resolution around 0.005 ppm at 600 MHz has been achieved with nLOD of 1.4 nmol sec$^{-1/2}$. Results of probe performance and applications are presented to demonstrate the potential of the current design.

The developed probe design could be useful for various microfluidic-nmr experiments like reaction monitoring, micro-imaging and metabolic studies of biological samples, protein structure determination and hyperpolarisation.

For this reason, we believe this paper fits well to the scope of your journal.

Thank you for your consideration!

Sincerely,
\end{document}

### 2019-02-08 ms5n17-tlp-mn-180216-001.tex
cover letter

@@
 which can be designed freely for specific experimental requirements as long as the
-overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative orientation.
+overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative positioning.
 
@@
 freely as long as the overall shape of the device is preserved, and the location
-of the sample chamber is maintained.
+of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirments.
 
@@
 mammalian cells. The probe is designed for double resonance, and
-acqusition of proton-detected heteronuclear correlation experiments
+acquisition of proton-detected heteronuclear correlation experiments
 has been demonstrated for small molecules as well as proteins.

### 2019-02-08 cover-letter/ms5n17-tlp-mn-180216-001.tex
edited cover letter

@@
-\documentclass[12pt, letterpaper, twoside]{article}
+\documentclass{mu-soton-letter}
 \usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setlength{\parskip}{\baselineskip}
-\title{Cover letter Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging}
+
+\signature{Marcel}
+
 \begin{document}
+\begin{letter}{Prof. Lucio Frydman\\
+  Editor,\\
+  Journal of Magnetic Resonance\\[2cm]
+  \textbf{Manuscript on a Modular Microfluidic NMR Probe System}}
+\vfill
+\opening{Dear Lucio,
+}
+Please find enclosed our manuscript titled
+``Modular transmission line probes for microfluidic nuclear
+magnetic resonance spectroscopy and imaging'', which we submit for publication
+in the Journal of Magnetic Resonance.
 
-Dear Editor,
+ We report a novel modular dual channel
+NMR probe assembly which enables a wide range microfluidic NMR experiments,
+including proton-detected double resonance methods.
+We show that its performance in terms of sensitivity, RF homogeneity, and
+resolution compares favourably with the best microfluidic NMR systems that
+have been reported to date. At the same time, the
+probe assembly is designed to keep the manufacturing process as simple
+as possible. The probe structure is built entirely from easily accessible
+materials such as Aluminium profiles, and the detector is implemented
+in standard printed circuit board technology.
+We hope that this will enable other researchers within the magnetic resonance
+community who are interested in developing applications
+of microfluidic NMR spectroscopy to build their own systems.
 
-We would like to submit a manuscript by M.
-Sharma and M.
-Utz entitled ``Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging" for possible publication in Journal of Magnetic Resonance.
+\closing{With best wishes,}
 
-In this manuscript, we report a novel modular dual channel NMR probe assembly for generic high sensitivity microfluidic NMR experiments.
-The probe assembly is designed to keep the manufacturing process as simple as possible and retaining generic NMR and microfluidic functionality.
-The sample is contained in a home made exchangeable microfluidic device.
-Microfluidic devices are made from cheap plastic materials with rapid prototyping techniques.
-The probe body is built from the readily accessible materials and the detector is made from PCB materials.
-Modularity of the detector enables the use of different detectors on the same probe base while the use of PCB materials ensures quick and easy design and manufacturing.
-Spectral resolution around 0.005 ppm at 600 MHz has been achieved with nLOD of 1.4 nmol sec$^{-1/2}$.
-Results of probe performance and applications are presented to demonstrate the potential of the current design.
+\end{letter}
 
-The developed probe design could be useful for various microfluidic-nmr experiments like reaction monitoring, micro-imaging and metabolic studies of biological samples, protein structure determination and hyperpolarisation.
-
-For this reason, we believe this paper fits well to the scope of your journal.
-
-Thank you for your consideration!
-
-Sincerely,
 \end{document}

### 2019-03-27 ms5n17-tlp-mn-180216-001.tex
most of the comments are fixed

@@
 \documentclass[preprint,5p]{elsarticle}
-\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
+\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
 %\linenumbers
@@
 of a fixed capillary into which the sample must be injected. Only a few designs
-that allow insertion of a removable microfluidic device into the detector have
-been described~\cite{Spengler-2014,Spengler-2016,gream_2016}.
+that allow insertion of a removable microfluidic device into the detector have \cbstart
+been described~\cite{Spengler-2014,Spengler-2016,gream_2016,swyer2019digital}. \cbend
 
@@
 %\end{itemize}
+\cbstart
 \begin{figure}
@@
 Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes.
-In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3.}
+In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3.
+Thickness of each of the PCB planes is 1.52 mm and the copper layers on the PCBs is 35 $\mu$m.
+Both the microfluidic device and the spacer are made from PMMA and have thickness of 0.9 mm and 1 mm respectively.}
 \label{fig:rf-device-assembly}
 \end{figure}
-
+\cbend
 %\begin{figure}
@@
 The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
-precision machined parts at both ends (scaffold support disks (9)).
-The semi-rigid cables are  threaded through these hollow aluminium tubes
-to reach the detector assembly.
+precision machined parts at both ends (scaffold support disks (9)).\cbstart
+The semi-rigid cables (RG 402) are  threaded through these hollow aluminium tubes
+to reach the detector assembly.\cbend
 Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
-In our case, these were laser cut from 5~mm thick PMMA sheets,
+In our case, these were laser cut from 5~mm thick poly(methyl methacrylate) (PMMA) sheets,
 but they may also be made by conventional machining.
@@
 additional support.
-The TMPCB is permantly fixed to the probe base, and serves as attachment point
-for the exchangeable detector assembly. It also provides
-capacitors (6) for secondary tuning and matching of the detector.
+The TMPCB is permanently fixed to the probe base, and serves as attachment point
+for the exchangeable detector assembly. \cbstart It also provides
+trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend
  The detector assembly is connected to the TMPCB through a pair of
 low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
+\cbstart SMP Connector Receptacle Male Pin is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3.
+The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend
 While each detector assembly is roughly
@@
 needed.
-The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4).
-The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
+The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them.
+\cbstart The spacer is made from a 1 mm thick PMMA sheet.\cbend  The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
 coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
@@
 into the probe,
-or the device can be actively perfused and operated in-situ.
+or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film when using the device as passive sample holder.\cbend
  The microfluidic device is held in place by the spacer
@@
 freely as long as the overall shape of the device is preserved, and the location
-of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirments.
-
+of the sample chamber is maintained.
+The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirements.
+\cbstart \fig{fig:device} shows various microfluidic devices.\cbend
+\cbstart
+\begin{table}[h]
+\centering
+\caption{Magnetic susceptibility values of the materials used in the probe\cite{wapler-2014,schenck-1996}}
+\label{tab:susceptibility}
+\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}||}
+\hline
+Material   & $\frac{\chi/PPM}{\rho/(g cm^{-3})}$	\\
+\hline
+PMMA		&-7.609(5)	\\
+Copper	&-9.63	\\
+FR4	&-1.918(9)		\\
+Aluminium	&20.7	\\
+\hline
+\end{tabular}
+\end{table}
+\cbend
+\cbstart
 \begin{figure}
 \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
 \caption{Microfluidic devices for different applications compatible with the current setup.
@@
 \end{figure}
+\cbend
 
-The double resnance circuit is based on the design shown in \fig{fig:circuit}.
+\cbstart The double resonance circuit is based on the design shown in \fig{fig:circuit}.\cbend
 %The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger
@@
 could be achieved without $L_1$.
-
+\cbstart
+\begin{table}[h]
+\centering
+\caption{Details of the circuit elements}
+\label{tab:circut}
+\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}||}
+\hline
+Circuit element   & Value	&Part Number\\
+\hline
+$C_1$, $C_2$ and, $C_8$		&1-23 pf	& NMAM25HV\\
+$C_9$	&3-23 pf	& NMNT23-6\\
+$C_3$, $C_7$	&4.3 pf		& S111TUE\\
+$C_4$	&82 pf	& S111TUE\\
+$C_5$, $C^{'}_{5}$	&2.4	& S111TUE\\
+$L_3$, $L_7$	 &16.6 nH	& 17NGLB\\
+$L_1$	&100 nH	& 4.7\\
+$C_6$	&3-23 pf	& NMAJ25HV\\
+$C_{20}$  & 2.4 pf		& S111TUE\\
+\hline
+\end{tabular}
+\end{table}
+\cbend
+\cbstart
 \begin{figure}
 \centering
-\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
+\includegraphics[width=.96\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
 \caption{Circuit diagram of the double resonance probe.
@@
 \end{figure}
+\cbend
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 detector planes (3 and 5) and the PMMA spacer between them were assembled using
-short bits of 0.5~mm magnet wire, which were soldered to the appropriate pads in
+short bits of 0.5~mm \cbstart diameter copper wire, \cbend which were soldered to the appropriate pads in
 the four corners of the detector structure.
@@
 for 2 hours before imaging.
+
+\cbstart
+\fig{fig:field map} were created through having echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms.
+\fig{fig:1H-nutation} of the water peak in an aqueous solution of 100~mM $^{15}$N-urea.
+\fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O acquired at 600 MHz.
+The spectrum was acquired with water presaturation at 100~Hz.
+32 transients were averaged with a repetition delay of 3~s.
+The proton spectrum of DMEM (Dulbecco
+modified Eagle's medium) cell growth medium acquired with 256 scans in 20 mins
+is shown in \fig{fig:media-spec}.
+The left panel shows a $^{13}$C-$^{1}$H heteronuclear single
+quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
+and 16 scans) from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in
+water. The right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400
+mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM
+$^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7.
+The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms
+and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness
+of the tissue \fig{fig:tisli}(C) shows a
+RARE image using the same parameters, with 8 echos acquired per scan, thus
+reducing the acquisition time to 8 minutes. A spin echo image is shown in
+\fig{fig:tisli}(D), acquired over 25~min. Finally, \fig{fig:tisli}(E) shows a
+$B_0$ field map, which has been obtained by acquiring two separate FLASH images
+with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
+\cbend
 
@@
 
+\cbstart
 \begin{figure} \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png}
 \caption{ Experimental tuning and matching curves measured at 600 MHz, 500 MHz,
 60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz
-(\textsuperscript{13}C frequency at  and 11.7 T). Probe can be tuned to 2
+(\textsuperscript{13}C frequency at 11.7 T). Probe can be tuned to 2
 frequencies at a time, above results were measured in pairs of 600 MHz with 60
@@
 as the channel separation is better than 15 decibels at all frequencies.}
-\label{fig:tandm} \end{figure}
+\label{fig:tandm}
+\end{figure}
+\cbend
 Initially, FR4 PCB material was used for the
@@
 be seen as fringes in~\fig{fig:field map} (A). B$_{0}$ field maps of the sample
-chamber were constructed from 2 gradient echo (FLASH) images having echo times
-($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms for both FR4
+chamber were constructed from 2 gradient echo (FLASH) images for both FR4
 and RO3035 PCB materials with the same chip~(\fig{fig:field map}). The
@@
 
+\cbstart
 \begin{figure} \centering
-\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
 \caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
-Rogers RO3035 (B) PCB material. Both the field maps were constructed from 2
+Rogers RO3035 (B) PCB material acquired at 11.7 T. Both the field maps were constructed from 2
 gradient echo images acquired on a chip filled with 130 mM sodium acetate
@@
 \end{figure}
+\cbend
 
 The RF field at proton frequency shows excellent homogeneity, with a
-810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation
-of the water peak in an aqueous solution of 100~mM $^{15}$N-urea at 600~MHz. The
+810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation at 600~MHz~\fig{fig:1H-nutation}. The
 probe generates 100~kHz nutation frequency from 100~W input power both at
@@
 
-%\begin{figure}
-%\centering
-%\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png}
-%\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz.
-The 810$^{\circ}$/90$^{\circ}$ ratio is more than 90\% at 600~MHz.
+\cbstart
+\begin{figure}
+\centering
+\includegraphics[width=.95\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png}
+\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz.
+The 810$^{\circ}$/90$^{\circ}$ ratio is 92\% at 600~MHz.
 The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 W.
-Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz}
-%\label{fig:1H-nutation}
-%\end{figure}
+Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz.}
+\label{fig:1H-nutation}
+\end{figure}
+\cbend
 
@@
 \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/lineshape.png}
+\includegraphics[width=.80\linewidth,keepaspectratio=true]{./figures/lineshape.png}
 \caption{Spectrum of 130 mM sodium acetate dissolved in water acquired in 32 scans with water presaturation.
@@
 \centering
-\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png}
 \caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
@@
 
-\fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium
-acetate dissolved in H$_2$O acquired at 600 MHz. The spectrum was acquired with
-water presaturation at 100~Hz. 32 transients were averaged with a repetition
-delay of 3~s. The inset shows an expanded view of the base of the acetate peak.
-Carbon satellites can be seen well above the noise level. The orange curve
+\fig{fig:lineshape} shows the spectrum of sodium acetate. The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above the noise level. The orange curve
 corresponds to a Lorentzian lineshape with full width at half maximum of 3.35
@@
 is sufficient to analyse complex mixtures. The proton spectrum of DMEM (Dulbecco
-modified Eagle's medium) cell growth medium acquired with 256 scans in 20 mins
-is shown in \fig{fig:media-spec}. This demonstrates the suitability of this
+modified Eagle's medium) shown in \fig{fig:media-spec} demonstrates the suitability of this
 probe for metabolomic studies of microfluidic cultures of cells, tissues, and
@@
 current setup. The left panel shows a $^{13}$C-$^{1}$H heteronuclear single
-quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
-and 16 scans) from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in
-water. The right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400
-mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM
-$^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7. All
+quantum correlation (HSQC) spectrum of $^{13}$C-glucose and the right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum of $^{15}$N-ubiquitin (17 $\mu$g). All
 expected cross peaks are present in the spectrum. The ability to obtain
@@
 detector location, as shown in \fig{fig:tisli}(A). The image shown in
-\fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms
-and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness
-of the tissue; the lateral dimensions of all MR images in \fig{fig:tisli} are
-512$\times$512 pixels at a resolution of 30~$\mu$m. \fig{fig:tisli}(C) shows a
-RARE image using the same parameters, with 8 echos acquired per scan, thus
-reducing the acquisition time to 8 minutes. A spin echo image is shown in
-\fig{fig:tisli}(D), acquired over 25~min. Finally, \fig{fig:tisli}(E) shows a
-$B_0$ field map, which has been obtained by acquiring two separate FLASH images
-with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
+\fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with; the lateral dimensions of all MR images in \fig{fig:tisli} are 512$\times$512 pixels at a resolution of 30~$\mu$m.
+\fig{fig:tisli}(C) shows a
+RARE image using the same parameters. A spin echo image is shown in
+\fig{fig:tisli}(D). Finally, \fig{fig:tisli}(E) shows a
+$B_0$ field map, which has been obtained by acquiring two separate FLASH images.
 
@@
 \includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png}
-\caption{MR images of a freshly cut live slice from a mouse.
+\caption{MR images of a freshly cut liver slice from a mouse.
 A: optical micrograph; B: Gradient echo image acquired in 1 minute; C: RARE8 image acquired in 8 minutes; D: Spin echo image acquired in 30 minutes; E: magnetic field map.}

### 2019-03-28 ms5n17-tlp-mn-180216-001.tex
All the commnets which could be added are added

@@
 detectors~\cite{stripline_jan}. Significant research has gone into developing
-micro-NMR detectors for flow probes, where the sample container takes the form
+micro-NMR detectors for flow probes\cbstart~\cite{bas-shim,Montinaro-2018,chen2017high,oosthoek2017continuous,bart2009microfluidic,bart2009optimization,massin2003planar}\cbend, where the sample container takes the form
 of a fixed capillary into which the sample must be injected. Only a few designs
@@
 precision machined parts at both ends (scaffold support disks (9)).\cbstart
-The semi-rigid cables (RG 402) are  threaded through these hollow aluminium tubes
+The semi-rigid cables (RG 402, 50~$\Omega$) are  threaded through these hollow aluminium tubes
 to reach the detector assembly.\cbend
@@
 low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
-\cbstart SMP Connector Receptacle Male Pin is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3.
+\cbstart SMP Connector Receptacle Male Pin ($J_3$ and $J_4$ in \fig{fig:circuit}) is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3 ($J_1$ and $J_2$ in \fig{fig:circuit}).
 The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend
@@
 Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
-thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.
+thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}. \cbstart Magnetic susceptibility value of PMMA and other materials in given in table~\ref{tab:susceptibility}\cbend
 Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
@@
 \hline
-Material   & $\frac{\chi/PPM}{\rho/(g cm^{-3})}$	\\
+Material   & $\chi$/ppm	\\
 \hline
-PMMA		&-7.609(5)	\\
+PMMA		&-9.054	\\
 Copper	&-9.63	\\
-FR4	&-1.918(9)		\\
+FR4	&-3.743		\\
 Aluminium	&20.7	\\
@@
  The transmission line detector is tuned to the desired proton
-Larmor frequency by chip capacitors located at its four corners,
+Larmor frequency by chip capacitors ($C_{20}$) located at its four corners,
 as well as a non-magnetic trimmer capacitor ($C_6$). Two primary
@@
 \textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz
-could be achieved without $L_1$.
-\cbstart
+could be achieved without $L_1$. \cbstart Details of all the circuit elements are given in table~\ref{tab:circuit}.
 \begin{table}[h]
 \centering
-\caption{Details of the circuit elements}
-\label{tab:circut}
-\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}||}
+\caption{Details of the circuit elements to tune the probe at 600 MHz and 60 MHz.}
+\label{tab:circuit}
+\begin{tabular}{||p{.3\linewidth}|p{.2\linewidth}|p{.3\linewidth}||}
 \hline
-Circuit element   & Value	&Part Number\\
+Circuit element   & Value	&Manufacturer Part Number	\\
 \hline
-$C_1$, $C_2$ and, $C_8$		&1-23 pf	& NMAM25HV\\
-$C_9$	&3-23 pf	& NMNT23-6\\
-$C_3$, $C_7$	&4.3 pf		& S111TUE\\
-$C_4$	&82 pf	& S111TUE\\
-$C_5$, $C^{'}_{5}$	&2.4	& S111TUE\\
+$C_1$, $C_2$ and, $C_8$		&1-23 pF	& NMAM25HV\\
+$C_9$	&3-23 pF	& NMNT23-6\\
+$C_6$	&3-23 pF	& NMAJ25HV\\
+$C_{20}$  & 2.4 pF		& S111TUE\\
+$C_3$, $C_7$	&4.3 pF		& S111TUE\\
+$C_4$	&82 pF	& S111TUE\\
+$C_5$, $C^{'}_{5}$	&2.4 pF	& S111TUE\\
+$L_1$	&111 nH	& 1010VS-111ME\\
 $L_3$, $L_7$	 &16.6 nH	& 17NGLB\\
-$L_1$	&100 nH	& 4.7\\
-$C_6$	&3-23 pf	& NMAJ25HV\\
-$C_{20}$  & 2.4 pf		& S111TUE\\
+$J_1$, $J_2$ & -&0734153591\\
+$J_3$, $J_4$ & -&SMP-MSLD-PCT-5\\
 \hline
@@
 \centering
-\includegraphics[width=.96\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
 \caption{Circuit diagram of the double resonance probe.
-Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).
+The background colour relates the different circuit elements on different PCBs.
+The back side of the PCB plane 5 and the front side of the PCB plane 3 is shown in horizontal orientation.
+The front side of the TMPCB 7 is shown in vertical orientation.
+Trimmer capacitor $C_6$ is placed on the back side of PCB plane 5.
+The copper layer is shown in brown and the solder pads to place the circuit elements are shown in off-white.
+An insulating solder mask layer over the copper layer prevents accidental short-circuiting.
 }
@@
 (detector support rods, auxiliary support disks). All electronic components
-including semi-rigid transmission lines were purchased from DigiKey Ltd. Cell
-cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
+including semi-rigid transmission lines were purchased from DigiKey Ltd \cbstart and Farnell element14, UK.
+Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\cbend Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
 (Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were
@@
 detector planes (3 and 5) and the PMMA spacer between them were assembled using
-short bits of 0.5~mm \cbstart diameter copper wire, \cbend which were soldered to the appropriate pads in
-the four corners of the detector structure.
-
-NMR experiments were performed on a Varian VNMRS console attached to a Varian
-600 premium shielded 14.1 T magnet. Imaging experiments were performed on Bruker
-AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet.
-Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK
-and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life
-Technologies, USA.
-
-Precision-cut murine liver slices (PCLS) were obtained by first extracting a
-tissue core of 8 mm diameter using a biopsy punch. PCLS of 250-300 $\mu$m
-thickness were cut from the core using a Krumdieck Tissue slicer, and then
-reduced to 3~mm diameter using a smaller punch. The slices were incubated in
-well-plates at 37$^\circ$C and 80\% O\textsubscript{2}, 5\% CO\textsubscript{2}
-for 2 hours before imaging.
+short bits of 0.5~mm \cbstart diameter copper wire bought from RS components, UK, \cbend which were soldered to the appropriate pads in the four corners of the detector structure.
 
 \cbstart
-\fig{fig:field map} were created through having echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms.
-\fig{fig:1H-nutation} of the water peak in an aqueous solution of 100~mM $^{15}$N-urea.
-\fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O acquired at 600 MHz.
-The spectrum was acquired with water presaturation at 100~Hz.
+\subsection{Details of NMR and MRI measurements}
+NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet.
+Field maps in the \fig{fig:field map} were created by gradient echo (FLASH) pulse sequence with echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms on a sample of 130 mM  sodium acetate dissolved in H$_2$O.
+The peak shown in the \fig{fig:1H-nutation} is of H$_2$O in an aqueous solution of 100~mM $^{15}$N-urea.
+\fig{fig:lineshape} shows proton spectrum of the acetate resonance from 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O.
+The spectrum was recorded after presturating the water signal with rf-field of 100~Hz.
 32 transients were averaged with a repetition delay of 3~s.
 The proton spectrum of DMEM (Dulbecco
-modified Eagle's medium) cell growth medium acquired with 256 scans in 20 mins
-is shown in \fig{fig:media-spec}.
-The left panel shows a $^{13}$C-$^{1}$H heteronuclear single
+modified Eagle's medium) cell growth medium in \fig{fig:media-spec} was acquired with 256 scans in 20 mins.
+The left panel of \fig{fig:HSQC} shows a $^{13}$C-$^{1}$H heteronuclear single
 quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
@@
 $^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7.
-The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms
-and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness
-of the tissue \fig{fig:tisli}(C) shows a
+
+For MRI experiments precision-cut murine liver slices (PCLS) were obtained by first extracting a
+tissue core of 8 mm diameter using a biopsy punch. PCLS of 250-300 $\mu$m
+thickness were cut from the core using a Krumdieck Tissue slicer, and then
+reduced to 3~mm diameter using a smaller punch. The slices were incubated in
+well-plates at 37$^\circ$C and 80\% O\textsubscript{2}, 5\% CO\textsubscript{2}
+for 2 hours before imaging. Imaging experiments were performed on Bruker
+AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet.
+The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms and $t_E=15.3$~ms.
+The slice thickness of  1~mm encompasses the entire thickness of the tissue \fig{fig:tisli}(C) shows a
 RARE image using the same parameters, with 8 echos acquired per scan, thus
@@
 in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can
-be seen as fringes in~\fig{fig:field map} (A). B$_{0}$ field maps of the sample
+be seen as fringes in~\fig{fig:field map} (A). \cbdelete B$_{0}$ field maps of the sample
 chamber were constructed from 2 gradient echo (FLASH) images for both FR4
@@
 colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.
-
+\cbdelete
 B$_{0}$ field map of RO3035 PCB material clearly show better B$_{0}$ field homogeneity compare to FR4. To avoid the inhomogeneities in FR4 and therefore to achieve better resolution,
@@
 \cbend
-
+\cbdelete 
 The RF field at proton frequency shows excellent homogeneity, with a
-810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation at 600~MHz~\fig{fig:1H-nutation}. The
+810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation at 600~MHz shown in~\fig{fig:1H-nutation}. The
 probe generates 100~kHz nutation frequency from 100~W input power both at
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
@@
 \label{fig:media-spec}
-\end{figure*}
-
-\fig{fig:lineshape} shows the spectrum of sodium acetate. The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above the noise level. The orange curve
+\end{figure}
+\cbdelete 
+\fig{fig:lineshape} shows the proton spectrum of sodium acetate.
+The inset shows an expanded view of the base of the acetate peak.
+Carbon satellites can be seen well above the noise level.
+The orange curve
 corresponds to a Lorentzian lineshape with full width at half maximum of 3.35
@@
 Even though the resolution of the proton spectra still needs to be improved, it
-is sufficient to analyse complex mixtures. The proton spectrum of DMEM (Dulbecco
+is sufficient to analyse complex mixtures. \cbdelete The proton spectrum of DMEM (Dulbecco
 modified Eagle's medium) shown in \fig{fig:media-spec} demonstrates the suitability of this
@@
 small organisms.
-
+\cbdelete 
 \fig{fig:HSQC} demonstrates proton-detected double resonance experiments in the
@@
 %$
+\cbdelete
 The probe can also be used to acquire micro magnetic resonance (MR) images using
@@
 replaced by an electrically insulating material in order to avoid image
-distortions due to eddy currents in the sleeve. \fig{fig:tisli} shows MR images
+distortions due to eddy currents in the sleeve.\cbstart In the current experiments a shorter aluminium tube with 3D printed top part to match the probe height was used.\cbend  \fig{fig:tisli} shows MR images
 of mouse liver tissue slice immersed in DMEM cell growth medium. The slice was

### 2019-03-29 cover-letter/mu1y11-tlp-mn-190329-response-reviwers.tex
started response letter

\documentclass{mu-soton-letter}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newenvironment{reviewer}{\begin{quote}\color{50!black}}{\end{quote}}

\signature{Marcel}

\begin{document}
\begin{letter}{Prof. Lucio Frydman\\
  Editor,\\
  Journal of Magnetic Resonance\\[2cm]
  \textbf{Revised Manuscript on a Modular Microfluidic NMR Probe System}}
\vfill
\opening{Dear Lucio,
}
Please find enclosed our revised manuscript titled
``Modular transmission line probes for microfluidic nuclear
magnetic resonance spectroscopy and imaging'', which we submit for publication
in the Journal of Magnetic Resonance.

We are grateful to the reviewers for their careful evaluation of the manuscript
and for their constructive comments. We have responded to their specific concerns
as detailed below:

\textbf{Reviewer 1}

\begin{reviewer}
  The submitted manuscript reports on a dual-channel modular probe assembly for NMR spectroscopy and imaging on microliter samples.
  The reported probe is an ''improved'' version of the one reported by the same authors in JMR in 2016 (Ref. 25).
  These improvements are:
  1)Dual channel (1H/15N or 1H/13C) instead of single channel (1H).
  2)Simplified fabrication and assembly of the probe parts, with significantly improved "versatility".

  General comment:
  The work presented in this manuscript deserve to be published. However, since it is a purely "technical" work, I would like to see the "technical content" described in more details.
  I think that the authors idea to have the drawings and the CAD files of the probe stored in a "open access" website is certainly good. However, I would like to see many more details of the probe design directly in the manuscript text, drawings, schematics, and figure captions.
\end{reviewer}

Values of all the circuit elements have been assembled in a table. The circuit diagram has been expanded to show the positioning of the circuit elements on the different PCBs. }

Detailed comments:

1) PAGE 1:  I would definitely add more relevant literature on "microfluidic NMR probes" such as:

-Swyer, Ian, et al. "Digital microfluidics and nuclear magnetic resonance spectroscopy for in situ diffusion measurements and reaction monitoring" Lab on a Chip 19, 641 (2019).

Added in removable device

-van Meerten, S. G. J., P. Jan M. van Bentum, and Arno PM Kentgens. "Shim-on-Chip Design for Microfluidic NMR Detectors." Analytical chemistry 90, 10134(2018)

Added in flow probe

-Montinaro, E., et al. "3D printed microchannels for sub-nL NMR spectroscopy." PloS one 13, e0192780 (2018).

Added in flow probe

-Chen, Ying, et al. "High-resolution microstrip NMR detectors for subnanoliter samples." Physical Chemistry Chemical Physics 19, 28163 (2017).

Added in flow probe

-Oosthoek-de Vries, Anna Jo, et al. "Continuous flow 1H and 13C NMR spectroscopy in microfluidic stripline NMR chips." Analytical Chemistry 89,  2296 (2017).

Added in flow probe

-Bart, J., et al. "A microfluidic high-resolution NMR flow probe." Journal of the American Chemical Society 131, 5014 (2009)

Added in flow probe

-Bart, J., et al. "Optimization of stripline-based microfluidic chips for high-resolution NMR." Journal of magnetic resonance 201, 175 (2009).

Added in flow probe

-Massin, C., et al. "Planar microcoil-based microfluidic NMR probes." Journal of Magnetic Resonance 164, 242 (2003).

Added in flow probe

Response: All of the suggested references are added in the introduction. Only the first article by Swyer, Ian, et al. describes a functional and exchangeable microfluidic device, rest of the references are added in the microfluidic flow probes for NMR.

2) FIGURE 1: Add in the caption the thickness of each "layer" (PCBs, spacer, microfluid device). Specify also the thickness of the Cu layers on the PCBs (this might be relevant for the spectral resolution due to a different thickness of the "air layers" in close proximity to the sample). Some of these dimensions are reported in the text but it would be nice to have all dimensions also in this figure caption.

Response: All the details are added in the figure caption.

3) FIGURE 1: From the drawings it seems to me that the Al spacer is short-circuiting the transmission line. Please clarify this point.

Response: The spacer is made of PMMA, hence it is non-conducting. In the caption of figure 5 it is added that an insulating solder mask layer on the copper prevents accidental short-circuiting.

4) PAGE 2, LINE 32, RIGHT: Indicated which specific semi-rigid coaxial cables are used.

Response: RG 402, 50 Ohm added to the text.

5) PAGE 2, LINE 48, RIGHT: Indicated which specific capacitors are used.

Response: The values and the manufacturer part number of all the circuit elements are added in table 2.

6) PAGE 2, LINE 50, RIGHT: Indicated which specific connectors are used (in the probe base as well as in the probe PCB).

Response: All the details are added in the text.

7) PAGE 3, LINE 30, LEFT: For the case in which the microfluidic device is used as "passive sample holder", how the microfluidic device is sealed?

Response: By an optical adhesive film, added in the text.

8) PAGE 3, LINE 58, LEFT: It would be useful for the reader to add the approximate values for the magnetic susceptibility of as many as possible probe materials (in order of importance: PMMA, Cu, RO3035, FR4, Al).

Response: suseptibilties are added in table 1.

9) PAGE 3, LINE 48, RIGHT: Typo "resnance".

Response: Resonance is corrected in the text.

10) FIGURE 4: I would make this figure bigger for clarity (scale it up to full column width).

Response:  The figure is increased to full column width.

11) FIGURE 5: Add a detailed picture and/or drawing of the tuning&matching PCB (the TMPCB in the authors notation), give the position on the PCB of all the components (capacitors, variable capacitors, and inductors), and give all values (and model and manufacturer, particularly for the inductors and the variable capacitors) of these components. Increase the font size (it is too small).

Response: The picture of TMPCB and detector PCB 3 and 5 are added. Details of all the circuit elements are added in the table 2.

12) PAGE 4, LINE 6, RIGHT: It is not clear to me the meaning of "0.5 mm magnet wire".

Response: copper wire of diameter 0.5 mm.

13) FIGURE 6: I would scale up the figure to full column width. The font size is a bit too small. In the caption there is a typo ("at and").

Response: The figure is scaled up with bigger fonts

14) FIGURE 7: Is it really true that the FR4 gives a worse spectral resolution with respect to R03035 because of "glass fibre rovings" as mentioned at PAGE 4, LINE 51, RIGHT ? Is the thickness of the Cu layer the same on both substrates ? Is the magnetic susceptibility of the two material similar ? The R03035 has significantly lower tensile modulus with respect to FR4. I wonder if this might help in having a better "mechanical fit" in the mounting, which might reduce the presence of "air voids".

Response: The resolution is directly related to the B0 field homogeneity. The field maps of the two materials under the same conditions show the fringes observed in the FR4 material. These fringes are caused by glass fiber rovings which can be seen optically. Magnetic susceptibility of the two materials is different, but the materials are more than 0.1 mm far from the sample and hence will have minimal effect on the B0 field. The mechanical fit is similar in both the designs as the chip is inserted without resistance in both the cases. The air voids are expected to be of the volume in both the designs as the spacer is same.

15) FIGURE 7: Add a drawing or picture of the "constriction" (with scale bar or, even better, indicated dimensions) where we can see the width of the constriction, the length of the constriction, and the width of the gap between the constriction and the "external" metal.

Response: The constriction drawing with dimensions is added in the figure 5.

16) PAGE 6, LINE 59, LEFT: Specify the material used as replacement of Al for the sleeve in the imaging experiments?

Response: Shorter aluminium tube with 3D printed part on top to match the probe height was used.

\closing{With best wishes,}

\end{letter}

\end{document}

### 2019-03-29 cover-letter/mu1y11-tlp-mn-190329-response-reviwers.tex
formated the coverletter and citations

@@
 
-\newenvironment{reviewer}{\begin{quote}\color{50!black}}{\end{quote}}
+\newenvironment{reviewer} {\begin{quote}\color{black!50}} {\end{quote}}
 
@@
 
-\begin{reviewer}
-  The submitted manuscript reports on a dual-channel modular probe assembly for NMR spectroscopy and imaging on microliter samples.
+\textcolor{black!50}
+{\emph{The submitted manuscript reports on a dual-channel modular probe assembly for NMR spectroscopy and imaging on microliter samples.
   The reported probe is an ''improved'' version of the one reported by the same authors in JMR in 2016 (Ref. 25).
@@
   1)Dual channel (1H/15N or 1H/13C) instead of single channel (1H).
-  2)Simplified fabrication and assembly of the probe parts, with significantly improved "versatility".
+  2)Simplified fabrication and assembly of the probe parts, with significantly improved "versatility".}}
 
-  General comment:
+\textcolor{black!50}{ \textbf{General comment:}}
+
+  \begin{reviewer}
   The work presented in this manuscript deserve to be published. However, since it is a purely "technical" work, I would like to see the "technical content" described in more details.
@@
 
-Values of all the circuit elements have been assembled in a table. The circuit diagram has been expanded to show the positioning of the circuit elements on the different PCBs. }
+Values of all the circuit elements have been assembled in a table. The circuit diagram has been expanded to show the positioning of the circuit elements on the different PCBs.
 
-Detailed comments:
+\textcolor{black!50}{ \textbf{Detailed comments:}}
 
+\begin{reviewer}
 1) PAGE 1:  I would definitely add more relevant literature on "microfluidic NMR probes" such as:
-
+\end{reviewer}
 -Swyer, Ian, et al. "Digital microfluidics and nuclear magnetic resonance spectroscopy for in situ diffusion measurements and reaction monitoring" Lab on a Chip 19, 641 (2019).
@@
 
-Response: All of the suggested references are added in the introduction.
+All of the suggested references are added in the introduction.
 Only the first article by Swyer, Ian, et al.
@@
 
+\begin{reviewer}
 2) FIGURE 1: Add in the caption the thickness of each "layer" (PCBs, spacer, microfluid device).
@@
 Some of these dimensions are reported in the text but it would be nice to have all dimensions also in this figure caption.
+\end{reviewer}
+All the details are added in the figure caption.
 
-Response: All the details are added in the figure caption.
+\begin{reviewer}
+3) FIGURE 1: From the drawings it seems to me that the Al spacer is short-circuiting the transmission line. Please clarify this point.
+\end{reviewer}
+The spacer is made of PMMA, hence it is non-conducting. In the caption of figure 5 it is added that an insulating solder mask layer on the copper prevents accidental short-circuiting.
+\begin{reviewer}
+4) PAGE 2, LINE 32, RIGHT: Indicated which specific semi-rigid coaxial cables are used.
+\end{reviewer}
+RG 402, 50 Ohm added to the text.
+\begin{reviewer}
+5) PAGE 2, LINE 48, RIGHT: Indicated which specific capacitors are used.
+\end{reviewer}
+The values and the manufacturer part number of all the circuit elements are added in table 2.
 
-3) FIGURE 1: From the drawings it seems to me that the Al spacer is short-circuiting the transmission line. Please clarify this point.
+\begin{reviewer}
+6) PAGE 2, LINE 50, RIGHT: Indicated which specific connectors are used (in the probe base as well as in the probe PCB).
+\end{reviewer}
+All the details are added in the text.
 
-Response: The spacer is made of PMMA, hence it is non-conducting. In the caption of figure 5 it is added that an insulating solder mask layer on the copper prevents accidental short-circuiting.
+\begin{reviewer}
+7) PAGE 3, LINE 30, LEFT: For the case in which the microfluidic device is used as "passive sample holder", how the microfluidic device is sealed?
+\end{reviewer}
+By an optical adhesive film, added in the text.
 
-4) PAGE 2, LINE 32, RIGHT: Indicated which specific semi-rigid coaxial cables are used.
+\begin{reviewer}
+8) PAGE 3, LINE 58, LEFT: It would be useful for the reader to add the approximate values for the magnetic susceptibility of as many as possible probe materials (in order of importance: PMMA, Cu, RO3035, FR4, Al).
+\end{reviewer}
+Susceptibilities are added in table 1.
 
-Response: RG 402, 50 Ohm added to the text.
+\begin{reviewer}
+9) PAGE 3, LINE 48, RIGHT: Typo "resnance".
+\end{reviewer}
+Resonance is corrected in the text.
 
-5) PAGE 2, LINE 48, RIGHT: Indicated which specific capacitors are used.
+\begin{reviewer}
+10) FIGURE 4: I would make this figure bigger for clarity (scale it up to full column width).
+\end{reviewer}
+The figure is increased to full column width.
 
-Response: The values and the manufacturer part number of all the circuit elements are added in table 2.
-
-6) PAGE 2, LINE 50, RIGHT: Indicated which specific connectors are used (in the probe base as well as in the probe PCB).
-
-Response: All the details are added in the text.
-
-7) PAGE 3, LINE 30, LEFT: For the case in which the microfluidic device is used as "passive sample holder", how the microfluidic device is sealed?
-
-Response: By an optical adhesive film, added in the text.
-
-8) PAGE 3, LINE 58, LEFT: It would be useful for the reader to add the approximate values for the magnetic susceptibility of as many as possible probe materials (in order of importance: PMMA, Cu, RO3035, FR4, Al).
-
-Response: suseptibilties are added in table 1.
-
-9) PAGE 3, LINE 48, RIGHT: Typo "resnance".
-
-Response: Resonance is corrected in the text.
-
-10) FIGURE 4: I would make this figure bigger for clarity (scale it up to full column width).
-
-Response:  The figure is increased to full column width.
-
-11) FIGURE 5: Add a detailed picture and/or drawing of the tuning&matching PCB (the TMPCB in the authors notation), give the position on the PCB of all the components (capacitors, variable capacitors, and inductors), and give all values (and model and manufacturer, particularly for the inductors and the variable capacitors) of these components.
+\begin{reviewer}
+11) FIGURE 5: Add a detailed picture and/or drawing of the tuning\&matching PCB (the TMPCB in the authors notation), give the position on the PCB of all the components (capacitors, variable capacitors, and inductors), and give all values (and model and manufacturer, particularly for the inductors and the variable capacitors) of these components.
 Increase the font size (it is too small).
-
-Response: The picture of TMPCB and detector PCB 3 and 5 are added. Details of all the circuit elements are added in the table 2.
-
+\end{reviewer}
+The picture of TMPCB and detector PCB 3 and 5 are added. Details of all the circuit elements are added in the table 2.
+\begin{reviewer}
 12) PAGE 4, LINE 6, RIGHT: It is not clear to me the meaning of "0.5 mm magnet wire".
-
-Response: copper wire of diameter 0.5 mm.
-
+\end{reviewer}
+copper wire of diameter 0.5 mm.
+\begin{reviewer}
 13) FIGURE 6: I would scale up the figure to full column width. The font size is a bit too small. In the caption there is a typo ("at and").
-
-Response: The figure is scaled up with bigger fonts
-
+\end{reviewer}
+The figure is scaled up with bigger fonts
+\begin{reviewer}
 14) FIGURE 7: Is it really true that the FR4 gives a worse spectral resolution with respect to R03035 because of "glass fibre rovings" as mentioned at PAGE 4, LINE 51, RIGHT ?
@@
 I wonder if this might help in having a better "mechanical fit" in the mounting, which might reduce the presence of "air voids".
-
-Response: The resolution is directly related to the B0 field homogeneity.
+\end{reviewer}
+The resolution is directly related to the B0 field homogeneity.
 The field maps of the two materials under the same conditions show the fringes observed in the FR4 material.
@@
 The air voids are expected to be of the volume in both the designs as the spacer is same.
+\begin{reviewer}
+15) FIGURE 7: Add a drawing or picture of the "constriction" (with scale bar or, even better, indicated dimensions) where we can see the width of the constriction, the length of the constriction, and the width of the gap between the constriction and the "external" metal.
+\end{reviewer}
+The constriction drawing with dimensions is added in the figure 5.
+\begin{reviewer}
+16) PAGE 6, LINE 59, LEFT: Specify the material used as replacement of Al for the sleeve in the imaging experiments?
+\end{reviewer}
+Shorter aluminium tube with 3D printed part on top to match the probe height was used.
 
-15) FIGURE 7: Add a drawing or picture of the "constriction" (with scale bar or, even better, indicated dimensions) where we can see the width of the constriction, the length of the constriction, and the width of the gap between the constriction and the "external" metal.
+\textbf{Reviewer 2}
 
-Response: The constriction drawing with dimensions is added in the figure 5.
+\textcolor{black!50}{
+\emph{In this manuscript, the authors report the design and construction of a modular NMR probe dedicated to microfluidics applications.
+The authors show 1D proton and HSQC spectra as well as images of mouse liver slices acquired with this probe.
+The proton RF coil design used has been published previously by the same group.
+This probe design is interesting for the microfluidics community especially since the authors make available all the drawings on github.}}
 
-16) PAGE 6, LINE 59, LEFT: Specify the material used as replacement of Al for the sleeve in the imaging experiments?
+\textcolor{black!50}{ \textbf{Major comments:}}
 
-Response: Shorter aluminium tube with 3D printed part on top to match the probe height was used.
+\begin{reviewer}
+1.
+The authors claim that the RF homogeneity is "excellent", they must show B1 maps to support this claim.
+On page 5, in the paragraph starting with "The RF field?" it should be 180/90 and not 810/90.
+\end{reviewer}
+The 1H nutation diagram is added as figure 8. It is indeed 810/90 as can be seen in figure 8.
+\begin{reviewer}
+2.      Are the B0 maps in Figure 7 acquired at 14T?  Please specify. Please show B0 and B1 maps both at 11.7 and 14.1T.
+\end{reviewer}
+B0 filed maps were acquired in 11.7 T. It is added in the text. B0 field maps can only be acquired at 11.7 T due to the availability of the gradient unit.
+\begin{reviewer}
+3.
+The images of liver slices are not convincing.
+If three different sequences are used the authors should adapt the parameters to obtain meaningful contrast.
+Please list all the acquisition parameters for the different sequences.
+In the caption of figure 11, should be "cut liver slices".
+\end{reviewer}
+It must be noted that the images were taken to demonstrate the proof of principle to obtain an MR image of a tissue slice using the current setup.
+The optimisation of the imaging parameters and the tissue culture are underway to obtain a physiologically relevant dataset.
+Parameters for different pulse sequences will be added in the methods section.
+\begin{reviewer}
+4.
+The Results and Discussion section is a mixture or Results and Experimental parameters (in particular NMR/MRI acquisition parameters).
+Please move all the experimental parameters into the Methods section under a subsection dedicated to NMR/MRI acquisitions.
+\end{reviewer}
+All the experimental parameters have been moved to a subsection in the methods section.
+
+\textcolor{black!50}{ \textbf{Minor comments:}}
+\begin{reviewer}
+1.      Please reformulate the last sentence on page 1 starting with "The probe is designed".
+\end{reviewer}
+??
 

### 2019-03-29 cover-letter/mu1y11-tlp-mn-190329-response-reviwers.tex
response letter and minor cleanup

@@
+% !TEX program = pdflatex
 \documentclass{mu-soton-letter}
@@
 and for their constructive comments. We have responded to their specific concerns
-as detailed below:
+as follows:
 
@@
 
-\textcolor{black!50}
-{\emph{The submitted manuscript reports on a dual-channel modular probe assembly for NMR spectroscopy and imaging on microliter samples.
+%\textcolor{black!50}
+\begin{reviewer}
+{The submitted manuscript reports on a dual-channel modular probe assembly for NMR spectroscopy and imaging on microliter samples.
   The reported probe is an ''improved'' version of the one reported by the same authors in JMR in 2016 (Ref. 25).
@@
   1)Dual channel (1H/15N or 1H/13C) instead of single channel (1H).
-  2)Simplified fabrication and assembly of the probe parts, with significantly improved "versatility".}}
+  2)Simplified fabrication and assembly of the probe parts, with significantly improved "versatility".}
 
@@
 
-  \begin{reviewer}
   The work presented in this manuscript deserve to be published. However, since it is a purely "technical" work, I would like to see the "technical content" described in more details.
@@
 
-\textcolor{black!50}{ \textbf{Detailed comments:}}
-
 \begin{reviewer}
+\textbf{Detailed comments:}
 1) PAGE 1:  I would definitely add more relevant literature on "microfluidic NMR probes" such as:
-\end{reviewer}
 -Swyer, Ian, et al. "Digital microfluidics and nuclear magnetic resonance spectroscopy for in situ diffusion measurements and reaction monitoring" Lab on a Chip 19, 641 (2019).
 
-Added in removable device
+%Added in removable device
 
@@
 
-Added in flow probe
+%Added in flow probe
 
@@
 
-Added in flow probe
-
-All of the suggested references are added in the introduction.
-Only the first article by Swyer, Ian, et al.
-describes a functional and exchangeable microfluidic device, rest of the references are added in the microfluidic flow probes for NMR.
+%Added in flow probe
+\end{reviewer}
+All of the suggested references have been added to the introduction.
 
@@
 \end{reviewer}
-All the details are added in the figure caption.
+All the details have been added to the figure caption.
 
@@
 \end{reviewer}
-The spacer is made of PMMA, hence it is non-conducting. In the caption of figure 5 it is added that an insulating solder mask layer on the copper prevents accidental short-circuiting.
+The spacer is made of PMMA, hence it is non-conducting. This is pointed out
+clearly in the revised manuscript. Also, the caption of figure 5 now points out
+that an insulating solder mask layer on the copper prevents accidental short-circuiting.
 \begin{reviewer}
@@
 \end{reviewer}
-The values and the manufacturer part number of all the circuit elements are added in table 2.
+The values and the manufacturer part number of all the circuit elements
+have been added in table 2.
 
@@
 \end{reviewer}
-All the details are added in the text.
+The detailed specficications of the connectors are now provided in the text.
 
@@
 \end{reviewer}
-By an optical adhesive film, added in the text.
+Using an optical adhesive film, as added to the revised manuscript.
 
@@
 \end{reviewer}
-Susceptibilities are added in table 1.
+All relevant known susceptibilities are now listed in Table 1.
 
@@
 \end{reviewer}
-Resonance is corrected in the text.
+corrected.
 
@@
 \end{reviewer}
-The picture of TMPCB and detector PCB 3 and 5 are added. Details of all the circuit elements are added in the table 2.
+Full information on the TMPCB as well as the other two PCB components is now
+included in Figure 5. The relationship between the circuit diagram and the PCB
+layouts is now also indicated clearly, andd etails of all the circuit
+elements are given in Table 2.
 \begin{reviewer}
@@
 \end{reviewer}
-copper wire of diameter 0.5 mm.
+copper wire of diameter 0.5 mm; the text has been corrected accordingly.
 \begin{reviewer}
@@
 \end{reviewer}
-The figure is scaled up with bigger fonts
+The figure has been scaled up, uses bigger fonts, and the typo has been corrected.
 \begin{reviewer}
@@
 The resolution is directly related to the B0 field homogeneity.
-The field maps of the two materials under the same conditions show the fringes observed in the FR4 material.
-These fringes are caused by glass fiber rovings which can be seen optically.
-Magnetic susceptibility of the two materials is different, but the materials are more than 0.1 mm far from the sample and hence will have minimal effect on the B0 field.
-The mechanical fit is similar in both the designs as the chip is inserted without resistance in both the cases.
-The air voids are expected to be of the volume in both the designs as the spacer is same.
+The field maps of the two materials under the same conditions show the fringes
+observed in the FR4 material. These fringes are caused by glass fiber
+rovings which can be seen optically.
+The mechanical fit is similar in both the designs as the chip is inserted
+without resistance in both the cases. The vertical boundaries between the chip and the
+detector planes do not contribute to susceptibility broadening, as they are parallel
+to the magnetic field; therefore the air voids between the chip and the detector
+are not relevant. The Cu layers in both materials are about 35 $\mu$m thick,
+and their horizontal edges (which define the constriction geometry) are unlikely
+to be a dominant factor in the observed line widths.
 \begin{reviewer}
@@
 \end{reviewer}
-Shorter aluminium tube with 3D printed part on top to match the probe height was used.
+A shorter aluminium housing was used, combined with a 3D printed (ABS plastic)
+housing for the detection part of the probe. This is pointed out clearly in the
+revised manuscript.
 
+\clearpage
 \textbf{Reviewer 2}
 
-\textcolor{black!50}{
-\emph{In this manuscript, the authors report the design and construction of a modular NMR probe dedicated to microfluidics applications.
+\begin{reviewer}
+  {In this manuscript, the authors report the design and construction of a modular NMR probe dedicated to microfluidics applications.
 The authors show 1D proton and HSQC spectra as well as images of mouse liver slices acquired with this probe.
 The proton RF coil design used has been published previously by the same group.
-This probe design is interesting for the microfluidics community especially since the authors make available all the drawings on github.}}
+This probe design is interesting for the microfluidics community especially since the authors make available all the drawings on github.}
 
-\textcolor{black!50}{ \textbf{Major comments:}}
+  \textbf{Major comments:}
 
-\begin{reviewer}
 1.
@@
 \end{reviewer}
-The 1H nutation diagram is added as figure 8. It is indeed 810/90 as can be seen in figure 8.
+In order to document the RF homogeneity, we have added the 1H nutation diagram
+as Figure 8. The quantity referred to by the reviewer is indeed the ratio of the
+amplitudes of signals following a 810$^\circ$ pulse and a 90$^\circ$ pulse, respectively.
+This quanitity is commonly used to quantify RF homogeneity in commercial probes,
+and is often referred to as "810/90 ratio". It is now explained clearly in Figure 8.
 \begin{reviewer}
@@
 \end{reviewer}
-B0 filed maps were acquired in 11.7 T. It is added in the text. B0 field maps can only be acquired at 11.7 T due to the availability of the gradient unit.
+B0 filed maps were acquired in 11.7 T, as now indicated in the text. B0 field maps could
+ only be acquired at 11.7 T, since we do not have a gradient unit available on
+ our 14.1T magnets.
+
 \begin{reviewer}
@@
 \end{reviewer}
-It must be noted that the images were taken to demonstrate the proof of principle to obtain an MR image of a tissue slice using the current setup.
-The optimisation of the imaging parameters and the tissue culture are underway to obtain a physiologically relevant dataset.
-Parameters for different pulse sequences will be added in the methods section.
+As requested, detailed parameters for the different pulse
+sequences have been added to the methods section.
+We agree with the reviewer that the contrast in the images shown could be
+improved. However,
+the images are merely providing a proof
+of principle that the probe is capable to support MR microimaging, and no
+conclusions going beyond this are drawn from this data in the manuscript.
+Optimisation of the parameters for a particular sample class was outside of the
+scope of the work presented here. That said, the images do exhibit some
+structural contrast, and features in the slices can be correlated with the
+optical micrograph. The optimisation of the imaging parameters and the
+tissue culture are currently underway, but will be reported separately.
+
+\clearpage
 \begin{reviewer}
@@
 \end{reviewer}
-??
+As suggested, we have reformulated the sentence, and connected it with the following one:
+"The probe is optimised for proton detected double resonance, with the
+second channel tunable to different nuclei\ldots"
+\vspace{3cm}
+
+Again, we are grateful to the reviewers for their constructive criticism, and
+we are confident that the above changes adequately address their concerns.
 

### 2019-03-29 ms5n17-tlp-mn-180216-001.tex
started response letter
formated the coverletter and citations
response letter and minor cleanup

@@
 %\linenumbers
+\biboptions{sort&compress}
 \hypersetup{
@@
 that allow insertion of a removable microfluidic device into the detector have \cbstart
-been described~\cite{Spengler-2014,Spengler-2016,gream_2016,swyer2019digital}. \cbend
+been described~\cite{Spengler-2014,Spengler-2016,gream_2016,swyer2019digital}.\cbend
 
@@
 within 2-3 days for less than $\sim$200 $\geneuro$.
-The probe is designed for proton detected double resonance.
-The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or
+The probe is optimised for proton detected double resonance, with the
+second channel tunable to different nuclei such as $^{13}$C, $^{15}$N, or
 $^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
@@
 into the probe,
-or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film when using the device as passive sample holder.\cbend
+or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film (MicroAmp, AB Applied Biosystems)
+when using the device as passive sample holder.\cbend
  The microfluidic device is held in place by the spacer
@@
 replaced by an electrically insulating material in order to avoid image
-distortions due to eddy currents in the sleeve.\cbstart In the current experiments a shorter aluminium tube with 3D printed top part to match the probe height was used.\cbend  \fig{fig:tisli} shows MR images
+distortions due to eddy currents in the sleeve.\cbstart\
+A shorter aluminium tube with 3D printed top part (made from ABS plastic)
+to match the probe height was used.\cbend  \fig{fig:tisli} shows MR images
 of mouse liver tissue slice immersed in DMEM cell growth medium. The slice was

### 2019-03-29 cover-letter/mu1y11-tlp-mn-190329-response-reviwers.tex
review format

@@
 
-\signature{Marcel}
-
 \begin{document}
@@
 \vfill
-\opening{Dear Lucio,
-}
-Please find enclosed our revised manuscript titled
-``Modular transmission line probes for microfluidic nuclear
-magnetic resonance spectroscopy and imaging'', which we submit for publication
-in the Journal of Magnetic Resonance.
-
-We are grateful to the reviewers for their careful evaluation of the manuscript
-and for their constructive comments. We have responded to their specific concerns
-as follows:
 
@@
 
-Again, we are grateful to the reviewers for their constructive criticism, and
-we are confident that the above changes adequately address their concerns.
-
-\closing{With best wishes,}
-
 \end{letter}

### 2019-03-29 cover-letter/mu1y11-tlp-mn-190329-resub-cover.tex
review format

--- 2019-03-29 cover-letter/mu1y11-tlp-mn-190329-response-reviwers.tex
@@
 in the Journal of Magnetic Resonance.
-
 We are grateful to the reviewers for their careful evaluation of the manuscript
-and for their constructive comments. We have responded to their specific concerns
-as detailed below:
-
-\textbf{Reviewer 1}
-
-\textcolor{black!50}
-{\emph{The submitted manuscript reports on a dual-channel modular probe assembly for NMR spectroscopy and imaging on microliter samples.
-  The reported probe is an ''improved'' version of the one reported by the same authors in JMR in 2016 (Ref. 25).
-  These improvements are:
-  1)Dual channel (1H/15N or 1H/13C) instead of single channel (1H).
-  2)Simplified fabrication and assembly of the probe parts, with significantly improved "versatility".}}
-
-\textcolor{black!50}{ \textbf{General comment:}}
-
-  \begin{reviewer}
-  The work presented in this manuscript deserve to be published. However, since it is a purely "technical" work, I would like to see the "technical content" described in more details.
-  I think that the authors idea to have the drawings and the CAD files of the probe stored in a "open access" website is certainly good.
-However, I would like to see many more details of the probe design directly in the manuscript text, drawings, schematics, and figure captions.
-\end{reviewer}
-
-Values of all the circuit elements have been assembled in a table. The circuit diagram has been expanded to show the positioning of the circuit elements on the different PCBs.
-
-\textcolor{black!50}{ \textbf{Detailed comments:}}
-
-\begin{reviewer}
-1) PAGE 1:  I would definitely add more relevant literature on "microfluidic NMR probes" such as:
-\end{reviewer}
--Swyer, Ian, et al. "Digital microfluidics and nuclear magnetic resonance spectroscopy for in situ diffusion measurements and reaction monitoring" Lab on a Chip 19, 641 (2019).
-
-Added in removable device
-
--van Meerten, S. G. J., P. Jan M. van Bentum, and Arno PM Kentgens. "Shim-on-Chip Design for Microfluidic NMR Detectors." Analytical chemistry 90, 10134(2018)
-
-Added in flow probe
-
--Montinaro, E., et al. "3D printed microchannels for sub-nL NMR spectroscopy." PloS one 13, e0192780 (2018).
-
-Added in flow probe
-
--Chen, Ying, et al. "High-resolution microstrip NMR detectors for subnanoliter samples." Physical Chemistry Chemical Physics 19, 28163 (2017).
-
-Added in flow probe
-
--Oosthoek-de Vries, Anna Jo, et al. "Continuous flow 1H and 13C NMR spectroscopy in microfluidic stripline NMR chips." Analytical Chemistry 89,  2296 (2017).
-
-Added in flow probe
-
--Bart, J., et al. "A microfluidic high-resolution NMR flow probe." Journal of the American Chemical Society 131, 5014 (2009)
-
-Added in flow probe
-
--Bart, J., et al. "Optimization of stripline-based microfluidic chips for high-resolution NMR." Journal of magnetic resonance 201, 175 (2009).
-
-Added in flow probe
-
--Massin, C., et al. "Planar microcoil-based microfluidic NMR probes." Journal of Magnetic Resonance 164, 242 (2003).
-
-Added in flow probe
-
-All of the suggested references are added in the introduction.
-Only the first article by Swyer, Ian, et al.
-describes a functional and exchangeable microfluidic device, rest of the references are added in the microfluidic flow probes for NMR.
-
-\begin{reviewer}
-2) FIGURE 1: Add in the caption the thickness of each "layer" (PCBs, spacer, microfluid device).
-Specify also the thickness of the Cu layers on the PCBs (this might be relevant for the spectral resolution due to a different thickness of the "air layers" in close proximity to the sample).
-Some of these dimensions are reported in the text but it would be nice to have all dimensions also in this figure caption.
-\end{reviewer}
-All the details are added in the figure caption.
-
-\begin{reviewer}
-3) FIGURE 1: From the drawings it seems to me that the Al spacer is short-circuiting the transmission line. Please clarify this point.
-\end{reviewer}
-The spacer is made of PMMA, hence it is non-conducting. In the caption of figure 5 it is added that an insulating solder mask layer on the copper prevents accidental short-circuiting.
-\begin{reviewer}
-4) PAGE 2, LINE 32, RIGHT: Indicated which specific semi-rigid coaxial cables are used.
-\end{reviewer}
-RG 402, 50 Ohm added to the text.
-\begin{reviewer}
-5) PAGE 2, LINE 48, RIGHT: Indicated which specific capacitors are used.
-\end{reviewer}
-The values and the manufacturer part number of all the circuit elements are added in table 2.
-
-\begin{reviewer}
-6) PAGE 2, LINE 50, RIGHT: Indicated which specific connectors are used (in the probe base as well as in the probe PCB).
-\end{reviewer}
-All the details are added in the text.
-
-\begin{reviewer}
-7) PAGE 3, LINE 30, LEFT: For the case in which the microfluidic device is used as "passive sample holder", how the microfluidic device is sealed?
-\end{reviewer}
-By an optical adhesive film, added in the text.
-
-\begin{reviewer}
-8) PAGE 3, LINE 58, LEFT: It would be useful for the reader to add the approximate values for the magnetic susceptibility of as many as possible probe materials (in order of importance: PMMA, Cu, RO3035, FR4, Al).
-\end{reviewer}
-Susceptibilities are added in table 1.
-
-\begin{reviewer}
-9) PAGE 3, LINE 48, RIGHT: Typo "resnance".
-\end{reviewer}
-Resonance is corrected in the text.
-
-\begin{reviewer}
-10) FIGURE 4: I would make this figure bigger for clarity (scale it up to full column width).
-\end{reviewer}
-The figure is increased to full column width.
-
-\begin{reviewer}
-11) FIGURE 5: Add a detailed picture and/or drawing of the tuning\&matching PCB (the TMPCB in the authors notation), give the position on the PCB of all the components (capacitors, variable capacitors, and inductors), and give all values (and model and manufacturer, particularly for the inductors and the variable capacitors) of these components.
-Increase the font size (it is too small).
-\end{reviewer}
-The picture of TMPCB and detector PCB 3 and 5 are added. Details of all the circuit elements are added in the table 2.
-\begin{reviewer}
-12) PAGE 4, LINE 6, RIGHT: It is not clear to me the meaning of "0.5 mm magnet wire".
-\end{reviewer}
-copper wire of diameter 0.5 mm.
-\begin{reviewer}
-13) FIGURE 6: I would scale up the figure to full column width. The font size is a bit too small. In the caption there is a typo ("at and").
-\end{reviewer}
-The figure is scaled up with bigger fonts
-\begin{reviewer}
-14) FIGURE 7: Is it really true that the FR4 gives a worse spectral resolution with respect to R03035 because of "glass fibre rovings" as mentioned at PAGE 4, LINE 51, RIGHT ?
-Is the thickness of the Cu layer the same on both substrates ?
-Is the magnetic susceptibility of the two material similar ?
-The R03035 has significantly lower tensile modulus with respect to FR4.
-I wonder if this might help in having a better "mechanical fit" in the mounting, which might reduce the presence of "air voids".
-\end{reviewer}
-The resolution is directly related to the B0 field homogeneity.
-The field maps of the two materials under the same conditions show the fringes observed in the FR4 material.
-These fringes are caused by glass fiber rovings which can be seen optically.
-Magnetic susceptibility of the two materials is different, but the materials are more than 0.1 mm far from the sample and hence will have minimal effect on the B0 field.
-The mechanical fit is similar in both the designs as the chip is inserted without resistance in both the cases.
-The air voids are expected to be of the volume in both the designs as the spacer is same.
-\begin{reviewer}
-15) FIGURE 7: Add a drawing or picture of the "constriction" (with scale bar or, even better, indicated dimensions) where we can see the width of the constriction, the length of the constriction, and the width of the gap between the constriction and the "external" metal.
-\end{reviewer}
-The constriction drawing with dimensions is added in the figure 5.
-\begin{reviewer}
-16) PAGE 6, LINE 59, LEFT: Specify the material used as replacement of Al for the sleeve in the imaging experiments?
-\end{reviewer}
-Shorter aluminium tube with 3D printed part on top to match the probe height was used.
-
-\textbf{Reviewer 2}
-
-\textcolor{black!50}{
-\emph{In this manuscript, the authors report the design and construction of a modular NMR probe dedicated to microfluidics applications.
-The authors show 1D proton and HSQC spectra as well as images of mouse liver slices acquired with this probe.
-The proton RF coil design used has been published previously by the same group.
-This probe design is interesting for the microfluidics community especially since the authors make available all the drawings on github.}}
-
-\textcolor{black!50}{ \textbf{Major comments:}}
-
-\begin{reviewer}
-1.
-The authors claim that the RF homogeneity is "excellent", they must show B1 maps to support this claim.
-On page 5, in the paragraph starting with "The RF field?" it should be 180/90 and not 810/90.
-\end{reviewer}
-The 1H nutation diagram is added as figure 8. It is indeed 810/90 as can be seen in figure 8.
-\begin{reviewer}
-2.      Are the B0 maps in Figure 7 acquired at 14T?  Please specify. Please show B0 and B1 maps both at 11.7 and 14.1T.
-\end{reviewer}
-B0 filed maps were acquired in 11.7 T. It is added in the text. B0 field maps can only be acquired at 11.7 T due to the availability of the gradient unit.
-\begin{reviewer}
-3.
-The images of liver slices are not convincing.
-If three different sequences are used the authors should adapt the parameters to obtain meaningful contrast.
-Please list all the acquisition parameters for the different sequences.
-In the caption of figure 11, should be "cut liver slices".
-\end{reviewer}
-It must be noted that the images were taken to demonstrate the proof of principle to obtain an MR image of a tissue slice using the current setup.
-The optimisation of the imaging parameters and the tissue culture are underway to obtain a physiologically relevant dataset.
-Parameters for different pulse sequences will be added in the methods section.
-\begin{reviewer}
-4.
-The Results and Discussion section is a mixture or Results and Experimental parameters (in particular NMR/MRI acquisition parameters).
-Please move all the experimental parameters into the Methods section under a subsection dedicated to NMR/MRI acquisitions.
-\end{reviewer}
-All the experimental parameters have been moved to a subsection in the methods section.
-
-\textcolor{black!50}{ \textbf{Minor comments:}}
-\begin{reviewer}
-1.      Please reformulate the last sentence on page 1 starting with "The probe is designed".
-\end{reviewer}
-??
+and for their constructive comments. We have revised the manuscript
+in response to their specific concerns
+as detailed in a separate document, and
+we are confident that these changes adequately address their concerns.
 

### 2019-03-29 ms5n17-tlp-mn-180216-001.tex
review format

@@
-\documentclass[preprint,5p]{elsarticle}
+\documentclass[review]{elsarticle}
 \usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
@@
 The TMPCB is permanently fixed to the probe base, and serves as attachment point
-for the exchangeable detector assembly. \cbstart It also provides
+for the exchangeable detector assembly. \cbstart\  It also provides
 trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend

### 2019-03-30 revised-manuscript/ms5n17-tlp-mn-180216-001.tex
Final corrections from Marcel are added revised-manuscript has the latest version without changebars

--- 2019-03-29 ms5n17-tlp-mn-180216-001.tex
@@
 %\linenumbers
+\nochangebars
 \biboptions{sort&compress}
@@
 In this paper we present a novel modular probe designed for generic
-microfluidic-NMR experiments. The design is based on a transmission line
+microfluidic NMR experiments. The design is based on a transmission line
 detector~\cite{stripline_jan,gream_2016} using inexpensive
@@
 %\end{itemize}
-\cbstart
+\cbstart\
 \begin{figure}
 \centering
-\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png}
+\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/fig1-ms5n17-tlp-im-190205-rf-device-assembly.png}
 \caption{Drawings of the detector assembly and the microfluidic device (1).
-A: front view; B: exploded view.
+A: front view (dimensions in mm); B: exploded view.
 Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes.
@@
 \end{figure}
-\cbend
+\cbend\
 %\begin{figure}
@@
 \centering
-\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png}
-\caption{Exploded view of the probe design (left) and assembled probe (right).
+\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/fig2-ms5n17-tlp-im-181007-Probe-explode.png}
+\caption{Exploded view of the probe design (left) and assembled probe (center).
 Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 7) provides a
@@
 The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
-precision machined parts at both ends (scaffold support disks (9)).\cbstart
-The semi-rigid cables (RG 402, 50~$\Omega$) are  threaded through these hollow aluminium tubes
-to reach the detector assembly.\cbend
+precision machined parts at both ends (scaffold support disks (9)).\cbstart\ The semi-rigid cables (RG 402, 50~$\Omega$) are  threaded through these hollow aluminium tubes
+to reach the detector assembly.\cbend\
 Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
@@
 The TMPCB is permanently fixed to the probe base, and serves as attachment point
-for the exchangeable detector assembly. \cbstart It also provides
-trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend
- The detector assembly is connected to the TMPCB through a pair of
+for the exchangeable detector assembly.\cbstart\ It also provides
+trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend\ The detector assembly is connected to the TMPCB through a pair of
 low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
-\cbstart SMP Connector Receptacle Male Pin ($J_3$ and $J_4$ in \fig{fig:circuit}) is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3 ($J_1$ and $J_2$ in \fig{fig:circuit}).
-The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend
-While each detector assembly is roughly
+\cbstart\ The SMP connector receptacle male pin ($J_3$ and $J_4$ in \fig{fig:circuit}) is soldered on the TMPCB and the SMP connector jack male pin is soldered on the PCB plane 3 ($J_1$ and $J_2$ in \fig{fig:circuit}).
+The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend\ While each detector assembly is roughly
 tuned and matched with fixed circuit elements soldered onto it,
@@
 needed.
-The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them.
-\cbstart The spacer is made from a 1 mm thick PMMA sheet.\cbend  The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
+The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them.\cbstart\ The spacer is made from a 1 mm thick PMMA sheet.\cbend\ The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
 coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
@@
 into the probe,
-or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film (MicroAmp, AB Applied Biosystems)
-when using the device as passive sample holder.\cbend
- The microfluidic device is held in place by the spacer
+or the device can be actively perfused and operated in-situ.\cbstart\ The device inlet and outlet are sealed by an optical adhesive film (MicroAmp, AB Applied Biosystems)
+when using the device as passive sample holder.\cbend\ The microfluidic device is held in place by the spacer
 between the two PCB planes coinciding the sample chamber with the constriction on the
@@
 \centering
-\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
+\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/fig3-ms5n17-tlp-im-181007-both-detectors.png}
 \caption{Dual channel probes with (A) and without (B) modular RF insert (13) for X channel.
@@
 \fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (13)
-for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 13.
+for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging (13).
 However, in (B) the circuitry of the RF insert (13) is integrated on the PCB plane (5),
@@
 Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with
-wide bore magnets with spacers or gradient stack to keep the probe centred.
+wide bore magnets with appropriate spacers to keep the probe centered.
 
-Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
-thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}. \cbstart Magnetic susceptibility value of PMMA and other materials in given in table~\ref{tab:susceptibility}\cbend
+The microfluidic devices were made from inexpensive PMMA sheets by laser cutting and
+thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.\cbstart\ PMMA was chosen for ease of fabrication, but also due to the close match in magnetic susceptibility with that of water (Table~\ref{tab:susceptibility}).\cbend\
 Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
@@
 \centering
-\caption{Magnetic susceptibility values of the materials used in the probe\cite{wapler-2014,schenck-1996}}
+\caption{Magnetic susceptibility values of some relevant materials.\cite{wapler-2014,schenck-1996}}
 \label{tab:susceptibility}
@@
 Aluminium	&20.7	\\
+Water & -9.02\\
 \hline
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig4-ms5n17-tlp-im-181007-devices.png}
 \caption{Microfluidic devices for different applications compatible with the current setup.
@@
 The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
-Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert (13), in combination with
+Tuning is achieved by $L_1$ and $C_4$ in combination with
 the complex admittance of the detector at the X channel frequency.
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig5-ms5n17-tlp-im-180110-circuit-diagram.png}
 \caption{Circuit diagram of the double resonance probe.
@@
 The front side of the TMPCB 7 is shown in vertical orientation.
-Trimmer capacitor $C_6$ is placed on the back side of PCB plane 5.
+Trimmer capacitor $C_6$ is placed on the back side of PCB plane 3.
 The copper layer is shown in brown and the solder pads to place the circuit elements are shown in off-white.
@@
 (detector support rods, auxiliary support disks). All electronic components
-including semi-rigid transmission lines were purchased from DigiKey Ltd \cbstart and Farnell element14, UK.
-Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\cbend Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
+including semi-rigid transmission lines were purchased from DigiKey Ltd\cbstart\ and Farnell element14, UK.
+Sodium acetate and $^{15}$N labeled urea were purchased from Sigma-Aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\cbend\ Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
 (Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were
 cut to desired size and functionality (holes or channels) using a laser
-engraving system  (HPC Laser L3040), and then bonded using the protocol
+engraving system  (L3040 from HPC Laser LTD, Elland, UK), and then bonded using the protocol
 described in~\cite{yilmaz_bonding}.
@@
 sensitivity and resolution (\fig{fig:ProbePhoto}(B)). The probe skeleton was
-assembled from prefabricated aluminium tubes held with the precision-machined
+assembled from prefabricated aluminium tubes held together with the precision-machined
 scaffold disks using brass screws. Semi-rigid transmission lines were then
@@
 detector planes (3 and 5) and the PMMA spacer between them were assembled using
-short bits of 0.5~mm \cbstart diameter copper wire bought from RS components, UK, \cbend which were soldered to the appropriate pads in the four corners of the detector structure.
+short bits of 0.5~mm\cbstart\ diameter copper wire bought from RS components, UK,\cbend\ which were soldered to the appropriate pads in the four corners of the detector structure.
 
@@
 \subsection{Details of NMR and MRI measurements}
-NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet.
+NMR spectra were obtained on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet.
 Field maps in the \fig{fig:field map} were created by gradient echo (FLASH) pulse sequence with echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms on a sample of 130 mM  sodium acetate dissolved in H$_2$O.
 The peak shown in the \fig{fig:1H-nutation} is of H$_2$O in an aqueous solution of 100~mM $^{15}$N-urea.
-\fig{fig:lineshape} shows proton spectrum of the acetate resonance from 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O.
-The spectrum was recorded after presturating the water signal with rf-field of 100~Hz.
+\fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O.
+The spectrum was recorded after pre-saturating the water signal at a nutation frequency of 100~Hz.
 32 transients were averaged with a repetition delay of 3~s.
@@
 well-plates at 37$^\circ$C and 80\% O\textsubscript{2}, 5\% CO\textsubscript{2}
-for 2 hours before imaging. Imaging experiments were performed on Bruker
-AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet.
+for 2 hours before imaging. Imaging experiments were performed on a Bruker
+AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet equipped with a Bruker Micro2.5 gradient system.
 The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms and $t_E=15.3$~ms.
-The slice thickness of  1~mm encompasses the entire thickness of the tissue \fig{fig:tisli}(C) shows a
+The slice thickness of  1~mm encompasses the entire thickness of the tissue.
+\fig{fig:tisli}(C) shows a
 RARE image using the same parameters, with 8 echos acquired per scan, thus
@@
 \begin{figure} \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig6-ms5n17-tlp-im-180710-tandm-sameaxis.png}
 \caption{ Experimental tuning and matching curves measured at 600 MHz, 500 MHz,
@@
 \begin{figure} \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig7-pcb-fieldmap-colorbar.png}
 \caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
@@
 single-frequency detector of half this size at a Larmor frequency of 300~MHz.
-For X channel, 100~W of input power produces nutation frequencies of 6 kHz for
+For the X channel, 100~W of input power produces nutation frequencies of 6 kHz for
 $^{15}$N and 14 kHz for $^{13}$C. No signs of arcing were obseved at this power
@@
 \centering
-\includegraphics[width=.95\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png}
+\includegraphics[width=.95\linewidth,keepaspectratio=true]{./figures/fig8-ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png}
 \caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz.
@@
 \centering
-\includegraphics[width=.80\linewidth,keepaspectratio=true]{./figures/lineshape.png}
+\includegraphics[width=.80\linewidth,keepaspectratio=true]{./figures/fig9-lineshape.png}
 \caption{Spectrum of 130 mM sodium acetate dissolved in water acquired in 32 scans with water presaturation.
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig10-media-180125-005-bigger-font.png}
 \caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
@@
 $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ ($n$ is the number of spins and
-$\Delta t$ is 1/linewidth of the observed resonance) is 1.4 nmol s$^{1/2}$ of
+$\Delta t$ is 1/linewidth of the observed resonance) is 1.4 nmol s$^{1/2}$ for
 protons at 600 MHz, slightly better than the value reported for a smaller
@@
 \begin{figure} \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig11-ms5n17-tlp-sp-180612-HSQCspect.png}
 \caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and
@@
 A shorter aluminium tube with 3D printed top part (made from ABS plastic)
-to match the probe height was used.\cbend  \fig{fig:tisli} shows MR images
+to match the probe height was used.\cbend\ \fig{fig:tisli} shows MR images
 of mouse liver tissue slice immersed in DMEM cell growth medium. The slice was
@@
 \centering
-\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png}
+\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig12-ms5n17-tisli-im-180511.png}
 \caption{MR images of a freshly cut liver slice from a mouse.

### 2019-03-30 ms5n17-tlp-mn-180216-001.tex
Update ms5n17-tlp-mn-180216-001.tex

--- 2019-03-29 ms5n17-tlp-mn-180216-001.tex
@@
 %\end{itemize}
-\cbstart
+\cbstart\
 \begin{figure}
@@
 \caption{Drawings of the detector assembly and the microfluidic device (1).
-A: front view; B: exploded view.
+A: front view (dimensions in mm); B: exploded view.
 Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes.
@@
 \includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png}
-\caption{Exploded view of the probe design (left) and assembled probe (right).
+\caption{Exploded view of the probe design (left) and assembled probe (center).
 Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 7) provides a
